---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');htmlName<-'egov-xml-structure';rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-',htmlName,'.html')) })
title : "e-Gov xml Structure"
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 4
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 1000px;}</style>

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fileName <- 
  'functionList.csv'
baseURL <- 
  'https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/'
functionList <- 
  read.csv(
    file = paste0(baseURL,'csv/',fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    RCurl::getURL(paste0(baseURL,functionList[iii,1]),ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
library(XML)
pathOutput <- 
  paste0("C:/Users/",Sys.info()['user'],"/Desktop/R_Data_Write/")
setwd(pathOutput)
xmlFile <-
  dir(pathOutput)[grep('\\.xml',dir(pathOutput))]
iii <- 2
xmlData <- xmlToList(xmlFile[iii])
```

#### Sample: `r xmlData$LawBody$LawTitle`
- `r xmlFile[iii]`

```{r}
names(xmlData)
xmlData$LawNum
names(xmlData$LawBody)
xmlData$LawBody$LawTitle
names(xmlData$LawBody$MainProvision$Article)
xmlData$LawBody$MainProvision$Article$ArticleCaption
xmlData$LawBody$MainProvision$Article$ArticleTitle
names(xmlData$LawBody$MainProvision$Article$Paragraph)
xmlData$LawBody$MainProvision$Article$Paragraph$ParagraphNum
names(xmlData$LawBody$MainProvision$Article$Paragraph$ParagraphSentence)
names(xmlData$LawBody$MainProvision$Article$Paragraph$ParagraphSentence$Sentence)
xmlData$LawBody$MainProvision$Article$Paragraph$ParagraphSentence$Sentence$text
names(xmlData$LawBody$MainProvision$Article$Paragraph$AmendProvision)
names(xmlData$LawBody$MainProvision$Article$Paragraph$AmendProvision$AmendProvisionSentence)
names(xmlData$LawBody$MainProvision$Article$Paragraph$AmendProvision$AmendProvisionSentence$Sentence)
xmlData$LawBody$MainProvision$Article$Paragraph$AmendProvision$AmendProvisionSentence$Sentence$text
names(xmlData$LawBody$SupplProvision)
xmlData$LawBody$SupplProvision$SupplProvisionLabel
names(xmlData$LawBody$SupplProvision$Article)
xmlData$LawBody$SupplProvision$Article$ArticleCaption
xmlData$LawBody$SupplProvision$Article$ArticleTitle
names(xmlData$LawBody$SupplProvision$Article$Paragraph)
xmlData$LawBody$SupplProvision$Article$Paragraph$ParagraphNum
names(xmlData$LawBody$SupplProvision$Article$Paragraph$ParagraphSentence)
names(xmlData$LawBody$SupplProvision$Article$Paragraph$ParagraphSentence$Sentence)
xmlData$LawBody$SupplProvision$Article$Paragraph$ParagraphSentence$Sentence$text
names(xmlData$LawBody$SupplProvision$Article$Paragraph$Item)
xmlData$LawBody$SupplProvision$Article$Paragraph$Item$ItemTitle
names(xmlData$LawBody$SupplProvision$Article$Paragraph$Item$ItemSentence)
names(xmlData$LawBody$SupplProvision$Article$Paragraph$Item$ItemSentence$Column)
names(xmlData$LawBody$SupplProvision$Article$Paragraph$Item$ItemSentence$Column$Sentence)
xmlData$LawBody$SupplProvision$Article$Paragraph$Item$ItemSentence$Column$Sentence$text
```

***

```{r warning=F,error=F,message=F,echo=F,results='hide'}
pathOutput <- 
  paste0("C:/Users/",Sys.info()['user'],"/Desktop/R_Data_Write/")
setwd(pathOutput)
xmlFile <-
  dir(pathOutput)[grep('\\.xml',dir(pathOutput))]
iii <- 1
xmlData <- xmlToList(xmlFile[iii])
```

#### Sample: `r xmlData$LawBody$LawTitle`
- `r xmlFile[iii]`

```{r}
names(xmlData)
xmlData$LawNum
names(xmlData$LawBody)
xmlData$LawBody$LawTitle
names(xmlData$LawBody$TOC)
xmlData$LawBody$TOC$TOCLabel
names(xmlData$LawBody$TOC$TOCChapter)
xmlData$LawBody$TOC$TOCChapter$ChapterTitle
xmlData$LawBody$TOC$TOCChapter$ArticleRange
names(xmlData$LawBody$TOC$TOCSupplProvision)
xmlData$LawBody$TOC$TOCSupplProvision$SupplProvisionLabel
names(xmlData$LawBody$MainProvision)
names(xmlData$LawBody$MainProvision$Chapter)
xmlData$LawBody$MainProvision$Chapter$ChapterTitle
names(xmlData$LawBody$MainProvision$Chapter$Article)
xmlData$LawBody$MainProvision$Chapter$Article$ArticleCaption
xmlData$LawBody$MainProvision$Chapter$Article$ArticleTitle
names(xmlData$LawBody$MainProvision$Chapter$Article$Paragraph)
xmlData$LawBody$MainProvision$Chapter$Article$Paragraph$ParagraphNum
names(xmlData$LawBody$MainProvision$Chapter$Article$Paragraph$ParagraphSentence)
names(xmlData$LawBody$MainProvision$Chapter$Article$Paragraph$ParagraphSentence$Sentence)
xmlData$LawBody$MainProvision$Chapter$Article$Paragraph$ParagraphSentence$Sentence$text
names(xmlData$LawBody$SupplProvision)
xmlData$LawBody$SupplProvision$SupplProvisionLabel
names(xmlData$LawBody$SupplProvision$Article)
xmlData$LawBody$SupplProvision$Article$ArticleTitle
names(xmlData$LawBody$SupplProvision$Article$Paragraph)
xmlData$LawBody$SupplProvision$Article$Paragraph$ParagraphNum
names(xmlData$LawBody$SupplProvision$Article$Paragraph$ParagraphSentence)
names(xmlData$LawBody$SupplProvision$Article$Paragraph$ParagraphSentence$Sentence)
xmlData$LawBody$SupplProvision$Article$Paragraph$ParagraphSentence$Sentence$text
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fun_updateURLcsv()
```

<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
