---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');htmlName<-'IndexYearlyVariation';rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-',htmlName,'.html')) })

title : "Historical Data Of Financial Indices:Yearly Variation Since the Beginning of the Year"
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 5
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<style>.main-container {max-width : 1000px;}</style>
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000)
```

```{r warning = F, error = F, message = F, echo = F}
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    RCurl::getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r warning=F, error=F, message=F, echo=F,results='hide'}
fun_plot_tsDataByYear <- 
  function(obj,startYear = 2010,varType = 1,pch = 20,cex = 1){
    dataSet <- fun_tsDataByYear(objDF = obj)
    obj0 <- dataSet$cbindData1
    lastDate <-
      tail(na.omit(dataSet$cbindData0[,grep(year(Sys.Date()),colnames(dataSet$cbindData0))-1]),1)
    if(varType == 1){
      obj1 <- apply(obj0,2,function(x)(na.omit(x)/head(x,1)-1)*100)
      variation <- 'Variation(%)'
    }else{
      obj1 <- apply(obj0,2,function(x)na.omit(x)-head(x,1))
      variation <- 'Variation(Difference)'
    }
    strawData <- Reduce(function(x,y){qpcR:::cbind.na(x, y)},obj1)
    colnames(strawData) <- colnames(obj0)
    objCol <- grep(startYear,colnames(strawData))
    ylim <- 
      c(min(strawData[,objCol:ncol(strawData)],na.rm = T),
        max(strawData[,objCol:ncol(strawData)],na.rm = T))
    dateFormat <- 
      ifelse(12<nrow(strawData),'%Y-%m-%d','%Y-%m')
    for(ccc in objCol:ncol(strawData)){
      par(family = 'Meiryo',font.main = 1,mar = c(5,3,3,1),cex.main = 1.1)
      obj <- strawData[,ccc,drop=F]
      if(ccc == objCol){
        plot(obj,
             ylim = ylim,
             xlab = ifelse(12<nrow(obj),'Day','Month'),
             ylab = '',
             panel.first = grid(nx = NULL,ny = NULL,lty = 2,equilogs = T),
             pch = pch,
             cex = cex,
             type = ifelse(12<nrow(obj),'l','o'),
             main = paste0(gsub('(.+):([0-9]+)','\\1',colnames(obj)),
                           ':',variation,'. Last:',format(x = lastDate,dateFormat)),
             col = ifelse(ccc%%2 == 1,'blue','black'))
      }else{
        lines(obj,
              xaxt = 'n',
              yaxt = 'n',
              xlab = '',
              ylab = '',
              pch = pch,
              cex = cex,
              col = ifelse(ccc==ncol(strawData),'red',ifelse(ccc%%2 == 1,'blue','black')),
              lwd = ifelse(ccc==ncol(strawData),2,1),
              type = ifelse(12<nrow(obj),'l','o'))
      }
      text(x = tail(index(na.omit(obj)),1),
           y = tail(na.omit(obj),1),
           labels = gsub('.+:([0-9]+)','\\1',colnames(obj)),
           col = ifelse(ccc == ncol(strawData),'red',ifelse(ccc%%2 == 1,'blue','black')),
           cex = ifelse(ccc == ncol(strawData),1.5,1.0),
           adj = 1,
           font = 4)
    }
    abline(h = 0,col = 'black',lwd = 2)
    returnResult <-
      list("cbindData0" = dataSet$cbindData0, 
           "cbindData1" = dataSet$cbindData1,
           'strawData' = strawData)
    return(returnResult)
  }
```

```{r,warning=F,error=F,message=F,results='hold',echo=F}
options(scipen = 999)
dateFormat <- '%Y-%m-%d'
dataTitle <- 
  paste0('Historical Data Of Financial Indices:Yearly Variation Since the Beginning of the Year')
dataSource <- 
  'Federal Reserve Bank of St. Louis'
windowsFonts(Meiryo=windowsFont("Meiryo"))
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`

***

#### Yearly Variation Since the Beginning of the Year

```{r warning=F, error=F, message=F, echo=F,results='asis'}
library(quantmod);library(lubridate)
timeSeriesData <- 
  c('DEXJPUS','USD/JPY',1,
    'DEXUSEU','EUR/USD',1,
    'DEXCHUS','USD/CNY',1,
    'DEXUSUK','GBP/USD',1,
    'DEXUSAL','AUD/USD',1,
    'DEXSFUS','USD/ZAR',1,
    'VIXCLS','CBOE Volatility Index',1,
    'NIKKEI225','NIKKEI225',1,
    'DJIA','Dow Jones Industrial Average',1,
    'UNRATE','Civilian Unemployment Rate',0,
    'DTWEXB','Trade Weighted U.S. Dollar Index: Broad',1,
    'DTWEXM','Trade Weighted U.S. Dollar Index: Major Currencies',1,
    'DGS10','10-Year Treasury Constant Maturity Rate',0,
    'CPIAUCSL','Consumer Price Index for All Urban Consumers: All Items',0)
for(iii in seq(1,length(timeSeriesData),by = 3)){
  tmp <- 
    getSymbols(timeSeriesData[iii], src = 'FRED', auto.assign = F)
  buf <-
    na.omit(data.frame(Date = as.Date(index(tmp)),
                       tmp,
                       stringsAsFactors = F,
                       check.names = F,
                       row.names = NULL))
  colnames(buf)[2] <- timeSeriesData[iii+1]
  cat('- ',timeSeriesData[iii+1],'\n')
  returnResult <- 
    fun_plot_tsDataByYear(obj = buf,
                          startYear = 2013,
                          varType = timeSeriesData[iii+2],
                          cex = 1.8)
  cat('\n<hr>\n')
}
```

```{r warning=F, error=F, message=F, echo=F,results='hide'}
# Reduce 挙動確認チャンク
objCol <- c(2,4,6)
test <- list()
test[[3]] <- returnResult$cbindData0[,objCol[1]]
test[[1]] <- returnResult$cbindData0[,objCol[2]]
test[[2]] <- returnResult$cbindData0[,objCol[3]]
head(Reduce(function(x,y){qpcR:::cbind.na(x, y)},test),3)
head(returnResult$cbindData0[,objCol],3)
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
username <-
  Sys.info()['user']
pathToFile <-
  paste0('C:/Users/', username,'/Desktop/pathToCSV/')
setwd(pathToFile)
fileName <-
  'defaultPath.csv'
buf <-
  read.csv(file = fileName,
           header = F,
           skip = 0,
           stringsAsFactor = F,
           check.names = F,
           fileEncoding = 'utf-8',quote = "\"")
pathOutputTOcsv <-
  paste0("C:/Users/", username, buf[2,1],'charts/chartImages/')
setwd(pathOutputTOcsv)
getwd()
par(family = 'Meiryo')
pngFile <-
  paste0(htmlName, ".png")
png(file = pngFile, width = 1000, height = 600)
##################
script <-
  RCurl::getURL(
    "https://raw.githubusercontent.com/am-consulting/Rscript/master/Rscript_JGBInterestRate.r",
    ssl.verifypeer = F
  )
eval(parse(text = script))
jgbData0 <- na.omit(jgbData)
colnames(jgbData0)[-1] <- paste0('JGB:',colnames(jgbData0)[-1])
iii <- 11
returnResult <- 
  fun_plot_tsDataByYear(obj = jgbData0[,c(1,iii)],
                        startYear = 2013,
                        varType = 0)
dev.off()
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fun_outputMD(tags = '金融指標',
             objDF = tail(jgbData0[,c(1,3,11,16)],10),
             htmlName = htmlName,
             image = 1,
             dataTitle = dataTitle,
             tableTitle = '直近10日分',
             tableName = '日本国債最終利回り(%)')
```

<script>MakeNegative()</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
