---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');htmlName<-'NEET';rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-',htmlName,'.html')) })

title : "Youth not in employment, education or training(NEET)"
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 5
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<style>.main-container {max-width : 1000px;}</style>
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000)
```

```{r warning = F, error = F, message = F, echo = F}
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    RCurl::getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r warning=F, error=F, message=F, echo=F,results='hide'}
library(countrycode)
username <- 
  Sys.info()['user']
pathOutput <- 
  paste0("C:/Users/", username, "/Desktop/R_Data_Write/")
setwd(pathOutput)
fileName <- dir(pathOutput)[grep('DP_LIVE.+\\.csv',dir(pathOutput),ignore.case = T)]
tmp0 <-
  read.csv(file = fileName,header = T,check.names = F,stringsAsFactors = F)
tmp1 <- tmp0
colnames(tmp1)[1] <- 
  gsub('.+(location)','\\1',colnames(tmp1)[1],ignore.case = T)
tmp1$Country <- 
  countrycode(tmp1$LOCATION,'iso3c','country.name')
tmp1$Country[which(is.na(tmp1$Country))] <- 
  tmp1$LOCATION[which(is.na(tmp1$Country))]
tmp1$Date <- 
  as.Date(paste0(tmp1$TIME,'-1-1'))
indicator <- unique(tmp1$INDICATOR)
measure <- unique(tmp1$MEASURE)
location <- unique(tmp1$LOCATION)
unique(tmp1$SUBJECT)
dataSet <- tmp1
```

```{r,warning=F,error=F,message=F,results='hold',echo=F}
options(scipen = 999)
JapanData <- 
  dataSet[grep('japan',dataSet$Country,ignore.case = T),]
JapanData <- JapanData[max(JapanData$Date)==JapanData$Date,]
JapanData <- JapanData[JapanData$SUBJECT=="15_29",]
dataTitle <- 
  paste0('NEET率:日本:',JapanData$TIME,'年:',JapanData$SUBJECT,'歳:',round(JapanData$Value,2),'%')
dataSource <- 'Organisation for Economic Co-operation and Development'
windowsFonts(Meiryo = windowsFont("Meiryo"))
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- Source https://data.oecd.org/youthinac/youth-not-in-employment-education-or-training-neet.htm

***

#### 各国のニート率:15歳から29歳

```{r warning=F, error=F, message=F, echo=F,results='asis'}
objSubject <- '15_29'
par(mfrow = c(1,1),font.main = 1,cex.main = 1,family = 'Meiryo')
for(iii in seq(length(location))){
  obj <- subset(dataSet,location[iii]==dataSet$LOCATION)
  obj <- subset(obj,objSubject==obj$SUBJECT)
  if(5 <= nrow(obj)){
    cat('#### ',unique(obj$Country),'\n')
    plot(x = obj$Date,
         y = obj$Value,
         type = 'o',
         pch = 20,
         cex = 2,
         xlab = '',
         ylab = '',
         xaxt = 'n',
         panel.first = grid(nx = NULL,ny = NULL,lty = 2,equilogs = T),
         main = paste0(indicator,'\n',
                       paste0(format(range(obj$Date),'%Y'),collapse = '~'),'\n',
                       unique(obj$Country),':',measure,':',objSubject))
    axis.Date(side = 1,at = obj$Date,format = '%Y',padj = 0.5,cex.axis = 1,las=2)
    abline(lm(obj$Value~obj$Date),col='red',lwd=2)
    cat('\n<hr>\n')
  }
}
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fun_preparePlot()
pngFile <- paste0(htmlName, "1.png")
png(file = pngFile, width = 1000, height = 600)
obj <- 
  dataSet[grep('japan',dataSet$Country,ignore.case = T),]
obj <- obj[obj$SUBJECT=="20_24",]
obj <- obj[,c(10,7,3,9)]
colnames(obj)[2] <- 'NEET率(%)'
fun_plotTimeSeries(obj = obj[,c(1,2)],dateFormat = '%Y年',
                   chartType = 0,typeL = 'o',
                   dataTitle = paste0(unique(obj$Country),':',unique(obj$SUBJECT),'歳'),
                   dataSource = dataSource,mar = c(4,5,6,2),fitLcolor = 2,cexL = 2)
dev.off()
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
objSubject <- '15_29'
for(iii in seq(length(location))){
  obj <- subset(dataSet,location[iii]==dataSet$LOCATION)
  obj <- subset(obj,objSubject==obj$SUBJECT)
  obj <- obj[which.max(obj$TIME),]
  if(iii==1){objDF <- obj}else{objDF <- rbind(objDF,obj)}
}
obj <- objDF[,c(9,6,7,3)]
obj[,3] <- round(obj[,3],2)
obj <- obj[order(obj$Value,decreasing = T),]
obj[,2] <- paste0(obj[,2],'年')
fun_outputMD(tags = 'OECD,NEET',
             objDF = obj[,-4],
             htmlName = htmlName,
             image1 = 1,
             dataTitle = dataTitle,
             tableTitle = paste0(unique(obj$SUBJECT),'歳'),
             tableName = 'Youth not in employment, education or training(NEET)')
fun_updateURLcsv()
```

<script>MakeNegative()</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
