---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-DOW.html')) })

title : 'Dow Jones Industrial Average, Its Historical Volatility and Change since United States presidential election, 2016'
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 5
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<style>.main-container {max-width : 1000px;}</style>
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000,scipen = 999)
```

```{r warning=F, error=F, message=F, echo=F, results='hide'}
windowsFonts(Meiryo = windowsFont("Meiryo"))
library(quantmod)
```

```{r warning=F, error=F, message=F, echo=F, results='hide'}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", functionList[iii,1]),
    ssl.verifypeer = F
  )
  eval(parse(text = script))
}
```

```{r warning=F, error=F, message=F, echo=F, results='hide'}
script <-
  getURL("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/importDOW30.r",
         ssl.verifypeer = F)
eval(parse(text = script))
```

```{r warning=F, error=F, message=F, results='hide', echo=F}
dateFormat <- '%Y-%m-%d'
DJI <- getSymbols(Symbols = '^DJI',auto.assign = F)
DJIDF <-
  data.frame(Date = index(DJI),DJI,stringsAsFactors = F,check.names = F,row.names = NULL)
fun_latestResult(obj = DJIDF,objColumn = 5,dateFormat = dateFormat)
dataTitle <-
  paste0('Dow Jones Industrial Average:',latestResult)
dataSource <-
  'Yahoo Finance'
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- Source http://finance.yahoo.com/

***

```{r warning=F, error=F, message=F, echo=F, results='hide'}
fun_historicalVolatility <- 
  function(obj, objColumn = 2, width = 30){
    HV <- vector()
    for(rrr in width:nrow(obj)){
      tmp <- 
        obj[c((rrr-width+1):rrr),c(1,objColumn)]
      fun_makeDiffRatioTable(obj = tmp,lag = 1,roundDigits = 3)
      HV[rrr] <- sd(diffRatioDF[,2]/100) * sqrt(260) * 100
    }
    assign('historicalVolatility',
           data.frame(Date = tail(obj[,1],-(width-1)),
                      `HistoricalVolatility(%)` = na.omit(HV),
                      stringsAsFactors = F,
                      check.names = F),
           envir = .GlobalEnv)
  }
```

#### Dow Jones Industrial Average

- `r width <- 30;paste0('Historical Volatility:Width = ',width)`

```{r warning=F, error=F, message=F, echo=F, results='asis'}
tailN <- 20*5
cat(paste0('<div align="center"><h5><b>Dow Jones Industrial Average</b></h5></div>'))
chartSeries(x = tail(DJI,tailN),
            type = 'candlesticks',
            name = 'Dow Jones Industrial Average',
            show.grid = T)
cat('<hr>')
obj <- DJI
objColumn <- 7
objDF <-
  data.frame(Date = index(obj),obj,stringsAsFactors = F,check.names = F,row.names = NULL)
fun_historicalVolatility(obj = objDF,objColumn = objColumn,width = width)
mergeData <- merge(historicalVolatility,objDF,by='Date')
objYR <- grep(colnames(objDF)[objColumn],colnames(mergeData))
fun_plotTimeSeries(obj = mergeData,
                   objYL = 2,
                   objYR = objYR,
                   chartType = 2,
                   lwdL = 1,
                   lwdR = 1,
                   dataSource = dataSource,
                   mar = c(3,4.5,4,4.5))
abline(v = as.numeric(as.Date('2016-11-8')),col='red',lty=2)
text(x = as.numeric(as.Date('2016-11-8')),
     y = median(mergeData[,objYR]),
     labels = 'United States presidential election, 2016',
     pos = 2)
cat('<hr>')
cat(paste0('<div align="center"><h5><b>Since United States presidential election, 2016</b></h5></div>'))
sinceTrump <-
  rbind(subset(objDF,objDF[,1] == as.Date('2016-11-8')),tail(objDF,1))
fun_transposeDataFrame(obj = sinceTrump)
fun_markdownTable(obj = data.frame(tDF,
                                   `Change(%)`=round((tDF[,3]/tDF[,2]-1)*100,1),
                                   stringsAsFactors = F,
                                   check.names = F))
```

***
#### By Company

- `r paste0('Historical Volatility:Width = ',width)`

```{r warning=F, error=F, message=F, echo=F, results='asis'}
tailN <- 20*5
for(iii in 1:length(dow30symbols)){
  cat(paste0('<div align="center"><h5><b>',dow30company[iii],'</b></h5></div>'))
  chartSeries(x = tail(symbolsDOW30[[iii]],tailN),
              type = 'candlesticks',
              name = dow30company[iii],
              show.grid = T)
  cat('<hr>')
  obj <- symbolsDOW30[[iii]]
  objDF <-
    data.frame(Date = index(obj),obj,stringsAsFactors = F,check.names = F,row.names = NULL)
  fun_historicalVolatility(obj = objDF,objColumn = objColumn)
  mergeData <- merge(historicalVolatility,objDF,by='Date')
  objYR <- grep(colnames(objDF)[objColumn],colnames(mergeData))
  fun_plotTimeSeries(obj = mergeData,
                     objYL = 2,
                     objYR = objYR,
                     chartType = 2,
                     lwdL = 1,
                     lwdR = 1,
                     dataSource = dataSource,
                     mar = c(3,4.5,4,4.5))
  abline(v = as.numeric(as.Date('2016-11-8')),col='red',lty=2)
  text(x = as.numeric(as.Date('2016-11-8')),
       y = median(mergeData[,objYR]),
       labels = 'United States presidential election, 2016',
       pos = 2)
  cat('<hr>')
  cat(paste0('<div align="center"><h5><b>Since United States presidential election, 2016</b></h5></div>'))
  sinceTrump <-
    rbind(subset(objDF,objDF[,1] == as.Date('2016-11-8')),tail(objDF,1))
  fun_transposeDataFrame(obj = sinceTrump)
  fun_markdownTable(obj = data.frame(tDF,
                                     `Change(%)`=round((tDF[,3]/tDF[,2]-1)*100,1),
                                     stringsAsFactors = F,
                                     check.names = F))
}
```

***
<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
