---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');htmlName<-'EPU';rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-',htmlName,'.html')) })

title : 'Economic Policy Uncertainty'
author: 'アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp'
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 4
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 1000px;}</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000)
```

```{r warning = F, error = F, message = F, echo = F}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r warning=F,error=F,message=F,echo=F}
library(RCurl);library(knitr)
script <-
  getURL("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/importEPU.r",
         ssl.verifypeer = F)
eval(parse(text = script))
```

```{r warning=F,error=F,message=F,results='hold',echo=F}
dateFormat <- '%Y-%m'
dataTitle <- 
  paste0("Economic Policy Uncertainty Index:",format(tail(EPUallData[,1],1),dateFormat))
dataSource <- "Economic Policy Uncertainty,Federal Reserve Bank of St. Louis"
windowsFonts(Meiryo = windowsFont("Meiryo"))
options(scipen = 999)
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- http://www.policyuncertainty.com/index.html

***

```{r warning=F, error=F, message=F, echo=F, results='asis'}
obj <- EPUallData[,c(1,2,3,4)]
n <- 1
fun_generateKnit(objDF = obj,plotNum = n,group = 0,
                 dygraphTitle = paste0(gsub('.+index for\\s(.+)','\\1',colnames(EPUallData)[2:4],
                                            ignore.case = T),collapse = ' × '))
eval(parse(text = paste0('dygraphPlot', n)))
```

***

#### Economic Policy Uncertainty Index
- Original

```{r warning=F, error=F, message=F, echo=F, results='asis'}
tDF <-
  fun_transposeDataFrame(obj = EPUallData,dateFormat = dateFormat,colName = 'Country/Region',tailN = 5)
tDF <-
  tDF[order(tDF[,ncol(tDF)],decreasing = T),]
fun_markdownTable(obj = tDF)
```

***
- Month Over Month(%)

```{r warning=F, error=F, message=F, echo=F, results='asis'}
diffRatioDF <- fun_makeDiffRatioTable(obj = EPUallData,lag = 1)
tDF <-
  fun_transposeDataFrame(obj = diffRatioDF,dateFormat = dateFormat,colName = 'Country/Region',tailN = 5)
tDF <-
  tDF[order(tDF[,ncol(tDF)],decreasing = T),]
fun_markdownTable(obj = tDF)
```

***

#### Economic Policy Uncertainty Index:Japan

```{r warning=F, error=F, message=F, echo=F, results='asis'}
obj <- 
  EPUallData[,c(1,grep('japan',colnames(EPUallData),ignore.case = T))]
fittedDF <- fun_fit(obj = obj)
n <- 2
fun_generateKnit(objDF = fittedDF[,-5],plotNum = n,group = 0)
eval(parse(text = paste0('dygraphPlot', n, ' %>% ', ConsumptionTax)))
cat('<hr>')
eval(parse(text = paste0('dygraphPlot', n, ' %>% ', primeMinisterOfJapan_dygraph)))
cat('<hr>')
eval(parse(text = paste0('dygraphPlot', n, ' %>% ', boj_dygraph)))
cat('<hr>')
eval(parse(text = paste0('dygraphPlot', n, ' %>% ', event_dygraph_point,' %>%  ',event_dygraph_range)))
```

***
<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
