---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-operationBOJdefinitePeriod.html')) })
title : "Operation of Bank of Japan:Definite Period"
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 5
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<style>.main-container {max-width : 1000px;}</style>
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>


```{r set-options, echo=F, cache=F}
# ―,ソ,噂,欺,圭,構,蚕,十,申,貼,能,表,暴,予,禄,兔
options(width = 1000)
```

```{r warning = F, error = F, message = F, echo = F}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r warning=F,error=F,message=F,echo=F}
library(RCurl)
script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/importBojOperationHistory.r",
    ssl.verifypeer = F
  )
eval(parse(text = script))
```

```{r warning=F,error=F,message=F,echo=F}
fun_bojOperationHistory(stopMonth = 11)
```

```{r warning=F,error=F,message=F,echo=F}
library(XLConnect);library(lubridate);library(Nippon)
username <- 
  Sys.info()['user']
pathOutput <- 
  paste0("C:/Users/", username, "/Desktop/R_Data_Write/")
setwd(pathOutput)
baseURL <- 
  "http://www.boj.or.jp/statistics/boj/fm/ope/m_release/"
YearFolder <- 
  2016
fileName <- 
  'ope1612.xlsx'
download.file(url = paste0(baseURL,YearFolder,'/',fileName), destfile = fileName, mode = 'wb')
buf0 <-
  readWorksheetFromFile(paste0(pathOutput, fileName), sheet = 2, check.names = F, header = F)
```

```{r warning=F,error=F,message=F,echo=F}
keyWord <- '実行日'
bufR <- which(apply(buf0,1,function(x){(length(grep(keyWord,x)))})!=0)
colnames(buf0) <- gsub('\\W','',buf0[bufR,])
buf1 <- buf0[-c(1:bufR),]
keyWord <- '種類'
bufC <- which(colnames(buf1)==keyWord)
buf2 <- buf1[!is.na(buf1[,bufC]),]
yy <- unique(year(buf2[,1]))
mm <- unique(month(buf2[,1]))
keyWord <- '落札額'
bufC <- which(colnames(buf2)==keyWord)
buf2[,bufC] <- as.numeric(gsub(',','',buf2[, bufC]))
attach(buf2)
keyWord <- '種類'
opeTable <- cbind(by(buf2[,bufC],`種類`,sum))
opeTable <- data.frame(row.names(opeTable),opeTable,check.names = F,stringsAsFactors = F,row.names = NULL)
opeTable[,1] <- sapply(opeTable[,1],zen2han)
opeTable <- 
  rbind(opeTable,c('合計',sum(opeTable[,2])))
colnames(opeTable) <- 
  c(colnames(totalOpeTable)[1],paste0(yy,'年',mm,'月'))
totalOpeTable <-
  merge(totalOpeTable,opeTable,by='種類/落札額(億円)',all=T)
totalOpeTable <-
  rbind(totalOpeTable[-grep('合計',totalOpeTable[,1]),],totalOpeTable[3,])
totalOpeTable[,-1] <- 
  apply(totalOpeTable[,-1],2,as.numeric)
```

```{r warning=F,error=F,message=F,echo=F,results='hold'}
dataTitle <- paste0('日本銀行年間オペレーション:2016年')
dataSource <- '日本銀行'
windowsFonts(Meiryo=windowsFont("Meiryo"))
options(scipen = 999)
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- http://www.boj.or.jp/statistics/boj/fm/ope/m_release/index.htm/

***

```{r warning=F,error=F,message=F,echo=F,results='asis'}
totalDF <-
  data.frame(totalOpeTable,
             `合計` = apply(totalOpeTable[,-1],1,function(x)sum(x,na.rm = T)),
             check.names = F,
             stringsAsFactors = F,
             row.names = NULL)
fun_dataTable(obj = totalDF, dateFormat = 0, orderDirection = 'asc', leftcolumns = 2,needID = 1)
cat('\n<hr>\n')
sumTotalOpeTable <-
  data.frame(totalOpeTable[,1],
             apply(totalOpeTable[,-1],1,function(x)sum(x,na.rm = T)),
             stringsAsFactors = F,
             check.names = F,
             row.names = NULL)
sumTotalOpeTable$ratio <-
  round(sumTotalOpeTable[,2]/sumTotalOpeTable[grep('合計',sumTotalOpeTable[,1]),2]*100,2)
colnames(sumTotalOpeTable) <- 
  c('種類','落札額合計(億円):2016年','構成比(%)')
fun_markdownTable(obj = sumTotalOpeTable)
cat('\n<hr>\n')
sumTotalJGB <-
  sumTotalOpeTable[grep('国債買入',sumTotalOpeTable[,1]),-3]
sumTotalJGB <-
  rbind(sumTotalJGB,c('合計',sum(sumTotalJGB[,2])))
sumTotalJGB[,-1] <- 
  apply(sumTotalJGB[,-1,drop=F],2,as.numeric)
sumTotalJGB$`構成比(%)` <-
  round(as.vector(sumTotalJGB[,2])/sumTotalJGB[grep('合計',sumTotalJGB[,1]),2]*100,2)
fun_markdownTable(obj = sumTotalJGB)
cat('\n<hr>\n')
sumTotalETF <-
  sumTotalOpeTable[grep('指数連動型',sumTotalOpeTable[,1]),]
sumTotalETF <-
  rbind(sumTotalETF,c('合計',sum(sumTotalETF[,2])))
sumTotalETF[,-1] <- 
  apply(sumTotalETF[,-1,drop=F],2,as.numeric)
sumTotalETF$`構成比(%)` <-
  round(as.vector(sumTotalETF[,2])/sumTotalETF[grep('合計',sumTotalETF[,1]),2]*100,2)
fun_markdownTable(obj = sumTotalETF)
```

***
<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
