---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');htmlName<-'DepositsByPrefecture';rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-',htmlName,'.html')) })

title : 'Deposits, Vault Cash, and Loans and Bills Discounted by Prefecture(Domestically Licensed Banks)'
author: 'アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp'
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 5
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 1000px;}</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000)
```

```{r warning = F, error = F, message = F, echo = F}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/importDepositsByPrefecture.r",
    ssl.verifypeer = FALSE
  )
eval(parse(text = script))
```

```{r warning=F,error=F,message=F,results='hold',echo=F}
dateFormat <- '%Y年%m月'
latestResult <-
  paste0(sheetTitle[1],':',tail(DepositsByPrefecture[[1]],1)[,1],':',
         tail(DepositsByPrefecture[[1]],1)[,2]*10^-4,'(兆円)')
dataTitle <- latestResult
dataSource <- "日本銀行"
windowsFonts(Meiryo = windowsFont("Meiryo"))
options(scipen = 999)
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- Source : http://www.boj.or.jp/statistics/dl/depo/pref/index.htm/

***

#### 直近の状況

```{r warning=F,error=F,message=F,echo=F,results='asis'}
objList <- 1
obj <- DepositsByPrefecture[[objList]][,c(1,2,11,12,15)]
fun_dataTable(obj = obj,dateFormat = 0,needID = 1,orderDirection = 'asc',title = sheetTitle[objList])
```

***

```{r warning=F,error=F,message=F,echo=F,results='asis'}
for(iii in seq(length(DepositsByPrefecture))){
  obj0 <- DepositsByPrefecture[[iii]]
  obj1 <- obj0[grep('全国計|東京',obj0[,1]),c(1,2,15)]
  obj1$Date <- as.Date(gsub('.+<([0-9]+)年([0-9]+)月末>','\\1-\\2-1',sheetTitle[iii]))
  if(iii == 1){timeSeriesData <- obj1}else{timeSeriesData <- rbind(timeSeriesData,obj1)}
}
tsData <- timeSeriesData[timeSeriesData[,1]=='全国計',]
fun_plotTimeSeries(obj = tsData,objX = 4,objYL = 2,objYR = 3,
                   typeL = 'o',typeR = 'o',dateFormat = dateFormat,
                   chartType = 2,dataTitle = paste0(dataTitle,':全国計'),
                   dataSource = dataSource,fitLcolor = 0,fitRcolor = 0,cexL = 2.5,cexR = 2.5)
cat('<hr>\n')
for(iii in seq(length(DepositsByPrefecture))){
  obj0 <- DepositsByPrefecture[[iii]]
  obj1 <- obj0[grep('計',obj0[,1]),c(1,2,11,12,15)]
  cat(paste0('<b>',sheetTitle[iii],'</b>\n'))
  fun_markdownTable(obj = obj1)
  cat('<hr>\n')
}
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
username <-
  Sys.info()['user']
pathToFile <-
  paste0('C:/Users/', username,'/Desktop/pathToCSV/')
setwd(pathToFile)
fileName <-
  'defaultPath.csv'
buf <-
  read.csv(file = fileName,
           header = F,
           skip = 0,
           stringsAsFactor = F,
           check.names = F,
           fileEncoding = 'utf-8',quote = "\"")
pathOutputTOcsv <-
  paste0("C:/Users/", username, buf[2,1],'charts/chartImages/')
setwd(pathOutputTOcsv)
getwd()
par(family = 'Meiryo')
pngFile <-
  paste0(htmlName, ".png")
png(file = pngFile, width = 1000, height = 600)
##################
tsData <- timeSeriesData[timeSeriesData[,1]=='東京',]
fun_plotTimeSeries(obj = tsData,objX = 4,objYL = 2,objYR = 3,
                   typeL = 'o',typeR = 'o',dateFormat = dateFormat,
                   chartType = 2,dataTitle = paste0(dataTitle,':東京'),
                   dataSource = dataSource,fitLcolor = 0,fitRcolor = 0,cexL = 2.5,cexR = 2.5)
dev.off()
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
objList <- 1
obj <- DepositsByPrefecture[[objList]][,c(1,2,11,12,15)]
fun_outputMD(tags = '日本銀行,都道府県別預金・現金・貸出金(国内銀行)',
             objDF = obj,
             htmlName = htmlName,
             image = 1,
             dataTitle = dataTitle,
             tableTitle = sheetTitle[objList])
```

<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
