---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-2016NationalPopularVoteTracker.html')) })
title : "2016 National Popular Vote Tracker.Source:THE COOK POLITICAL REPORT"
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 5
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet"> 
<style>
.main-container {
	max-width: 1100px;
	margin-left: auto;
	margin-right: auto;
}

table{
 white-space: nowrap;
}
</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan

本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r warning = F, error = F, message = F, echo = F, results = 'hold'}
dataTitle <- '2016 National Popular Vote Tracker.Source:THE COOK POLITICAL REPORT / 2016年アメリカ大統領選挙一般投票の結果と各州の寄与度'
Author <- "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
cat(paste("Title  : ", dataTitle, "\n"))
cat(paste("Author : ", Author, "\n"))
windowsFonts(Meiryo = windowsFont("Meiryo"))
```

Source:

- http://cookpolitical.com/story/10174
- Updated 11-26-16

Notes:

- "Clinton - Trump":The number of votes for Hillary Clinton minus the number of votes for Donald Trump.
- "Contribution Ratio(%)":"Clinton - Trump" for each states / "Clinton - Trump" for U.S. Total × 100
- "Clinton - Trump":ヒラリー・クリントン氏への投票数からドナルド・トランプ氏への投票数を引いた投票数差。
- "Contribution Ratio(%)":それぞれの州の上記投票数差をアメリカ全体の投票数差で除して100を掛けた寄与度。

```{r warning = F, error = F, message = F, echo = F}
library(excel.link)
fileName <- 'defaultPath.csv'
username <- Sys.info()['user']
pathToFile <- paste0('C:/Users/', username, '/Desktop/pathToCSV/')
setwd(pathToFile)
buf000 <- read.csv(fileName,header = F, skip = 0, stringsAsFactor = F, check.names = F, fileEncoding = 'utf-8')
pathOutput <- paste0("C:/Users/", username, buf000[3, 1])
setwd(pathOutput)
fileName <- dir(pathOutput)[grep('presidential_results_2016', dir(pathOutput))]
tmp <- xl.read.file(fileName, header=T, top.left.cell = "A1", xl.sheet = 2, excel.visible = F)
tmp[, ncol(tmp)] <- apply(tmp[, ncol(tmp), drop = F], 2, function(x) round(x, 2))
tmp[,2] <- gsub('\\*','',tmp[,2])
NationalPopularVoteTracker2016 <- tmp
```

***

```{r warning = F, error = F, message = F, echo = F, results = 'asis'}
funDataTable <- 
  function(obj, orderColumn = 0, orderDirection = 'asc', width00 = '3%', caption = '', dataTitle='',title='',append='') {
  cat(paste('<h4>', dataTitle, '</h4>'))  
  DT::datatable(
    obj,
    extensions = c("Buttons", "ColReorder" , "FixedColumns", "FixedHeader"),
    options = list(paging = T, autoWidth = F, info = T, lengthChange = T, ordering = T,
      searching = T, scrollX = T, lengthMenu = list(c(15,-1), c(15,'All')),
      orderClasses = T, order = list(list(orderColumn, orderDirection)), 
      search = list(regex = T, caseInsensitive = T), searchHighlight = T,
      columnDefs = list(list(width = width00, targets = 0)),
      dom = 'BRlfrtip', buttons = I('colvis'), colReorder = T, fixedHeader = T, fixedColumns = list(leftColumns = 2)),
    rownames = F, class = 'display compact', escape = F, filter = 'top', 
    caption = caption
    # caption = htmltools::tags$caption(style = 'caption-side: bottom; text-align: center;','Table ', htmltools::em(caption))
  )  
  }

funDataTable(obj = NationalPopularVoteTracker2016, dataTitle = dataTitle)
```

***

<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
