---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y-%m-%d %H:%M:%S');htmlName<-'00005';rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-',htmlName,'.html')) })

title : 'Time Series Analysis'
output: 
  html_document:
    fig_height: 4
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
    toc: true
    toc_depth: 6
    number_section: false
    toc_float:
      collapsed: false
      smooth_scroll: false
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 1000px;}</style>
<style>
*{-webkit-text-size-adjust: 100%;}
h1{font-size:6vw;font-weight: bold;}
h2{font-size:5vw;font-weight: bold;}
h3{font-size:4vw;font-weight: bold;}
h4{font-size:3vw;font-weight: bold;}
h5{font-size:2vw;font-weight: bold;}
h6{font-size:1vw;font-weight: bold;}
@media(min-width:500px){
  h1{font-size:1.6em;font-weight: bold;}
  h2{font-size:1.3em;font-weight: bold;}
  h3{font-size:1.1em;font-weight: bold;}
  h4{font-size:1.0em;font-weight: bold;}
  h5{font-size:0.9em;font-weight: bold;}
  h6{font-size:0.8em;font-weight: bold;}
}
</style>

# Title,Timestamp,Source etc.
- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- `r timeStamp`
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options,echo=F,cache=F}
options(width = 1000,scipen = 999)
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
windowsFonts(Meiryo = windowsFont("Meiryo"))
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fileName <- 
  'functionList.csv'
baseURL <- 
  'https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/'
functionList <- 
  read.csv(
    file = paste0(baseURL,'csv/',fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    RCurl::getURL(paste0(baseURL,functionList[iii,1]),ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fun_billToTri <- function(obj,dateCol = 1,valueCol = 2){
  obj <- 
    data.frame(obj[,dateCol,drop=F],apply(obj[,valueCol,drop=F],2,function(x)x*10^-4),
               stringsAsFactors = F,check.names = F,row.names = NULL)
  colnames(obj)[2] <- Nippon::zen2han(gsub('億円','兆円',colnames(obj)[2]))
  obj <- na.omit(obj)
  row.names(obj) <- NULL
  return(obj)
}
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
if(htmlName=='00001'){
  importData <- c('importMonetarybaseOfJapan-2017.r')
  script <-
    RCurl::getURL(paste0(baseURL,importData[1]),ssl.verifypeer = FALSE)
  eval(parse(text = script))
  buf <- monetaryBase_Japan
  colnames(buf) <-
    gsub('[^:]+:(.+)','\\1',colnames(buf))
  obj <- fun_billToTri(obj = buf,valueCol = 6)
  fun_latestResult(obj = obj)
  dataTitle <- 
    paste0("マネタリーベース:日本:",latestResult)
  dataSource <- "日本銀行"
  dateFormat <- '%Y-%m'
  tags <- 'マネタリーベース,日本銀行'
}
if(htmlName=='00002'){
  importData <- c('importMonetarybaseOfJapan-2017.r')
  script <-
    RCurl::getURL(paste0(baseURL,importData[1]),ssl.verifypeer = FALSE)
  eval(parse(text = script))
  buf <- monetaryBase_Japan
  colnames(buf) <-
    gsub('[^:]+:(.+)','\\1',colnames(buf))
  obj <- fun_billToTri(obj = buf,valueCol = 9)
  fun_latestResult(obj = obj)
  dataTitle <- 
    paste0("マネタリーベース:日本:",latestResult)
  dataSource <- "日本銀行"
  dateFormat <- '%Y-%m'
  tags <- 'マネタリーベース,日銀当座預金,日本銀行'
}
if(htmlName=='00003'){
  importData <- c('importMoneyStock-2017.r')
  script <-
    RCurl::getURL(paste0(baseURL,importData[1]),ssl.verifypeer = FALSE)
  eval(parse(text = script))
  buf <- MoneyStock
  colnames(buf) <-
    gsub('[^:]+:(.+)','\\1',colnames(buf))
  obj <- fun_billToTri(obj = buf,valueCol = 10)
  fun_latestResult(obj = obj)
  dataTitle <- 
    paste0("マネーストック:日本:",latestResult)
  dataSource <- "日本銀行"
  dateFormat <- '%Y-%m'
  tags <- 'マネーストック,日本銀行'
}
if(htmlName=='00004'){
  importData <- c('importMoneyStock-2017.r')
  script <-
    RCurl::getURL(paste0(baseURL,importData[1]),ssl.verifypeer = FALSE)
  eval(parse(text = script))
  buf <- MoneyStock
  colnames(buf) <-
    gsub('[^:]+:(.+)','\\1',colnames(buf))
  obj <- fun_billToTri(obj = buf,valueCol = 11)
  fun_latestResult(obj = obj)
  dataTitle <- 
    paste0("マネーストック:日本:",latestResult)
  dataSource <- "日本銀行"
  dateFormat <- '%Y-%m'
  tags <- 'マネーストック,日本銀行'
}
if(htmlName=='00005'){
  importData <- c('importMoneyStock-2017.r')
  script <-
    RCurl::getURL(paste0(baseURL,importData[1]),ssl.verifypeer = FALSE)
  eval(parse(text = script))
  buf <- MoneyStock
  colnames(buf) <-
    gsub('[^:]+:(.+)','\\1',colnames(buf))
  obj <- fun_billToTri(obj = buf,valueCol = 13)
  fun_latestResult(obj = obj)
  dataTitle <- 
    paste0("マネーストック:日本:",latestResult)
  dataSource <- "日本銀行"
  dateFormat <- '%Y-%m'
  tags <- 'マネーストック,日本銀行'
}
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
objYear <- tail(unique(year(obj[,1])),5)[1]
ratioDF <- list()
lag <- c(1,3,6,12,24,36)
for(cnt in seq(length(lag))){
  buf <- 
    fun_makeDiffRatioTable(obj = obj,lag = lag[cnt])
  colnames(buf)[2] <- 
    paste0(gsub('\\([^\\(]+円\\)','',colnames(buf)[2]),':',lag[cnt],'ヶ月前との比(%)')
  print(tail(buf))
  ratioDF[[cnt]] <- buf
}
tsTitle <- paste0(colnames(obj)[2],':',format(tail(obj[,1],1),dateFormat))
```

```{r warning=F,error=F,message=F,echo=F,results='asis'}
cat('\n***\n')
cat(paste0("- Title : ", dataTitle,'\n'))
cat(paste0("- Source : ", dataSource,'\n'))
cat('- NSA,SAの区別なくxヶ月前との比を表示しています\n')
cat('\n***\n')
```

```{r warning=F,error=F,message=F,echo=F,results='asis',out.width='100%'}
cat(paste0('<div id="htmlTitle" style="text-align:center;font-weight: bold;font-size:1.6em;">',
           tsTitle,'</div>\n\n'))
cat('\n<hr>\n')
```

```{r warning=F,error=F,message=F,echo=F,results='asis',out.width='100%'}
cat('# 時系列チャート\n\n')
n <- 1
fun_generateKnit(objDF = obj,plotNum = n,dygraphTitle = colnames(obj)[2],group = 0,quantiles = 1)
eval(parse(text = paste0('dygraphPlot', n, ' %>% ', primeMinisterOfJapan_dygraph)))
cat('\n\n')
```

```{r warning=F,error=F,message=F,echo=F,results='asis'}
tsData <- fun_convertToTS(tsData = subset(obj,objYear<=year(obj[,1])))
fun_markdownTable(obj = tsData$returnDF,rownames = T)
cat('\n<hr>\n')
```

```{r warning=F,error=F,message=F,echo=F,results='asis'}
cat('# xヶ月前との比較(%)\n\n')
for(iii in seq(length(lag))){
  cat('## x=',lag[iii],'\n\n')
  tmp <- ratioDF[[iii]]
  tsData <- fun_convertToTS(tsData = subset(tmp,objYear<=year(tmp[,1])))
  fun_markdownTable(obj = tsData$returnDF,rownames = T)
  cat('\n<hr>\n')
}
```

```{r warning=F,error=F,message=F,echo=F,results='asis',out.width='100%'}
cat('# 移動平均\n\n')
ma <- fun_MovingAverage(obj = obj,dateFormat = dateFormat)
cat('\n\n')
n <- 2
fun_generateKnit(objDF = ma,plotNum = n,dygraphTitle = colnames(ma)[2],group = 0,quantiles = 0)
eval(parse(text = paste0('dygraphPlot', n, ' %>% ', primeMinisterOfJapan_dygraph)))
cat('\n<hr>\n')
```

```{r warning=F,error=F,message=F,echo=F,results='asis',out.width='100%'}
fun_rolling <- function(obj = ma,h = 12,objCol = 3,plot = 0,plotNum = 1){
  resultDF <- 
    fun_changesInSlope(obj = obj,h = h,objCol = objCol,plot = plot)
  tmp <- 
    resultDF$changesInConditions
  xtsData <- 
    xts(tmp[,-1],order.by=tmp[,1])
  p <- 
    dygraph(xtsData) %>%
    dyAxis("y",label = colnames(xtsData)[1]) %>%
    dyAxis("y2",label = colnames(xtsData)[2],independentTicks = T) %>%
    dySeries(colnames(xtsData)[1], axis = 'y',fillGraph = F) %>%
    dySeries(colnames(xtsData)[2], axis = 'y2',fillGraph = T) %>%
    dyLegend(show = "follow") %>%
    dyRangeSelector() %>%
    dyUnzoom() %>%
    dyOptions(maxNumberWidth = 100)
  assign(paste0('dygraphPlot',plotNum),p,envir = .GlobalEnv)
# 'arg' should be one of “y”, “y2”
  if(nrow(resultDF$changesInSlope)!=0){
    changeDate <- 
      resultDF$changesInSlope[,1]
    changeDateDF <-
      data.frame(format(changeDate,dateFormat),c(0,diff(year(changeDate)*12+month(changeDate))),
                 stringsAsFactors = F)
    colnames(changeDateDF) <-
      c('Point of Change','Month Difference')
    tmp <- 
      cbind(summary(tail(changeDateDF[,2],-1)))
    summaryData <-
      data.frame(Item=row.names(tmp),Value=tmp[,1],
                 row.names = NULL,stringsAsFactors = F)
  }else{
    changeDateDF <- NA
    summaryData <-NA
  }
  returnList <-
      list('changeDateDF' = changeDateDF,
           'summaryData' = summaryData)
  return(returnList)
}
cat('# ローリング回帰\n\n')
h <- 12
cat('- The Width of the rolling window(months):',h,'\n\n')
cat('## SMA\n\n')
objCol <- 3
returnList <- fun_rolling(objCol = objCol,plotNum = objCol,h = h)
eval(parse(text = paste0('dygraphPlot',objCol)))
cat('\n<hr>\n')
if(!is.na(returnList$changeDateDF)){
  fun_markdownTable(obj = returnList$changeDateDF)
  cat('\n<hr>\n')
  fun_markdownTable(obj = returnList$summaryData)
  cat('\n<hr>\n')
}
cat('## EMA\n\n')
objCol <- 4
returnList <- fun_rolling(objCol = objCol,plotNum = objCol,h = h)
eval(parse(text = paste0('dygraphPlot',objCol)))
cat('\n<hr>\n')
if(!is.na(returnList$changeDateDF)){
  fun_markdownTable(obj = returnList$changeDateDF)
  cat('\n<hr>\n')
  fun_markdownTable(obj = returnList$summaryData)
  cat('\n<hr>\n')
}
```

```{r warning=F,error=F,message=F,echo=F,results='hide',out.width='100%'}
library(ggpubr)
library(ggsci)
fun_preparePlot()
pngFile <-
  paste0(htmlName, "-1.png")
png(file = pngFile, width = 1000, height = 600)
fun_plotTimeSeries(obj = obj,chartType = 0,dateFormat = dateFormat,dataSource = dataSource,
                   mar = c(4,4,5,1),needLefLab = 0,fitLcolor = 2)
fun_addTxtToChart(obj = obj,cexTxt = 1,funType = 'min',col = 'black')
dev.off()
##########
pngFile <-
  paste0(htmlName, "-2.png")
png(file = pngFile, width = 1000, height = 600)
fun_ggboxplot(obj = obj,dataSource = dataSource)
dev.off()
##########
pngFile <-
  paste0(htmlName, "-3.png")
png(file = pngFile, width = 1000, height = 600)
fun_withList(obj = obj)
obj <- dfWithList
fun_gglboxpotPM(obj = obj,dataSource = dataSource)
dev.off()
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fun_outputMDforTS(tags = tags,
                  objDF = fun_summaryByName(obj = obj,omitFirst = 1,dateFormat = dateFormat),
                  htmlName = htmlName,
                  image1 = 1,image2 = 1,image3 = 1,
                  title = dataTitle,
                  tableTitle = colnames(obj)[2])
fun_timeSeriesList(tsTitle = tsTitle,htmlName = htmlName)
```

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- `r timeStamp`
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
