---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');htmlName<-'MovementOfFinancialIndicesBeforeJudgmentDay';rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-',htmlName,'.html')) })

title : 'Movement of Financial Indices before Judgment Day/Bankruptcy of Lehman Brothers'
author: 'アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp'
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 5
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 1000px;}</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000)
```

```{r warning = F,error = F,message = F,echo = F,results = 'hide'}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r warning = F,error = F,message = F,echo = F,results = 'hide'}
library(quantmod)
fredSymbolsDaily <- 
c(
  'DGS10','10-Year Treasury Constant Maturity Rate',
  'BAMLH0A0HYM2','BofA Merrill Lynch US High Yield Option-Adjusted Spread',
  'DTB3','3-Month Treasury Bill: Secondary Market Rate',
  'T10Y2Y','10-Year Treasury Constant Maturity Minus 2-Year Treasury Constant Maturity',
  'USD1MTD156N','1-Month London Interbank Offered Rate (LIBOR), based on U.S. Dollar',
  'USD3MTD156N','3-Month London Interbank Offered Rate (LIBOR), based on U.S. Dollar',
  'DCOILWTICO','Crude Oil Prices: West Texas Intermediate (WTI) - Cushing, Oklahoma',
  'T10YIE','10-Year Breakeven Inflation Rate',
  'SP500','S&P 500',
  'T5YIFR','5-Year, 5-Year Forward Inflation Expectation Rate',
  'DAAA','Moody\'s Seasoned Aaa Corporate Bond Yield',
  'DBAA','Moody\'s Seasoned Baa Corporate Bond Yield',
  'DEXUSEU','U.S. / Euro Foreign Exchange Rate',
  'DGS1','1-Year Treasury Constant Maturity Rate',
  'BAMLH0A0HYM2EY','BofA Merrill Lynch US High Yield Effective Yield',
  'TEDRATE','TED Spread',
  'DEXJPUS','Japan / U.S. Foreign Exchange Rate',
  'DJIA','Dow Jones Industrial Average',
  'VIXCLS','CBOE Volatility Index: VIX',
  'GOLDAMGBD228NLBM','Gold Fixing Price 10:30 A.M. (London time) in London Bullion Market, based in U.S. Dollars',
  'DEXCAUS','Canada / U.S. Foreign Exchange Rate',
  'T5YIE','5-Year Breakeven Inflation Rate',
  'T10YFF','10-Year Treasury Constant Maturity Minus Federal Funds Rate',
  'NASDAQCOM','NASDAQ Composite Index',
  'NIKKEI225','Nikkei Stock Average, Nikkei 225',
  'STLFSI','St. Louis Fed Financial Stress Index'
)
tsData <- list()
cnt <- 1
for(iii in seq(1,length(fredSymbolsDaily),by=2)){
  tmp0 <- 
    getSymbols(Symbols = fredSymbolsDaily[iii],src = 'FRED',auto.assign = F)
  tmp1 <-
    data.frame(Date = index(tmp0),tmp0,check.names = F,stringsAsFactors = F,row.names = NULL)
  colnames(tmp1)[2] <- fredSymbolsDaily[iii+1]
  tsData[[cnt]] <- tmp1
  print(tail(tsData[[cnt]],3))
  cnt <- cnt + 1
}
importIndex <- 
  c('importPutCallRatios.r','importSkew.r','importGMVI.r')
for(jjj in seq(length(importIndex))){
  script <- 
    RCurl::getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                         importIndex[jjj]),
                  ssl.verifypeer = F)
  eval(parse(text = script))
}
tsData[[cnt]] <- putCallRatio[[1]][,c(1,5)]
cnt <- cnt + 1
tsData[[cnt]] <- putCallRatio[[2]][,c(1,5)]
cnt <- cnt + 1
tsData[[cnt]] <- putCallRatio[[3]][,c(1,5)]
cnt <- cnt + 1
tsData[[cnt]] <- putCallRatio[[4]][,c(1,5)]
cnt <- cnt + 1
tsData[[cnt]] <- putCallRatio[[5]][,c(1,2)]
cnt <- cnt + 1
tsData[[cnt]] <- skewCBOE
cnt <- cnt + 1
tsData[[cnt]] <- GMVI1[,c(1,2)]
cnt <- cnt + 1
tsData[[cnt]] <- GMVI2[,c(1,2)]
cnt <- cnt + 1
tsData[[cnt]] <- GMVI2[,c(1,6)]
cnt <- cnt + 1
importIndex <- 
  c('Rscript_JGBInterestRate.r')
for(jjj in seq(length(importIndex))){
  script <- 
    RCurl::getURL(paste0("https://raw.githubusercontent.com/am-consulting/Rscript/master/", 
                         importIndex[jjj]),
                  ssl.verifypeer = F)
  eval(parse(text = script))
}
obj <- na.omit(jgbData[,c(1,11)])
colnames(obj)[2] <- paste0('Japanese Government Bond:',colnames(obj)[2])
tsData[[cnt]] <- obj
```

```{r warning=F,error=F,message=F,results='hold',echo=F}
dataTitle <- 
  paste0("審判の日/リーマンショック前後における金融指標の動き")
dataSource <- "Federal Reserve Bank of St. Louis、財務省、国際通貨研究所、Chicago Board Options Exchange"
windowsFonts(Meiryo = windowsFont("Meiryo"))
options(scipen = 999)
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`

***

```{r warning = F,error = F,message = F,echo = F,results = 'asis'}
JudgmentDay <- as.Date('2008-9-15')
pastDays <- 365*1
startDate <- JudgmentDay - pastDays
dataSource <- 'Federal Reserve Bank of St. Louis'
resultDF <- data.frame()
cat('#### Movement from ',pastDays,' days before Judgment Day\n')
for(iii in seq(length(tsData))){
  obj0 <- 
    na.omit(subset(tsData[[iii]],startDate<=tsData[[iii]][,1] & tsData[[iii]][,1]<=(JudgmentDay+pastDays)))
  cat('#### ',colnames(obj0)[2],'\n')
  fun_plotTimeSeries(obj = obj0,chartType = 0,
                     dataSource = dataSource,mar = c(4,4,4,2),needLefLab = 0,fitLcolor = 2,
                     typeL = 'o',cexL = 0.6,fitlwdL = 2)
  abline(v = as.numeric(JudgmentDay),col='red',lty=1)
  text(x = as.numeric(JudgmentDay),y = max(obj0[,2]),
       labels = '\n\n\n\n\nJudgment Day\nBankruptcy of Lehman Brothers',pos = 4,col='red')
  obj <- 
    na.omit(subset(obj0,obj0[,1]<=JudgmentDay))
  abline(h=as.numeric(tail(obj,1)[,2]),lty=2)
  peakDate <- tail(obj[which.max(obj[,2]),],1)
  abline(v=as.numeric(peakDate[,1]),lty=2)
  abline(h=as.numeric(peakDate[,2]),lty=2)
  bottomDate <- tail(obj[which.min(obj[,2]),],1)
  abline(v=as.numeric(bottomDate[,1]),lty=2)
  abline(h=as.numeric(bottomDate[,2]),lty=2)
  text(x = as.numeric(peakDate[,1]),y = as.numeric(peakDate[,2]),labels = paste0('\n\nPeak'),pos = 2)
  text(x = as.numeric(bottomDate[,1]),y = as.numeric(bottomDate[,2]),labels = paste0('Bottom\n\n'),adj = 5,pos = 2)
  cat('<hr>')
  resultDF[iii,1] <- iii
  resultDF[iii,2] <- colnames(obj)[2]
  resultDF[iii,3] <- peakDate[,1]
  resultDF[iii,4] <- JudgmentDay - peakDate[,1]
  resultDF[iii,5] <- bottomDate[,1]
  resultDF[iii,6] <- JudgmentDay - bottomDate[,1]
}
resultDF[,3] <- as.Date(resultDF[,3])
resultDF[,5] <- as.Date(resultDF[,5])
colnames(resultDF) <- 
  c('No.','Index','Peak','Before(days)','Bottom','Before(days)')
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fun_outputMD(tags = 'リーマンショック',
             objDF = resultDF,
             htmlName = htmlName,
             image1 = 0,image2 = 0,
             dataTitle = dataTitle,
             tableTitle = paste0('リーマンショック前後',pastDays,'日'),
             tableName = '金融指標の動き')
fun_updateURLcsv()
```

<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
