---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-QuantitativeAnalysisForBitcoin.html')) })

title : 'Quantitative Analysis For Bitcoin'
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 5
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<style>.main-container {max-width : 1000px;}</style>
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan

本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo = F, cache = F}
options(width = 1000)
```

```{r warning = F, error = F, message = F, echo = F}
windowsFonts(Meiryo = windowsFont("Meiryo"))
options(scipen = 100)
```

```{r warning = F, error = F, message = F, echo = F}
fileName <-
  'defaultPath.csv'
username <- 
  Sys.info()['user']
pathToFile <- 
  paste0('C:/Users/', username,'/Desktop/pathToCSV/')
setwd(pathToFile)
buf000 <- 
  read.csv(fileName, header = F, skip = 0, stringsAsFactor = F, check.names = F, fileEncoding = 'utf-8')
pathOutput <- 
  paste0("C:/Users/", username, buf000[2,1],'csv/')
setwd(pathOutput)
bitCoinCSV <- 'bitCoin.csv'
bitCoinOld <- 
  read.csv(file = bitCoinCSV, header = T, as.is = T)
bitCoinOld[,1] <-
  as.Date(bitCoinOld[,1])
```

```{r warning = F, error = F, message = F, echo = F}
library(quantmod)
tmp <- getSymbols('BTC/USD', 
                  src = "oanda", 
                  auto.assign = F, 
                  from = Sys.Date() - 365 * 10, to = Sys.Date())
bitCoinNew <- 
  data.frame(Date = as.Date(index(tmp)),
             tmp,
             check.names = F,
             stringsAsFactors = F,
             row.names = NULL)
bitCoinNew <- 
  subset(bitCoinNew, tail(bitCoinOld[,1],1) < bitCoinNew[,1])
if(nrow(bitCoinNew) != 0){
  bitCoin <- 
    rbind(bitCoinOld,bitCoinNew)
  write.csv(x = bitCoin, file = bitCoinCSV, quote = F, row.names = F, append = F, fileEncoding = 'utf8')
}else{
  bitCoin <- bitCoinOld
}
```

```{r warning = F, error = F, message = F, results = 'hide', echo = F}
fun_latestResult(obj = bitCoin,dateFormat = '%Y-%m-%d')
dataTitle <- 
  paste0('ビットコインの計量分析:',latestResult)
dataSource <- 
  'OANDA Corporation'
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- Source https://www.oanda.com/

***

```{r warning = F, error = F, message = F, echo = F}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r warning = F, error = F, message = F, echo = F}
n <- 1
fun_generateKnit(objDF = bitCoin, plotNum = n, group = 0,dygraphTitle = '')
eval(parse(text = paste0('dygraphPlot', n)))
```

```{r warning = F, error = F, message = F, echo = F}
fun_makeDiffTable(obj = bitCoin)
n <- 2
fun_generateKnit(objDF = diffDF, plotNum = n, barPlot = 1, group = 0, dygraphTitle = '前日差')
eval(parse(text = paste0('dygraphPlot', n)))
```

```{r warning = F, error = F, message = F, echo = F}
```

***

<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
