---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');htmlName<-'CO2Emissions';rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-',htmlName,'.html')) })

title : 'CO2 Emissions From Fuel Combustion Highlights 2016(Source:IEA)'
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 5
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 1000px;}</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 500)
```

```{r warning = F, error = F, message = F, echo = F}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r,warning=F,error=F,message=F,echo=F}
tmp0 <-
  read.csv(file = 'https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/csvData/TSdata/IEA_CO2_FC.csv',header = F,stringsAsFactors = F,fileEncoding = 'utf8')
sheetTitle <- tmp0[1,1]
sheetUnit <- tmp0[1,2]
tmp1 <- tmp0[-1,]
tmp2 <- t(tmp1)
colnames(tmp2) <- tmp2[1,]
tmp3 <- tmp2[-1,]
colnames(tmp3)[grep('Ivoire',colnames(tmp3))] <- 'Côte d\'Ivoire'
colnames(tmp3)[grep('Cura',colnames(tmp3))] <- 'Curaçao'
dataSet <- 
  data.frame(Date = as.Date(paste0(tmp3[,1],'-1-1')),
             apply(tmp3[,-1],2,as.numeric),check.names = F,row.names = NULL,stringsAsFactors = F)
```

```{r,warning=F,error=F,message=F,results='hold',echo=F}
dataTitle <- 
  paste0('-パリ協定離脱-燃料燃焼による二酸化炭素排出/-Withdraw from the Paris Agreement-CO2 Emissions From Fuel Combustion Highlights(Source:IEA):2016')
dataSource <- 'International Energy Agency'
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- Source https://www.iea.org/publications/freepublications/publication/co2-emissions-from-fuel-combustion-highlights-2016.html
- The Paris Agreement http://unfccc.int/paris_agreement/items/9485.php
- 2017-06-01:『U.S. President Donald Trump announced that the United States would withdraw from the agreement.』(quotation from [Wikipedia](https://en.wikipedia.org/wiki/Paris_Agreement))

***

```{r warning=F,error=F,message=F,echo=F,results='asis'}
cat('#### ',sheetTitle,':',sheetUnit,'\n\n')
obj <- 
  fun_transposeDataFrame(obj = dataSet,dateFormat = '%Y',colName = 'Region/Country/Economy')
obj <-
  obj[-which(apply(obj,1,function(x)sum(is.na(x)))==(ncol(obj)-1)),]
obj <- obj[order(obj[,ncol(obj)],decreasing = T),]
fun_markdownTable(obj = obj)
```

***

```{r warning=F,error=F,message=F,echo=F,results='asis',fig.height=6}
objCol <-
  grep('of china$|States$|india$|russian|japan',colnames(dataSet),ignore.case = T)
obj <- na.omit(dataSet[,c(1,objCol)])
lineColors <-
      RColorBrewer::brewer.pal(ncol(obj), 'Dark2')
ylim <-
  c(min(obj[,-1]),max(obj[,-1]))
par(mar=c(4,6,4,1),font.main=1,cex.main=1,family='Meiryo')
for(ccc in 2:ncol(obj)){
  if(ccc == 2){
    plot(x = obj[,1],y = obj[,ccc],type='o',pch=20,col=lineColors[ccc],
         xaxt='n',xlab='',ylim=ylim,log='y',ylab=paste0(sheetUnit,'\nlogarithmic axis'),
         panel.first = grid(nx = NULL,ny = NULL,lty = 2,equilogs = F),
         main = paste0(sheetTitle,'\n',
                       paste0(format(range(obj[,1]),'%Y'),collapse = '~'),
                       '\nSourece:',dataSource))
  }else{
    lines(x = obj[,1],y = obj[,ccc],type='o',pch=20,col=lineColors[ccc],xaxt='n',yaxt='n',xlab='',ylab='')
  }
}
axis.Date(side = 1,at = obj[,1],format = '%Y',padj = 1,cex.axis = 1)
graphics::legend(x = 'topleft',col = lineColors[-1],lty = 1,legend = colnames(obj)[-1],
                 cex = 1,bty = 'n',lwd = 4)
```

***

```{r warning=F,error=F,message=F,echo=F,results='asis'}
fun_barPlot <- function(objCol){
obj <- na.omit(dataSet[,c(1,objCol)])
diffDF <- fun_makeDiffRatioTable(obj = obj,lag = 1)
diffDF$Col <- ifelse(0<=diffDF[,2],'#4169e1','#dc143c')
par(mar=c(4,3,4,1),font.main=1,cex.main=1,family='Meiryo')
barplot(height = diffDF[,2],names.arg = format(diffDF[,1],'%Y'),las=2,
        col = diffDF$Col,main = paste0(colnames(diffDF)[2],'\n',sheetTitle,'\nYear over Year(%)'))
}
fun_barPlot(objCol = objCol[1])
cat('<hr>')
fun_barPlot(objCol = objCol[2])
cat('<hr>')
fun_barPlot(objCol = objCol[3])
cat('<hr>')
fun_barPlot(objCol = objCol[4])
cat('<hr>')
fun_barPlot(objCol = objCol[5])
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
obj <-
  fun_transposeDataFrame(obj = fun_makeDiffRatioTable(obj = dataSet,lag = 1),dateFormat = '%Y')
obj <-
  obj[-which(apply(obj,1,function(x)sum(is.na(x)))==(ncol(obj)-1)),]
obj <- obj[order(obj[,ncol(obj)],decreasing = T),]
fun_outputMD(tags = 'IEA,CO2',
             objDF = obj,
             htmlName = htmlName,
             image1 = 0,image2 = 0,
             dataTitle = dataTitle,
             tableTitle = 'Year over Year(%)/前年比(%)',
             tableName = sheetTitle)
fun_updateURLcsv()
```

***
<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
