---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');htmlName<-'EPU';rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-',htmlName,'.html')) })

title : 'Economic Policy Uncertainty'
author: 'アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp'
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 4
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 1000px;}</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000)
```

```{r warning = F, error = F, message = F, echo = F}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
importAMCC <- 
  c('importEPU.r')
for(iii in seq(length(importAMCC))){
  script <-
    getURL(
      paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/",
             importAMCC[iii]),
      ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
needExe <- 0
if(needExe != 0){
importAMCC <- 
  c('importEconomicPolicyUncertaintyIndex.r')
for(iii in seq(length(importAMCC))){
  script <-
    RCurl::getURL(
      paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/",
             importAMCC[iii]),
      ssl.verifypeer = F)
  eval(parse(text = script))
}
}
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
username <-
  Sys.info()['user']
pathToFile <-
  paste0('C:/Users/', username,'/Desktop/pathToCSV/')
setwd(pathToFile)
fileName <-
  'defaultPath.csv'
buf <-
  read.csv(file = fileName,
           header = F,
           skip = 0,
           stringsAsFactor = F,
           check.names = F,
           fileEncoding = 'utf-8',quote = "\"")
pathToFolder <- 'TSdata'
pathOutputTOcsv <-
  paste0("C:/Users/", username, buf[2,1],'csv/csvData/',pathToFolder,'/')
setwd(pathOutputTOcsv)
objCSV <- 
  dir(pathOutputTOcsv)[grep('EPU_',dir(pathOutputTOcsv))]
EconomicPolicyUncertaintyIndex <- list()
for(iii in seq(length(objCSV))){
  buf <- 
    read.csv(file = objCSV[iii],check.names = F,stringsAsFactors = F,fileEncoding = 'UTF-8')
  buf[,-1] <- 
    data.frame(apply(buf[,-1,drop=F],2,as.numeric),stringsAsFactors = F,check.names = F)
  buf[,1] <- as.Date(buf[,1])
  EconomicPolicyUncertaintyIndex[[iii]] <- buf
  print(tail(EconomicPolicyUncertaintyIndex[[iii]]))
}
```

```{r warning=F,error=F,message=F,results='hide',echo=F}
for(iii in seq(length(EconomicPolicyUncertaintyIndex))){
  tmp <- colnames(EconomicPolicyUncertaintyIndex[[iii]])[2]
  print(paste0(iii,':',gsub('(.+):.+','\\1',tmp)))
}
```

```{r warning=F,error=F,message=F,results='hold',echo=F}
dateFormat <- '%Y-%m'
fun_latestResult(obj = EconomicPolicyUncertaintyIndex[[7]],objColumn = 2)
dataTitle <- 
  paste0("Economic Policy Uncertainty Index:",latestResult)
dataSource <- "Economic Policy Uncertainty,Federal Reserve Bank of St. Louis"
windowsFonts(Meiryo = windowsFont("Meiryo"))
options(scipen = 999)
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- http://www.policyuncertainty.com/index.html

***

```{r warning=F, error=F, message=F, echo=F, results='asis'}
obj <- EPUallData[,c(1,2,3,4)]
n <- 1
fun_generateKnit(objDF = obj,plotNum = n,group = 0,
                 dygraphTitle = paste0(gsub('.+index for\\s(.+)','\\1',colnames(EPUallData)[2:4],
                                            ignore.case = T),collapse = ' × '))
eval(parse(text = paste0('dygraphPlot', n)))
```

***

#### Economic Policy Uncertainty Index
- Original

```{r warning=F, error=F, message=F, echo=F, results='asis'}
for(iii in seq(length(EconomicPolicyUncertaintyIndex))){
  tmp <- 
    EconomicPolicyUncertaintyIndex[[iii]]
  if(iii==1){allData <- tmp}else{allData <- merge(allData,tmp,by='Date',all=T)}
}
allData <- 
  allData[,apply(allData,2,function(x)sum(is.na(x)))!=nrow(allData)]
fun_markdownTable(obj = fun_transposeDataFrame(obj = allData,
                                               dateFormat = dateFormat,colName = 'Country/Region',tailN = 5))
```

***
- Month Over Month(%)

```{r warning=F, error=F, message=F, echo=F, results='asis'}
fun_markdownTable(obj = fun_transposeDataFrame(obj = fun_makeDiffRatioTable(obj = allData,lag = 1),
                                               dateFormat = dateFormat,colName = 'Country/Region',tailN = 5))
```

***

#### Economic Policy Uncertainty Index:Japan

```{r warning=F, error=F, message=F, echo=F, results='asis'}
iii <- 10
obj <- EconomicPolicyUncertaintyIndex[[iii]]
for(ccc in 2:ncol(obj)){
  fun_plotTimeSeries(obj = obj,objYL = ccc,typeL = 'o',chartType = 0,
                     dateFormat = dateFormat,dataSource = dataSource,
                     dataTitle = 'Economic Policy Uncertainty Index',
                     needLefLab = 0,fitLcolor = 2,mar = c(4,4,5,1),fitlwdL = 2)
  cat('<hr>')
}
```

```{r warning=F,error=F,message=F,echo=F,results='hide',fig.height=5}
username <-
  Sys.info()['user']
pathToFile <-
  paste0('C:/Users/', username,'/Desktop/pathToCSV/')
setwd(pathToFile)
fileName <-
  'defaultPath.csv'
buf <-
  read.csv(file = fileName,
           header = F,
           skip = 0,
           stringsAsFactor = F,
           check.names = F,
           fileEncoding = 'utf-8',quote = "\"")
pathOutputTOcsv <-
  paste0("C:/Users/", username, buf[2,1],'charts/chartImages/')
setwd(pathOutputTOcsv)
getwd()
par(family = 'Meiryo')
pngFile <-
  paste0(htmlName, ".png")
png(file = pngFile, width = 1000, height = 600)
##################
iii <- 10
obj <- EconomicPolicyUncertaintyIndex[[iii]][,c(1,2)]
fun_plot4charts(obj = obj,tailN = c(10^10,12*5,12*3,12),dateFormat = dateFormat)
dev.off()
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fun_outputMD(tags = 'Economic Policy Uncertainty Index',
             objDF = fun_summaryByName(obj = obj,dateFormat = dateFormat),
             htmlName = htmlName,
             image = 1,
             dataTitle = dataTitle,
             tableTitle = colnames(obj)[2])
```

<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
