---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-CrossCorrelationBetweenTwoRandomWalkTimeSeries.html')) })
title : "Cross-Correlation Between Two Random Walk Time Series"
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 5
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet"> 
<style>
.main-container {
	max-width: 1000px;
	margin-left: auto;
	margin-right: auto;
}

table{
 white-space: nowrap;
}
</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan

本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r warning = F, error = F, message = F, echo = F, results = 'hold'}
dataTitle <- 'Cross-Correlation Between Two Random Walk Time Series / 2つのランダムウォーク時系列データの相互相関係数'
Author <- "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
cat(paste("Title  : ", dataTitle, "\n"))
cat(paste("Author : ", Author, "\n"))
windowsFonts(Meiryo = windowsFont("Meiryo"))
```

```{r warning = F, error = F, message = F, echo = T, results = 'asis'}
funRW <- function(n = 100, lineColor = c('blue', 'red'), variableNames = c('randomWalk01', 'randomWalk02')){
  assign(variableNames[1], cumsum(rnorm(n)))
  assign(variableNames[2], cumsum(rnorm(n)))
  x1 <- get(variableNames[1])
  x2 <- get(variableNames[2])
  par(mfrow = c(1, 3), family = 'Meiryo')
# CCF Part
  resultCCF <-
    ccf(x1, x2, lag = 36, main = paste0('Cross-Correlation Function\n', paste0(variableNames, collapse = ' × ')))
  panel.first = grid(nx = NULL, ny = NULL, lty = 2, equilogs = T)
# CCF Part
# Time Series Part
  plot(x1, type = 'l', col = lineColor[1], 
       ylim = c(min(x1, x2), max(x1, x2)), xlab = '', ylab = '', 
       main = paste0('Time Series Plot\n', paste0(variableNames, collapse = ' × '),'\n'))
  lines(x2, type = 'l', col = lineColor[2])
  panel.first = grid(nx = NULL, ny = NULL, lty = 2, equilogs = T)
  graphics::legend('topleft', col = lineColor, lty = 1, legend = variableNames, cex = 1, bty = 'n')
# Time Series Part
  buf0 <- data.frame(resultCCF$lag,resultCCF$acf)
  buf <- buf0[order(buf0[,2],decreasing = T),][c(1,nrow(buf0)),]
  colnames(buf) <- c('lag','ccf')
  ccfResult <- buf
# Scatter Part
  ccf0 <- buf0[buf0[,1]==0,][,2]
  plot(x1, x2, xlab = '', ylab = '', 
       main = paste0('Scatter Plot:Lag = 0, r = ', ccf0, '\n', paste0(variableNames, collapse = ' × '),'\n'))
  abline(lm(x2~x1),col = 'red')
  panel.first = grid(nx = NULL, ny = NULL, lty = 2, equilogs = T)
# Scatter Part
  print(knitr::kable(ccfResult,row.names = F))
}
for(iii in 1:20){funRW(); cat('\n<hr>')}
```

<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
