---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');htmlName<-'OICA';rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-',htmlName,'.html')) })

title : 'Production Statistics Of Cars and Commercial vehicles(Source:OICA)'
author: 'アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp'
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 5
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 1000px;}</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000,scipen = 999)
```

```{r warning = F, error = F, message = F, echo = F}
fileName <- 
  'functionList.csv'
baseURL <- 
  'https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/'
functionList <- 
  read.csv(
    file = paste0(baseURL,'csv/',fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    RCurl::getURL(paste0(baseURL,functionList[iii,1]),ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
importData <- c('importOICA.r')
script <-
  RCurl::getURL(paste0(baseURL,importData[1]),ssl.verifypeer = FALSE)
eval(parse(text = script))
```

```{r warning=F,error=F,message=F,results='hold',echo=F}
obj <- OICA[[length(OICA)]][1,]
latest <-
  paste0(obj[,6],':',obj[,1],':',format(obj[,grep('total$',colnames(obj),ignore.case = T)],big.mark=','))
dataTitle <- 
  paste0("国別自動車生産量:",latest)
dataSource <- "International Organization of Motor Vehicle Manufacturers"
windowsFonts(Meiryo = windowsFont("Meiryo"))
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- Source http://www.oica.net/category/production-statistics/

***

```{r warning=F, error=F, message=F, echo=F, results='asis'}
for(iii in seq(length(OICA))){
  obj0 <- OICA[[iii]]
  obj1 <- 
    obj0[,grep('country|total|year',colnames(obj0),ignore.case = T)]
  dateYear <- 
    as.Date(paste0(unique(obj1$Year),'-1-1'))
  obj2 <- 
    data.frame(t(obj1[,c(1,2)]),stringsAsFactors = F)
  obj3 <- 
    data.frame(row.names(obj2),obj2,row.names = NULL,stringsAsFactors = F)
  colnames(obj3) <- obj3[1,]
  obj3 <- obj3[-1,]
  obj3$Date <- dateYear
  colnames(obj3) <- gsub('^totals$','Total',colnames(obj3),ignore.case = T)
  if(iii==1){totalData <- obj3}else{totalData <- plyr::rbind.fill(totalData,obj3)}
}
objCol <- grep('Date|Country',colnames(totalData))
totalData[,-objCol] <- apply(totalData[,-objCol],2,as.numeric)
dateCol <-
  grep('date',colnames(totalData),ignore.case = T)
elimCol <-
  grep('country',colnames(totalData),ignore.case = T)
objCol <-
  which(seq(ncol(totalData))!=dateCol & seq(ncol(totalData))!=elimCol)
totalData <- totalData[,c(dateCol,objCol)]
```

#### Total Production(Cars and Commercial vehicles)

```{r warning=F,error=F,message=F,echo=F,results='asis'}
objCol <-
  grep('total',colnames(totalData),ignore.case = T)
obj <-
  totalData[,c(1,objCol)]
imageTitle <- 
  paste0('Production Statistics Of Cars and Commercial vehicles')
par(mar=c(4,5,4,1),family='Meiryo',font.main=1,cex.main=1.1)
plot(x = obj[,1],y = obj[,2],type = 'o',xaxt = 'n',xlab = '',ylab = colnames(obj)[2],
     pch = 20,cex = 1,col = 'blue',
     panel.first = grid(nx = NA,ny = NULL,lty = 2,equilogs = T),lwd = 1,
     main = paste0(imageTitle,'\nSource:',dataSource))
axis(side = 1,at = obj[,1],labels = format(obj[,1],'%Y'),las=2)
fun_markdownTable(obj = fun_transposeDataFrame(obj = obj,dateFormat = '%Y',
                                               colName = 'Country/Region',tailN = 6))
cat('<hr>')
YoY <-
  fun_makeDiffRatioTable(obj = obj,lag = 1)
colnames(YoY)[2] <- paste0(colnames(YoY)[2],':Year Over Year')
par(mar=c(4,5,4,1),family='Meiryo',font.main=1,cex.main=1.1)
plot(x = YoY[,1],y = YoY[,2],type = 'h',xaxt = 'n',xlab = '',ylab = colnames(YoY)[2],
     pch = 20,cex = 1,col = 'blue',
     panel.first = grid(nx = NA,ny = NULL,lty = 2,equilogs = T),lwd = 5,
     main = paste0(imageTitle,'\nSource:',dataSource))
axis(side = 1,at = YoY[,1],labels = format(YoY[,1],'%Y'),las=2)
abline(h=0,col='red',lwd=2)
fun_markdownTable(obj = fun_transposeDataFrame(obj = YoY,dateFormat = '%Y',colName = 'Country/Region',
                                               tailN = 6))
```

***
#### By Country(Cars and Commercial vehicles)

```{r warning=F,error=F,message=F,echo=F,results='asis'}
objCol <-
  grep('china|germany|japan|south korea|usa|mexico',colnames(totalData),ignore.case = T)
obj <-
  totalData[,c(1,objCol)]
lineColors <-
  RColorBrewer::brewer.pal(8, 'Dark2')
# Accent 8
# Dark2 8
# Paired 12
# Pastel1 9
# Pastel2 8
# Set1 9
# Set2 8
# Set3 12
ylim <- 
  c(floor(min(obj[,-1])),ceiling(max(obj[,-1])))
par(mar=c(4,5,4,1),family='Meiryo',font.main=1,cex.main=1.1)
colN <- 1
plot(x = obj[,1],y = obj[,2],type = 'o',xaxt = 'n',xlab = '',ylab = 'Total(Cars and Commercial vehicles)',
     pch = 20,cex = 1,col = lineColors[colN+0],
     panel.first = grid(nx = NA,ny = NULL,lty = 2,equilogs = T),lwd = 1,
     main = paste0(imageTitle,'\nSource:',dataSource))
lines(x = obj[,1],y = obj[,3],type = 'o',col = lineColors[colN+1],pch = 20,cex = 1,lwd = 1)
lines(x = obj[,1],y = obj[,4],type = 'o',col = lineColors[colN+2],pch = 20,cex = 1,lwd = 1)
lines(x = obj[,1],y = obj[,5],type = 'o',col = lineColors[colN+3],pch = 20,cex = 1,lwd = 1)
lines(x = obj[,1],y = obj[,6],type = 'o',col = lineColors[colN+4],pch = 20,cex = 1,lwd = 1)
lines(x = obj[,1],y = obj[,7],type = 'o',col = lineColors[colN+5],pch = 20,cex = 1,lwd = 1)
axis(side = 1,at = obj[,1],labels = format(obj[,1],'%Y'),las=2)
graphics::legend(x = 'top',col = lineColors[colN:(colN+5)],lty = 1,
                 legend = colnames(obj)[-1],cex = 1.2,bty = 'n',lwd = 4)
tDF <-
  fun_transposeDataFrame(obj = obj,dateFormat = '%Y',colName = 'Country/Region',tailN = 6)
fun_markdownTable(obj = tDF[order(tDF[,ncol(tDF)],decreasing = T),])
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fun_preparePlot()
pngFile <- 
  paste0(htmlName, "1.png")
png(file = pngFile, width = 1000, height = 600)
objCol <-
  grep('japan',colnames(totalData),ignore.case = T)
obj <-
  totalData[,c(1,objCol)]
mergeData <- 
  merge(obj,fun_makeDiffRatioTable(obj = obj,lag = 1),by = 'Date')
colnames(mergeData)[-1] <- 
  c('Total(Cars and Commercial vehicles)','Year Over Year(%)')
fun_plotTimeSeries(obj = mergeData,chartType = 2,typeL = 'o',typeR = 'h',
                   dateFormat = '%Y',lwdR = 3,dataTitle = 'Japan',dataSource = dataSource,cexL = 2,
                   mar = c(4,5,5,5))
dev.off()
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
obj <- 
  data.frame(na.omit(t(tail(totalData,1))),stringsAsFactors = F)
obj <- 
  data.frame(row.names(obj),obj,stringsAsFactors = F,row.names = NULL)
colnames(obj) <- obj[1,]
obj <- obj[-1,]
colnames(obj)[2] <- format(as.Date(colnames(obj)[2]),'%Y年')
obj[,2] <- sapply(obj[,2],as.numeric)
obj <- obj[order(obj[,2],decreasing = T),]
fun_outputMD(tags = 'International Organization of Motor Vehicle Manufacturers',
             objDF = obj,
             htmlName = htmlName,
             image1 = 1,
             image2 = 0,
             title = dataTitle,
             tableTitle = colnames(obj)[2],
             tableName = imageTitle)
fun_updateURLcsv()
```

<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
