---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-JapaneseLaws.html')) })

title : "Japanese Laws"
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 4
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<style>.main-container {max-width : 1000px;}</style>
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>table { white-space: normal; }</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan

本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000)
```

<script src="https://ajax.googleapis.com/ajax/libs/jquery/2.2.4/jquery.min.js"></script>
<link  href="https://cdn.datatables.net/1.10.12/css/jquery.dataTables.min.css" rel="stylesheet">
<script src="https://cdn.datatables.net/1.10.12/js/jquery.dataTables.min.js"></script>
<script src="https://bartaz.github.io/sandbox.js/jquery.highlight.js"></script>
<script src="https://cdn.datatables.net/plug-ins/1.10.12/features/searchHighlight/dataTables.searchHighlight.min.js"></script>
<link  href="https://cdn.datatables.net/plug-ins/1.10.12/features/searchHighlight/dataTables.searchHighlight.css" rel="stylesheet">
<script>
$(document).ready(function() {
  $('table').DataTable( {
    "dom"            : '<"top"p>rt<"bottom"fli><"clear">',
    "order"          : [[ 0, "asc" ]],
    "lengthMenu"     : [[5, 10, -1],[5, 10, "All"]],
    "searching"      : true,
    "paging"         : true,
    "ordering"       : true,
    "info"           : true,
    "scrollX"        : true,
    "retrieve"       : true,
    "searchHighlight": true
  } );
} );
</script>

<!-- <div class="arttitle"></div> -->
<!-- <div class="item"></div> -->
<!-- <div class="number"></div> -->
<!-- <div class="paraX"></div> -->

```{r warning=F,error=F,message=F,echo=F,results='hide'}
# 括弧内の文字列のみ抽出
# http://stackoverflow.com/questions/33066058/regex-in-r-replace-only-part-of-a-pattern
# http://stackoverflow.com/questions/24534782/how-do-skip-or-f-work-on-regex
# http://stackoverflow.com/questions/8613237/extract-info-inside-all-parenthesis-in-r
# http://stackoverflow.com/questions/28955367/extract-text-in-parentheses-in-r?noredirect=1&lq=1
# http://stackoverflow.com/questions/36176442/highlight-search-result-in-datatables
url <- 
  "http://law.e-gov.go.jp/htmldata/S25/S25HO201.html"
htmlLines <- 
  readLines(url,skipNul = F,encoding = 'shift_jis')
lawText <- 
  Reduce(function(x, y) paste0(x, y), htmlLines)
lawTitle <-
  regmatches(lawText, gregexpr("(?<=title>).*?(?=</title)", lawText, perl=T,ignore.case = T))[[1]]
pattern <- 
  '<DIV\\s*?class=".*?">(\\s|\\S)*?</div>'
divS <- 
  regmatches(lawText, 
             gregexpr(pattern = pattern,
                      text = lawText,
                      ignore.case = T))[[1]]
lawTable <- 
  data.frame()
#for(iii in 1:length(divS)){
for(iii in 1:50){
  textWithDIVremoved <-
    gsub('<div\\s*?class=".*?">|</div>',
         '',
         divS[iii],
         ignore.case = T)
  textWithDIVandLABELremoved <-
    gsub('<a\\s*?name=\"[^>]*?\">(.*?)</a>',
         '\\1',
         textWithDIVremoved,
         ignore.case = T)
  textWithDIVandLABELremovedBREAKadded <-
    gsub('<b>',
         '<br><b>',
         textWithDIVandLABELremoved,
         ignore.case = T)
  textWithDIVandLABELremovedBREAKadded <-
    gsub('</b>',
         '</b><br>',
         textWithDIVandLABELremovedBREAKadded,
         ignore.case = T)
  pattern <-
    '<a\\s*?href=.*?>'
  if(length(grep(pattern,
                 textWithDIVandLABELremovedBREAKadded,
                 ignore.case = T)) != 0){
    finalText <-
      enc2native(gsub('HREF=\"/',
                      'HREF=\"http://law.e-gov.go.jp/',
                      textWithDIVandLABELremovedBREAKadded,
                      ignore.case = T))
  }else{
    finalText <- 
      textWithDIVandLABELremovedBREAKadded
  }
  finalText <- 
    gsub('^<br>',
         '',
         finalText,
         ignore.case = T)
  lawTable[iii,1] <- finalText
}
```

```{r warning=F,error=F,message=F,echo=F,results='asis'}
lawTable <- 
  data.frame(seq(nrow(lawTable)),
             lawTable,
             stringsAsFactors = F)
colnames(lawTable) <-
  c('No.', '条文')
```

```{r warning=F,error=F,message=F,echo=F,results='asis'}
knitr::kable(lawTable,
             escape = F,
             format = 'html',
             table.attr = "ID = 'AMCC' class = 'display compact' width = '100%'")
```

***
<script>MakeNegative()</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
