---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-EffectiveExchangeRateIndices.html')) })
title : "実効為替レート"
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
output: 
  html_document:
    fig_height: 4
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet"> 
<style>
.main-container {
	max-width: 1000px;
	margin-left: auto;
	margin-right: auto;
}

table{
 white-space: nowrap;
}
</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan

```{r set-options, echo=F, cache=F}
options(width = 1000)
```

```{r,warning=F,error=F,message=F,results='hold',echo=F}
dataTitle <- '実効為替レート / Effective exchange rate indices' 
dataSource <- 'Bank for International Settlements'
Author <- "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
cat(paste("Title       : ", dataTitle, "\n"))
cat(paste("Data Source : ", dataSource, "\n"))
cat(paste("Author      : ", Author, "\n"))
cat(paste("作成日      : ", Sys.time(), "\n"))
windowsFonts(Meiryo = windowsFont("Meiryo"))
options(scipen = 999)
```

***

```{r warning=F,error=F,message=F,echo=F}
library(excel.link)
library(xts)
library(dygraphs)
# Reference https://rstudio.github.io/dygraphs/
username <- Sys.info()['user']
pathOutput <- paste0("C:/Users/", username, "/Desktop/R_Data_Write/")
setwd(pathOutput)
urlToData <- 'http://www.bis.org/statistics/'
zipFile <- 'full_webstats_eer_d_dataflow_csv.zip'
if(!file.exists(paste0(pathOutput, zipFile))) {
  download.file(paste0(urlToData,zipFile), zipFile, mode = 'wb')
  unzip(zipFile)
}
fileName <- dir(pathOutput)[grep('\\.csv',dir(pathOutput))]
buf0 <- xl.read.file(fileName, header=F, top.left.cell = "A1", xl.sheet = 1, excel.visible = F)
# buf0 <- data.table::fread(fileName, header=FALSE)) 
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
buf1 <- buf0
cc <- which((apply(buf1,2,(function(x)length(grep('reference area',x,ignore.case = T)))))!=0)
rr <- which((apply(buf1,1,(function(x)length(grep('reference area',x,ignore.case = T)))))!=0)
buf2 <- buf1[rr:nrow(buf1),cc:ncol(buf1)]
buf3 <- t(buf2) # matrix
buf3 <- data.frame(buf3,row.names = NULL,stringsAsFactors = F)
colnames(buf3) <- paste0(unlist(buf3[1,]),'-',unlist(buf3[2,]))
buf3 <- buf3[-c(1:2),]
colnames(buf3)[1] <- 'Date'
class(buf3[,1])
buf3[,1] <- as.Date(buf3[,1])
class(buf3[,1])
buf3[,-1] <- apply(buf3[,-1],2,as.numeric)
class(buf3[,ncol(buf3)])
buf4 <- buf3
buf4[is.na(buf4)] <- NA
dataSet <- buf4
```

```{r warning=F,error=F,message=F,echo=F}
fun_dygraph <- function(grepWord = 'JP'){
  obj <- grep(grepWord,colnames(dataSet),ignore.case = T)
  timeSeries0 <- na.omit(dataSet[,c(1,obj)])
  timeSeries <- xts(timeSeries0[,-1], order.by=timeSeries0[,1])
  dygraph(timeSeries,xlab = 'Date',main = paste0(colnames(timeSeries0)[-1],collapse = ' × '))  %>% 
    dyLegend(width = 500) %>% dyRangeSelector()
}
```

```{r warning=F,error=F,message=F,echo=F}
# colnames(dataSet)
fun_dygraph(grepWord = 'Japan')
```

***

```{r warning=F,error=F,message=F,echo=F}
fun_dygraph(grepWord = 'United States')
```

***

```{r warning=F,error=F,message=F,echo=F}
fun_dygraph(grepWord = 'Euro area')
```

```{r warning=F,error=F,message=F,echo=F}
funDataTable <- function(obj, orderColumn = 0, orderDirection = 'desc', width01 = '3%', width02 = '10%', caption = '') {
  DT::datatable(
    obj,
    extensions = c("Buttons", "ColReorder" , "FixedColumns", "FixedHeader"),
    options = list(paging = T, autoWidth = F, info = T, lengthChange = T, ordering = T,
      searching = T, scrollX = T, lengthMenu = list(c(15, -1, 1), c(15, 'All', 1)),
      orderClasses = T, order = list(list(orderColumn, orderDirection)), 
      search = list(regex = T, caseInsensitive = T), searchHighlight = T,
      columnDefs = list(list(width = width01, targets = 0), list(width = width02, targets = 1)),
      dom = 'BRlfrtip', buttons = I('colvis'), colReorder = T, fixedColumns = list(leftColumns = 1), fixedHeader = T),
    rownames = F, caption = caption, class = 'display compact', escape = F, filter = 'top'
  )  
}
```

***

```{r warning=F,error=F,message=F,echo=F}
# df <- data.frame(Date = index(timeSeries),timeSeries,check.names = F,stringsAsFactors = F)
# funDataTable(obj = df)
```

***

<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>