---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-GoldPrice.html')) })
title : "Gold Price"
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 4
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 1000px;}</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options,echo=F,cache=F}
options(width = 1000)
```

```{r warning = F, error = F, message = F, echo = F}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r warning=F,error=F,message=F,echo=F}
script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/importWorldGoldCouncilPriceData.r",
    ssl.verifypeer = F
  )
eval(parse(text = script))
```

```{r warning=F,error=F,message=F,echo=F,results='hold'}
dateFormat <- '%Y年%m月%d日'
fun_latestResult(obj = goldPriceData,objColumn = c(2,4),dateFormat = dateFormat)
dataTitle <-
  paste0('ゴールド価格(Source:World Gold Council,トロイオンス当り):',latestResult)
dataSource <- 'World Gold Council'
windowsFonts(Meiryo = windowsFont("Meiryo"))
options(scipen = 999)
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- Source http://www.gold.org/

***

#### Time Series

```{r warning=F,error=F,message=F,echo=F,results='asis'}
n <- 2
fun_fit(obj = goldPriceData,objColumn = n)
fun_generateKnit(objDF = merge(goldPriceData[,c(1,n)],fittedDF[,c(1,3)]),
                 plotNum = n,
                 quantiles = 2,
                 dygraphTitle = colnames(goldPriceData)[n])
eval(parse(text = paste0('dygraphPlot', n)))
cat('<hr>')
n <- 3
fun_fit(obj = goldPriceData,objColumn = n)
fun_generateKnit(objDF = merge(goldPriceData[,c(1,n)],fittedDF[,c(1,3)]),
                 plotNum = n,
                 quantiles = 2,
                 dygraphTitle = colnames(goldPriceData)[n])
eval(parse(text = paste0('dygraphPlot', n)))
cat('<hr>')
n <- 4
fun_fit(obj = goldPriceData,objColumn = n)
fun_generateKnit(objDF = merge(goldPriceData[,c(1,n)],fittedDF[,c(1,3)]),
                 plotNum = n,
                 quantiles = 2,
                 dygraphTitle = colnames(goldPriceData)[n])
eval(parse(text = paste0('dygraphPlot', n)))
```

***

#### Historical Volatility
- `r objColumn <- 2;colnames(goldPriceData)[objColumn]`
- Width:`r width <- 30;width`

```{r warning=F,error=F,message=F,echo=F,results='asis'}
n <- 5
fun_historicalVolatility(obj = goldPriceData,objColumn = objColumn,width = width)
fun_generateKnit(objDF = historicalVolatility,
                 plotNum = n,
                 quantiles = 2,
                 group = 0,
                 dygraphTitle = paste0(colnames(goldPriceData)[objColumn],
                                       ':',
                                       colnames(historicalVolatility)[2]))
eval(parse(text = paste0('dygraphPlot', n)))
```

***

```{r warning=F,error=F,message=F,echo=F,results='asis'}
ccc <- 2
fun_timeSeriesDataFundamentalStatistics(obj = goldPriceData,objCCC = ccc)
fun_markdownTable(obj = tail(timeSeriesdata[,c(1,ccc)]))
cat('\n\n<hr>')
fun_markdownTable(obj = tail(timeSeriesdataDiff[,c(1,ccc)]))
cat('\n\n<hr>')
fun_markdownTable(obj = resultADF,rownames = T)
cat('\n\n<hr>')
fun_markdownTable(obj = resultADFdiff,rownames = T)
cat('\n\n<hr>')
fun_markdownTable(obj = statisticsTable,rownames = T)
cat('\n\n<hr>')
fun_markdownTable(obj = statisticsTableDiff,rownames = T)
cat('\n\n<hr>')
fun_markdownTable(obj = statisticsTableDiffMaxMin,rownames = F)
cat('\n\n<hr>')
fun_markdownTable(obj = statisticsTableDiffRatio,rownames = T)
cat('\n\n<hr>')
fun_markdownTable(obj = statSequencePositive,rownames = F)
cat('\n\n<hr>')
fun_markdownTable(obj = statSequenceNegative,rownames = F)
cat('\n\n<hr>')
```

<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
