---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-USTradeInGoodsByCountry.html')) })

title : 'U.S. Trade In Goods By Country'
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 4
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<style>.main-container {max-width : 1000px;}</style>
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r,warning=F,error=F,message=F,echo=F}
library(RCurl)
functionList <-
  read.csv(file = 'https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/functionList.csv',
           header = F,
           as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", functionList[iii,1]),
    ssl.verifypeer = F
  )
  eval(parse(text = script))
}
```

```{r,warning=F,error=F,message=F,echo=F,results='hide'}
script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/importUSTradeInGoodsByCountry.r",
    ssl.verifypeer = F
  )
eval(parse(text = script))
```

```{r warning=F,error=F,message=F,echo=F,results='hold'}
dateFormat <- '%Y/%m'
objCountry <-
  grep('japan',countryS,ignore.case = T)
fun_latestResult(obj = TradeInGoodsByCountry[[objCountry]],objColumn = c(2,3,4),dateFormat = dateFormat) 
dataTitle <- 
  paste0('U.S. Trade In Goods By Country:', 
         latestResult)
dataSource <- 'U.S. Census Bureau'
windowsFonts(Meiryo = windowsFont("Meiryo"))
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- 単位:百万ドル(名目値)、非季節調整値
- https://www.census.gov/foreign-trade/data/index.html
- https://www.census.gov/foreign-trade/statistics/historical/index.html
- https://www.census.gov/foreign-trade/balance/index.html
- https://www.census.gov/foreign-trade/statistics/country/index.html

***
#### Compare Japan and China
##### In millions of U.S. dollars on a nominal basis, not seasonally adjusted

- Import

```{r warning=F,error=F,message=F,echo=F,results='hold'}
objCountry <-
  grep('japan|china',countryS,ignore.case = T)
compareData <-
  merge(TradeInGoodsByCountry[[objCountry[1]]],
        TradeInGoodsByCountry[[objCountry[2]]],
        by = 'Date')
importDF <-
  compareData[,c(1,grep('import',colnames(compareData),ignore.case = T))]
n <- 1
fun_generateKnit(objDF = importDF,plotNum = n,group = 0)
eval(parse(text = paste0('dygraphPlot', n)))
```

***
- Export

```{r warning=F,error=F,message=F,echo=F,results='hold'}
exportDF <-
  compareData[,c(1,grep('export',colnames(compareData),ignore.case = T))]
n <- 1
fun_generateKnit(objDF = exportDF,plotNum = n,group = 0)
eval(parse(text = paste0('dygraphPlot', n)))
```

***
- Balance

```{r warning=F,error=F,message=F,echo=F,results='hold'}
balanceDF <-
  compareData[,c(1,grep('balance',colnames(compareData),ignore.case = T))]
n <- 1
fun_generateKnit(objDF = balanceDF,plotNum = n,group = 0)
eval(parse(text = paste0('dygraphPlot', n)))
```

***
#### World
##### In millions of U.S. dollars on a nominal basis, not seasonally adjusted
- Export & Import

```{r warning=F,error=F,message=F,echo=F,results='hold'}
objCountry <-
  grep('world',countryS,ignore.case = T)
compareData <-
  merge(TradeInGoodsByCountry[[objCountry[1]]],
        TradeInGoodsByCountry[[objCountry[2]]],
        by = 'Date')
worldDF <-
  compareData[,c(1,grep('import|export',colnames(compareData),ignore.case = T))]
n <- 1
fun_generateKnit(objDF = worldDF,plotNum = n,group = 0)
eval(parse(text = paste0('dygraphPlot', n)))
```

***
- Balance

```{r warning=F,error=F,message=F,echo=F,results='hold'}
objCountry <-
  grep('world',countryS,ignore.case = T)
compareData <-
  merge(TradeInGoodsByCountry[[objCountry[1]]],
        TradeInGoodsByCountry[[objCountry[2]]],
        by = 'Date')
worldDF <-
  compareData[,c(1,grep('balance',colnames(compareData),ignore.case = T))]
n <- 1
fun_generateKnit(objDF = worldDF,plotNum = n,group = 0)
eval(parse(text = paste0('dygraphPlot', n)))
```

***
#### Latest`r tailN <- 3;tailN`months

```{r warning=F,error=F,message=F,echo=F,results='asis'}
tDF <-
  fun_transposeDataFrame(obj = grandData,dateFormat = dateFormat,colName = 'Country/Region',tailN = tailN)
fun_dataTable(obj = tDF,orderDirection = 'asc',needID = 1,dateFormat = 0)
```

***
<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
