---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');htmlName<-'CreditToTheNonfinancialSector';rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[4,1],'am-consulting.co.jp-',htmlName,'.html')) })

title : "Credit To The Nonfinancial Sector"
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 5
    fig_width: 9
    keep_md: no
    md_extensions: -ascii_identifiers 
    includes:
       in_header: insertHeader.html
    self_contained: false
---

```{r setup, include=FALSE}
tag <-
  read.csv(file = 'https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/components/insertHeader.csv',header = F,fileEncoding = 'UTF8')
tagTxt <- ''
for(rrr in 1:nrow(tag)){
  tagTxt <- paste0(tagTxt,tag[rrr,1],'\n')
}
insertFile <- file("insertHeader.html")
writeLines(text = tagTxt,con = insertFile)
close(insertFile)
```

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

<link rel="stylesheet" href="http://rawgit.com/am-consulting/am-consulting.github.io/master/components/jquery-responsive-tables/responsive-tables.css" type="text/css">

```{r set-options, echo=F, cache=F}
options(width = 900)
```

```{r warning = F, error = F, message = F, echo = F}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r warning=F,error=F,message=F,echo=F}
script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/importCreditToTheNonfinancialSector.r",
    ssl.verifypeer = FALSE
  )
eval(parse(text = script))
dataSet <- CreditToTheNonfinancialSector
```

```{r warning=F,error=F,message=F,echo=F,results='hold'}
dateFormat <- '%Y-%m-%d'
dataTitle <- 
  paste0('Credit To The Nonfinancial Sector/世界各国の非金融部門債務残高対国内総生産比:',
         format(tail(dataSet[,1],1),dateFormat))
dataSource <- 
  'Bank for International Settlements'
windowsFonts(Meiryo = windowsFont("Meiryo"))
options(scipen = 999)
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- Source http://www.bis.org/statistics/totcredit.htm?m=6%7C326
- 『They capture the outstanding amount of credit at the end of the reference quarter. 』(BIS)
- Non financial sector =  General government + Households and NPISHs + Non-financial corporations
- Private non-financial sector = Households and NPISHs + Non-financial corporations
- NPISHs:対家計民間非営利団体/Non-profit institution serving households 

***

```{r warning=F,error=F,message=F,echo=F,results='asis'}
titleN <-
  c('Non financial sector',
    'General government - All sectors - Market value',
    'General government - All sectors - Nominal value',
    'Households and NPISHs',
    'Non-financial corporations',
    'Private non-financial sector - All sectors',
    'Private non-financial sector - Banks, total')
```

```{r warning=F,error=F,message=F,echo=F,results='asis'}
for(iii in seq(length(titleN))){
  objCol <- 
    grep(titleN[iii],colnames(dataSet),ignore.case = T)
  buf <- dataSet[,c(1,objCol)]
  buf <- buf[,-grep('using PPP exchange rates',colnames(buf))]
  colnamesShort <- 
    gsub('([^-]+)\\s-(.+)','\\1',colnames(buf)[-1])
  commonTxt <- 
    unique(gsub('([^-]+)\\s-\\s(.+)','\\2',colnames(buf)[-1]))
  colnames(buf)[-1] <- colnamesShort
  obj0 <- 
    fun_transposeDataFrame(obj = buf,tailN = 5,dateFormat = dateFormat,colName = 'Country/Region')
  obj <-
    obj0[order(obj0[,ncol(obj0)],decreasing = T),]
  cat('#### ',commonTxt,'\n')
  cat(fun.html.table(obj = obj))
  cat('\n<hr>\n')
}
```

#### Japan vs USA vs China

```{r warning=F, error=F, message=F, echo=F, results='asis'}
objCol <- 
  grep('japan|china|united states',colnames(dataSet),ignore.case = T)
buf <- na.omit(dataSet[,c(1,objCol)])
lineColor <- c('blue','black','red')
```

```{r warning=F, error=F, message=F, echo=F, results='asis'}
fun_reshape <- function(iii = 1){
  objCol <- 
    grep(titleN[iii],colnames(buf),ignore.case = T)
  obj <- buf[,c(1,objCol)]
  colnamesShort <- 
    gsub('([^-]+)\\s-(.+)','\\1',colnames(obj)[-1])
  commonTxt <- 
    unique(gsub('([^-]+)\\s-\\s(.+)','\\2',colnames(obj)[-1]))
  colnames(obj)[-1] <- colnamesShort
  returnDF <-
    list("obj" = obj, "commonTxt" = commonTxt)
  return(returnDF)
}
```

```{r warning=F, error=F, message=F, echo=F, results='asis'}
n <- 1
returnData <- fun_reshape(iii = n)
fun_generateKnit(objDF = returnData$obj,plotNum = n,
                 dygraphTitle = returnData$commonTxt,group = 0,colors = lineColor)
eval(parse(text = paste0('dygraphPlot', n, ' %>% ', primeMinisterOfJapan_dygraph)))
cat('<hr>')
```

```{r warning=F, error=F, message=F, echo=F, results='asis'}
n <- 2
returnData <- fun_reshape(iii = n)
fun_generateKnit(objDF = returnData$obj,plotNum = n,
                 dygraphTitle = returnData$commonTxt,group = 0,colors = lineColor)
eval(parse(text = paste0('dygraphPlot', n, ' %>% ', primeMinisterOfJapan_dygraph)))
cat('<hr>')
```

```{r warning=F, error=F, message=F, echo=F, results='asis'}
n <- 3
returnData <- fun_reshape(iii = n)
fun_generateKnit(objDF = returnData$obj,plotNum = n,
                 dygraphTitle = returnData$commonTxt,group = 0,colors = lineColor)
eval(parse(text = paste0('dygraphPlot', n, ' %>% ', primeMinisterOfJapan_dygraph)))
cat('<hr>')
```

```{r warning=F, error=F, message=F, echo=F, results='asis'}
n <- 4
returnData <- fun_reshape(iii = n)
fun_generateKnit(objDF = returnData$obj,plotNum = n,
                 dygraphTitle = returnData$commonTxt,group = 0,colors = lineColor)
eval(parse(text = paste0('dygraphPlot', n, ' %>% ', primeMinisterOfJapan_dygraph)))
cat('<hr>')
```

```{r warning=F, error=F, message=F, echo=F, results='asis'}
n <- 5
returnData <- fun_reshape(iii = n)
fun_generateKnit(objDF = returnData$obj,plotNum = n,
                 dygraphTitle = returnData$commonTxt,group = 0,colors = lineColor)
eval(parse(text = paste0('dygraphPlot', n, ' %>% ', primeMinisterOfJapan_dygraph)))
cat('<hr>')
```

```{r warning=F, error=F, message=F, echo=F, results='asis'}
n <- 6
returnData <- fun_reshape(iii = n)
fun_generateKnit(objDF = returnData$obj,plotNum = n,
                 dygraphTitle = returnData$commonTxt,group = 0,colors = lineColor)
eval(parse(text = paste0('dygraphPlot', n, ' %>% ', primeMinisterOfJapan_dygraph)))
cat('<hr>')
```

```{r warning=F, error=F, message=F, echo=F, results='asis'}
n <- 7
returnData <- fun_reshape(iii = n)
fun_generateKnit(objDF = returnData$obj,plotNum = n,
                 dygraphTitle = returnData$commonTxt,group = 0,colors = lineColor)
eval(parse(text = paste0('dygraphPlot', n, ' %>% ', primeMinisterOfJapan_dygraph)))
cat('<hr>')
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
username <- Sys.info()['user']
pathToFile <- paste0('C:/Users/', username,'/Desktop/pathToCSV/')
setwd(pathToFile)
fileName <- 'defaultPath.csv'
buf <-
  read.csv(file = fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,
           fileEncoding = 'utf-8',quote = "\"")
pathOutputTOchart <- paste0("C:/Users/", username, buf[4,1])
setwd(pathOutputTOchart)
#---------------------------------------------------
library(ggplot2)
caption.subtitle.size <- 14
plot.text.size <- 13
base.size <- 11
objCol0 <- 
  grep('japan|china|united states',colnames(dataSet),ignore.case = T)
obj0 <- dataSet[,c(1,objCol0)]
objCol <- 
  grep(titleN[4],colnames(obj0),ignore.case = T)
obj <- na.omit(obj0[,c(1,objCol)])
col <- c('#4169e1','#00008b','#6495ed')
fun_plot <- function(obj.col = 2){
  date.range <- paste0(range(obj[,1]),collapse = '~')
  g <- ggplot(data = obj,aes(x = obj[,1],y = obj[,obj.col]))
  g <- g + theme_grey(base_size = base.size,base_family = 'Meiryo')
  g <- g + geom_line(col=col[obj.col-1]) + geom_point(col=col[obj.col-1]) + geom_smooth(col='red')
  g <- g + ggtitle(label = paste0(paste0(gsub('([^-| ]+).+','\\1',colnames(obj)[obj.col]),':',titleN[4]),
                                  '\n',date.range,'\nSource:',dataSource))
  g <- g + scale_y_continuous(name = '%',breaks = scales::pretty_breaks(20),sec.axis = dup_axis())
  g <- g + xlab(label = '')
  g <- g + theme(plot.title = element_text(hjust = 0.5))
  g <- g + theme(axis.text.x = element_text(size = plot.text.size,angle = 0))
  g <- g + theme(axis.text.y = element_text(size = plot.text.size,angle = 0))
  g <- g + theme(plot.subtitle = element_text(size = caption.subtitle.size,angle = 0))
  g <- g + theme(plot.caption = element_text(size = caption.subtitle.size,angle = 0))
  print(g)
}
pngFile <-
  paste0(htmlName, "1.png")
png(file = pngFile, width = 1000, height = 600)
fun_plot(obj.col = 2)
dev.off()
pngFile <-
  paste0(htmlName, "2.png")
png(file = pngFile, width = 1000, height = 600)
fun_plot(obj.col = 3)
dev.off()
pngFile <-
  paste0(htmlName, "3.png")
png(file = pngFile, width = 1000, height = 600)
fun_plot(obj.col = 4)
dev.off()
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fun_outputMD(tags = '非金融部門債務残高対国内総生産比,BIS',
             objDF = fun_summaryByName(obj = obj),
             htmlName = htmlName,
             image1 = 1,image2 = 1,image3 = 1,
             title = dataTitle,
             tableTitle = colnames(obj)[2],
             tableName = '',
             buf.row = 4)
fun_updateURLcsv()
fun_updateURLcsv.olive()
```

<script src="http://rawgit.com/am-consulting/am-consulting.github.io/master/components/jquery-responsive-tables/jquery.responsive-tables.js"></script>
<script src="http://rawgit.com/am-consulting/am-consulting.github.io/master/components/jquery-responsive-tables/app.js"></script>

<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
