---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-DGSversusJGB.html')) })
title : "Treasury Constant Maturity Rate vs. Japanese Government Bonds Interest Rate"
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 5
    fig_width: 9
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 900px;}</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan

本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000)
```

```{r,warning=F,error=F,message=F,echo=F}
library(knitr)
```

```{r,warning=F,error=F,message=F,results='hold',echo=F}
dataTitle <- paste0('日米国債金利差')
dataSource <- '財務省、Federal Reserve Bank of St.Louis'
windowsFonts(Meiryo = windowsFont("Meiryo"))
options(scipen = 999)
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`

***

```{r warning=F,error=F,message=F,echo=F}
eventData<-c(
  "2016-11-09", "United States presidential election of 2016",
  "2008-09-15", "Bankruptcy of Lehman Brothers",
  "2011-03-11", "Tohoku earthquake and tsunami"
)
eventData <- iconv(eventData,'shift_jis','utf8')
eventDataDF <- data.frame()
for (eee in seq(0, length(eventData) / 2 - 1, by = 1)) {
  eventDataDF[eee + 1, 1] <- eventData[eee * 2 + 1]
  eventDataDF[eee + 1, 2] <- eventData[eee * 2 + 2]
}
eventDataDF[, 1] <- as.Date(eventDataDF[, 1])
eventDataDF[, 2] <- paste0(eventDataDF[, 1],':',eventDataDF[,2])
colnames(eventDataDF) <- c('Date', 'Event')
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
library(quantmod)
fredData <- list()
cnt <- 0
treasuryRate <-
  c(
    'DGS1',  '01-Year Treasury Constant Maturity Rate(%)',
    'DGS2',  '02-Year Treasury Constant Maturity Rate(%)',
    'DGS3',  '03-Year Treasury Constant Maturity Rate(%)',
    'DGS5',  '05-Year Treasury Constant Maturity Rate(%)',
    'DGS7',  '07-Year Treasury Constant Maturity Rate(%)',
    'DGS10', '10-Year Treasury Constant Maturity Rate(%)',
    'DGS20', '20-Year Treasury Constant Maturity Rate(%)',
    'DGS30', '30-Year Treasury Constant Maturity Rate(%)'
  )
for (lll in seq(1, length(treasuryRate), by = 2)) {
  cnt <- cnt + 1
  tmp <- getSymbols(treasuryRate[lll], src = 'FRED', auto.assign = F)
  tmp <-
    data.frame(Date = as.Date(index(tmp)),tmp[, 1],check.names = F,row.names = NULL,stringsAsFactors = F)
  colnames(tmp)[2] <- treasuryRate[lll + 1]
  fredData[[cnt]] <- tmp
  tail(fredData[[cnt]])
  if(lll == 1){allDGSData <- tmp}else{allDGSData <- merge(allDGSData, tmp, by='Date', all=T)}
}
```

- DGS:Daily Treasury Constant Maturity Rate(%)
- JGB:Japanese Government Bonds Interest Rate(%)

```{r warning=F,error=F,message=F,echo=F,results='hide'}
library(RCurl)
script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/Rscript/master/Rscript_JGBInterestRate.r",
    ssl.verifypeer = F)
eval(parse(text = script))
colnames(jgbData)[-1] <- paste0('JGB-',colnames(jgbData)[-1],'(%)')
jgbData0 <- jgbData
jgbData <- na.omit(jgbData0)
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
rawData <- diffData <- list()
totalData <- merge(allDGSData,jgbData0,by = 'Date',all = T)
for(ccc1 in 2:(ncol(allDGSData))){
  n <- as.numeric(substring(colnames(allDGSData)[ccc1],1,2))  
  ccc2 <- grep(paste0('\\b',n,'y\\b'),colnames(totalData),ignore.case = T)  
  rawData[[ccc1-1]] <- na.omit(totalData[,c(1,ccc1,ccc2)])
  diffData[[ccc1-1]] <- 
    data.frame(Date=rawData[[ccc1-1]][,1],rawData[[ccc1-1]][,2]-rawData[[ccc1-1]][,3],check.names = F,stringsAsFactors = F)
  colnames(diffData[[ccc1-1]])[2] <- paste0(colnames(rawData[[ccc1-1]])[2],' - ',colnames(rawData[[ccc1-1]])[3])
}
```

```{r warning=F,error=F,message=F,echo=F}
library(dygraphs)
dyBarChart <- function(dygraph) {
  dyPlotter(dygraph = dygraph,
            name = "BarChart",
            path = system.file("examples/plotters/barchart.js",package = "dygraphs"))
}
dyUnzoom <-function(dygraph) {
  dyPlugin(dygraph = dygraph,
           name = "Unzoom",
           path = system.file("examples/plugins/unzoom.js", package = "dygraphs"))
}
dyCrosshair <- function(dygraph,direction = c("both", "horizontal", "vertical")) {
  dyPlugin(dygraph = dygraph,
           name = "Crosshair",
           path = system.file("examples/plugins/crosshair.js",package = "dygraphs"),
           options = list(direction = match.arg(direction)))
}
fun_dygraph <- function(obj = buf){
  timeSeries0 <- na.omit(obj)
  timeSeries0 <- subset(timeSeries0,as.Date('2007-1-1')<=timeSeries0[,1])
  timeSeries <- xts(timeSeries0[,-1], order.by=timeSeries0[,1])
  colnames(timeSeries) <- colnames(timeSeries0)[-1]
  dygraph(timeSeries,main = paste0(colnames(timeSeries0)[-1],collapse = ' × '))  %>% 
    dyLegend(width = 600) %>% dyRangeSelector() %>% 
    dyUnzoom() %>% dyCrosshair(direction = "both") %>% 
    dyLimit(0, color = "red") %>% 
    dyEvent(eventDataDF[1,1], eventDataDF[1,2], labelLoc = "bottom") %>%
    dyEvent(eventDataDF[2,1], eventDataDF[2,2], labelLoc = "bottom") %>%
    dyEvent(eventDataDF[3,1], eventDataDF[3,2], labelLoc = "bottom")
  }
```

```{r,warning=F,error=F,message=F,echo=F,include=F}
out1 = NULL
for (iii in 1:length(rawData)) {
  knit_expanded <-
    paste0(
      "\n```{r results='asis', echo=F}\n\n",
      "cat(paste0('<h4>',paste0(colnames(rawData[[",iii,"]][-1]),collapse = ' × '),'</h4>'))\n\n",
      "fun_dygraph(obj = rawData[[",iii,"]])\n\n",
      "fun_dygraph(obj = diffData[[",iii,"]])\n\ncat('<hr>')\n\n```"
    )
  out1 = c(out1, knit_expanded)
}
```
`r paste(knit(text = out1), collapse = '\n')`

<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
