---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-DGS.html')) })

title : 'Treasury Constant Maturity Rate'
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:    
    fig_height: 5
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 900px;}</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan

本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
#options(width = 1000)
```

```{r,warning=F,error=F,message=F,echo=F}
library(quantmod)
library(DT)
library(knitr)
```

```{r warning = F, error = F, message = F, echo = F}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r,warning=F,error=F,message=F,echo=F}
fredData <- list()
cnt <- 0
treasuryRate <-
  c(
    'DGS1',  '1-Year Treasury Constant Maturity Rate(%)',
    'DGS2',  '2-Year Treasury Constant Maturity Rate(%)',
    'DGS3',  '3-Year Treasury Constant Maturity Rate(%)',
    'DGS5',  '5-Year Treasury Constant Maturity Rate(%)',
    'DGS7',  '7-Year Treasury Constant Maturity Rate(%)',
    'DGS10', '10-Year Treasury Constant Maturity Rate(%)',
    'DGS20', '20-Year Treasury Constant Maturity Rate(%)',
    'DGS30', '30-Year Treasury Constant Maturity Rate(%)'
  )
for (lll in seq(1, length(treasuryRate), by = 2)) {
  cnt <- cnt + 1
  tmp <- getSymbols(treasuryRate[lll], src = 'FRED', auto.assign = F)
  tmp <-
    data.frame(
      Date = as.Date(index(tmp)),
      tmp[, 1],
      check.names = F,
      row.names = NULL,
      stringsAsFactors = F
    )
  colnames(tmp)[2] <- treasuryRate[lll + 1]
  fredData[[cnt]] <- tmp
  tail(fredData[[cnt]])
  if(lll == 1){allData <- tmp}else{allData <- merge(allData, tmp, by='Date', all=T)}
}
```

```{r,warning=F,error=F,message=F,results='hold',echo=F}
dateFormat <- '%Y-%m-%d'
fun_latestResult(obj = allData,objColumn = c(7,9),dateFormat = dateFormat)
dataTitle <-
  paste0('米国債金利:',latestResult)
dataSource <- 'Federal Reserve Bank of St. Louis'
windowsFonts(Meiryo = windowsFont("Meiryo"))
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`

***

```{r,warning=F,error=F,message=F,results='hold',echo=F}
for (iii in 1:length(fredData)) {
  obj <- na.omit(fredData[[iii]])
  cat(paste(range(obj[, 1]), collapse = ' ~ '), '\n')
  print(apply(obj[, 2, drop = F], 2, summary))
  cat('\n\n')
}
```

```{r,warning=F,error=F,message=F,echo=F}
rAmCharts::amBoxplot(allData[, -1], horiz = T)
```
<hr>
```{r,warning=F,error=F,message=F,echo=F,fig.height=6,fig.width=10}
# dataSet <- na.omit(allData[, c(1, 3, 7)])
# lineColor <- c('blue', 'red', 'green', 'orange')
# maxValue <- max(dataSet[, -1])
# minValue <- min(dataSet[, -1])
# par(mar = c(3, 3, 4, 1), family = 'Meiryo')
# plot(
#   dataSet[, 1],
#   dataSet[, 2],
#   type = 'l',
#   col = lineColor[1],
#   xlab = '' ,
#   ylab = '' ,
#   panel.first = grid(nx = NULL, ny = NULL, lty = 2, equilogs = T) ,
#   xaxt = 'n',
#   ylim = c(minValue, maxValue),
#   main = paste('Treasury Constant Maturity Rate(%)\nSource:', dataSource,
#                '\n',paste(range(dataSet[, 1]), collapse = ' ~ ')),
#   cex.axis = 1,
#   cex.lab = 1,
#   cex.main = 1,
#   lwd = 1
# )
# lines(dataSet[, 1], dataSet[, 3], col = lineColor[2])
# graphics::legend(
#   'topleft',
#   col = lineColor[1:2],
#   lty = 1,
#   legend = c(colnames(dataSet)[2:3]),
#   cex = 1,
#   bty = 'n'
# )
# axis.Date(side = 1, at = dataSet[, 1], format = dateFormat, padj = 1, cex.axis = 1.0)
```

```{r warning=F,error=F,message=F,echo=F,fig.height=5}
dataSet <- na.omit(allData[, c(1, 3, 5, 7)])
n <- 1
fun_generateKnit(objDF = dataSet,
                 plotNum = n,
                 dygraphTitle = paste('Treasury Constant Maturity Rate(%)<br>Source:', 
                                      dataSource,
                                      '<br>',
                                      paste(range(dataSet[, 1]), collapse = ' ~ ')),
                 group = 0)
eval(parse(text = paste0('dygraphPlot',n)))
```

<hr>
```{r,warning=F,error=F,message=F,echo=F,fig.height=5}
xRange <- paste0(c(1, 2, 3, 5, 7, 10, 20, 30), 'Y')
yieldCurve <- na.omit(allData)
maxValue <- max(yieldCurve[, -1])
minValue <- min(yieldCurve[, -1])
#nrow(yieldCurve)
buf01 <- unlist(head(yieldCurve, 1))
buf02 <- unlist(yieldCurve[1000, ])
buf03 <- unlist(yieldCurve[2000, ])
buf04 <- unlist(yieldCurve[3000, ])
buf05 <- unlist(yieldCurve[4000, ])
buf06 <- unlist(tail(yieldCurve, 1))
par(mar = c(3, 3, 4, 1), family = 'Meiryo', font.main = 1)
plot(
  buf01[-1],
  ylim = c(minValue, maxValue),
  type = 'o',
  col = 1 ,
  xlab = '' ,
  ylab = '' ,
  panel.first = grid(nx = NULL, ny = NULL, lty = 2, equilogs = T) ,
  xaxt = 'n',
  main = paste('Treasury Constant Maturity Rate(%) - Yield Curve\nSource:', dataSource),
  cex.axis = 1,
  cex.lab = 1,
  cex.main = 1,
  lwd = 1,
  pch = 20,
  cex = 2
)
lines(buf02[-1], type = 'o', col = 2, lwd = 1, pch = 20, cex =2)
lines(buf03[-1], type = 'o', col = 3, lwd = 1, pch = 20, cex =2)
lines(buf04[-1], type = 'o', col = 4, lwd = 1, pch = 20, cex =2)
lines(buf05[-1], type = 'o', col = 5, lwd = 1, pch = 20, cex =2)
lines(buf06[-1], type = 'o', col = 6, lwd = 1, pch = 20, cex =2)
graphics::legend(
  'topleft',
  col = 1:6,
  lty = 1,
  legend = as.Date(c(buf01[1],buf02[1],buf03[1],buf04[1],buf05[1],buf06[1])),
  cex = 1,
  bty = 'n',
  lwd = 2
)
axis(side = 1, at = 1:length(xRange), labels = xRange)
```
<hr>
```{r,warning=F,error=F,message=F,echo=F,results='asis'}
fun_dataTable(obj = tail(na.omit(allData),500),title = 'Treasury Constant Maturity Rate(%)')
```

```{r,warning=F,error=F,message=F,echo=F,results='hide'}
buf <- t(tail(allData, 4))
buf1 <- data.frame(rownames(buf), buf, check.names = F, row.names = NULL)
colnames(buf1) <- unlist(buf1[1, ])
buf2 <- buf1[-1, ]
colnames(buf2)[1] <- 'Type'
knitr::kable(buf2, row.names = F)
```

<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
