---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');htmlName<-'MonthlyStatementOfThePublicDebtOfTheUnitedStates';rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-',htmlName,'.html')) })

title : 'Monthly Statement Of The Public Debt Of The United States'
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 4
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers
    includes:
       in_header: insertHeader.html
    self_contained: false
---

```{r setup, include=FALSE}
# https://stackoverflow.com/questions/43329230/r-markdown-add-tag-to-head-of-html-output/43334558#43334558
insertFile <- file("insertHeader.html")
writeLines('
<link rel="shortcut icon" href="http://knowledgevault.saecanet.com/charts/indicator/favicon-bar-chart.ico">
',
insertFile)
close(insertFile)
```

<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 1000px;}</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000)
```

```{r,warning=F,error=F,message=F,echo=F}
library(RCurl)
functionList <-
  read.csv(
    file = 'https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/functionList.csv',
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(
      paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", functionList[iii,1]),
      ssl.verifypeer = F
      )
  eval(parse(text = script))
}
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
library(RCurl);library(knitr)
script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/importMonthlyStatementOfThePublicDebtOfTheUnitedStates.r",
    ssl.verifypeer = F
  )
eval(parse(text = script))

script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/Rscript/master/importMajorForeignHoldersUSTreasury.r",
    ssl.verifypeer = F
  )
eval(parse(text = script))

windowsFonts(Meiryo=windowsFont("Meiryo"))
options(scipen=100)
dateFormat <- '%Y-%m'
```

```{r warning=F,error=F,message=F,echo=F,results='hold'}
fun_MSPD(breakYear = 2017, breakMonth = 7)
# 2009-01は計算式
```

```{r warning=F,error=F,message=F,echo=F,results='hold'}
MSPD0 <- MSPD
MSPD0[,2] <- MSPD0[,2]*10^-6
fun_latestResult(MSPD0,dateFormat = dateFormat)
dataTitle <- 
  paste0('米国の公的債務(兆ドル):',latestResult)
dataSource <- 'U.S. Department of the Treasury'
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- Source https://www.treasurydirect.gov/govt/reports/pd/mspd/mspd.htm

***

#### Time Series
- Unit:Trillion $

```{r warning=F,error=F,message=F,echo=F,results='asis'}
tmpDF <- MSPD
tmpDF[,-1] <- tmpDF[,-1] * 10^-6
mdDF <- tmpDF
n <- 1
fun_generateKnit(objDF = tmpDF,
                 plotNum = n,
                 barPlot = 0,
                 group = 0,
                 quantiles = 2,
                 dygraphTitle = 'THE PUBLIC DEBT OF THE UNITED STATES(Trillion $) / 米国の公的債務(兆ドル)')
eval(parse(text = paste0('dygraphPlot', n)))
```

```{r warning=F,error=F,message=F,echo=F,results='asis'}
fun_markdownTable(obj = fun_transposeDataFrame(obj = tmpDF,dateFormat = dateFormat))
```

***

```{r warning=F,error=F,message=F,echo=F,results='hide'}
mergeData <-
  merge(MSPD, allData[,grep('date|grand|japan|china',colnames(allData),ignore.case = T)],by='Date')
ccc1 <- ncol(mergeData) + 1
ccc2 <- 2
ccc3 <- 5
mergeData[,ccc1] <- mergeData[,ccc2] - mergeData[,ccc3]
colnames(mergeData)[ccc1] <- 'U.S. citizens and American entities'
mergeData[,-1] <- mergeData[,-1] * 10^-6
```

#### Composition
- `r paste0(colnames(mergeData)[ccc1],':',colnames(mergeData)[ccc2],' minus ',colnames(mergeData)[ccc3])`
- Grand Total: Grand Total of Major Foreign Holders of U.S. Treasury Securities
- Unit:Trillion $

```{r warning=F,error=F,message=F,echo=F,results='asis'}
fun_markdownTable(obj = fun_transposeDataFrame(obj = mergeData,dateFormat = dateFormat,tailN = 5))
```

***
- Percent

```{r warning=F,error=F,message=F,echo=F,results='asis'}
mergeDataRatio <- mergeData
mergeDataRatio[,-1] <- round(mergeDataRatio[,-1]/mergeDataRatio[,ccc2]*100,1)
fun_markdownTable(obj = fun_transposeDataFrame(obj = mergeDataRatio,dateFormat = dateFormat,tailN = 5))
```

- Time Series Chart for Composition Ratio of U.S. citizens and American entities

```{r warning=F,error=F,message=F,echo=F,results='asis'}
n <- 2
fun_generateKnit(objDF = mergeDataRatio[,c(1,ccc1)],plotNum = n,group = 0,quantiles = 2)
eval(parse(text = paste0('dygraphPlot', n)))
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fun_preparePlot()
pngFile <-
  paste0(htmlName, ".png")
png(file = pngFile, width = 1000, height = 600)
##################
obj <- fun_makeDiffRatioTable(obj = mdDF)
fun_plotTimeSeries(obj = obj,
                   typeL = 'h',typeR = 'o',
                   dateFormat = dateFormat,
                   chartType = 0,dataTitle = 'Year over Year(%)',
                   dataSource = dataSource,
                   fitLcolor = 2,fitlwdL = 3,cexL = 1.5,
                   fitRcolor = 2,fitlwdR = 3,cexR = 1.5,
                   mar = c(5,4,6,2),needLefLab = 0)
abline(h = 0,col = 'red',lwd = 2)
dev.off()
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fun_outputMD(tags = 'U.S. Department of the Treasury,米国の公的債務',
             objDF = tail(obj,10),
             htmlName = htmlName,
             image1 = 1,
             title = dataTitle,
             tableTitle = 'Year over Year(%)',
             tableName = 'Total Public Debt Outstanding')
fun_updateURLcsv()
```

***
<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
