---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-ADPvsDOL.html')) })

title : 'Comparison between U.S. ADP Nonfarm Employment Change and U.S. Nonfarm Payrolls'
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 4
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 1000px;}</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 500)
```

```{r warning = F, error = F, message = F, echo = F}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r,warning=F,error=F,message=F,echo=F}
script <-
  getURL(url = "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/importADP.r",
         ssl.verifypeer = F)
eval(parse(text = script))
```

```{r,warning=F,error=F,message=F,echo=F}
library(quantmod)
tmp <- getSymbols('PAYEMS',src='FRED',auto.assign=F)
tmp <-
  data.frame(
    Date = as.Date(index(tmp)),
    tmp[, 1],
    check.names = F,
    row.names = NULL,
    stringsAsFactors = F
  )
colnames(tmp)[2] <-
  'All Employees: Total Nonfarm Payrolls:Change, Thousands of Persons,Seasonally Adjusted'
fun_makeDiffTable(obj = tmp,lag = 1)
DOLreport <- diffDF
```

```{r,warning=F,error=F,message=F,results='hold',echo=F}
objColumn <- tail(grep('total',colnames(ADPreport),ignore.case = T),1)
fun_latestResult(obj = ADPreport,objColumn = objColumn)
dataTitle <- 
  paste0('ADP雇用統計と米国労働省雇用統計の比較:最新のADP雇用統計',latestResult)
dataSource <- 'Automatic Data Processing, Inc.'
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- Source http://www.adpemploymentreport.com/

***

```{r warning=F,error=F,message=F,echo=F,results='asis'}
mergeData <- 
  na.omit(merge(ADPreport[,c(1,objColumn)],DOLreport,by='Date'))
mergeData$Sign <- 
  ifelse(0 < mergeData[,2]*mergeData[,3],'○:Same','×:Difference')
mergeData$`DOL minus ADP` <- 
  mergeData[,3] - mergeData[,2]
```

```{r warning=F,error=F,message=F,echo=F,results='asis'}
n <- 10
fun_generateKnit(objDF = ADPreport[,c(1,objColumn)],
                 plotNum = n,
                 group = 0,
                 barPlot = 1,
                 quantiles = 2,
                 dygraphTitle = colnames(ADPreport)[objColumn])
eval(parse(text = paste0('dygraphPlot', n, ' %>% ', potus_dygraph)))
cat('<hr>')
fun_transposeDataFrame(obj = ADPreport[,c(1,objColumn)],dateFormat = '%Y-%m')
fun_markdownTable(obj = tDF)
```

***

```{r warning=F,error=F,message=F,echo=F,results='asis'}
n <- 1
fun_generateKnit(objDF = mergeData[,c(1:3)],
                 plotNum = n,
                 group = 0,
                 dygraphTitle = 'Comparison between U.S. ADP Nonfarm Employment Change and U.S. Nonfarm Payrolls')
eval(parse(text = paste0('dygraphPlot', n, ' %>% ', potus_dygraph)))
```

***

```{r warning=F,error=F,message=F,echo=F,results='asis'}
fun_dataTable(obj = mergeData[,c(1:3)],menuLength = 5)
cat('<hr>')
fun_dataTable(obj = mergeData[,c(1,4:5)],menuLength = 5)
cat('<hr>')
n <- 3
fun_generateKnit(objDF = mergeData[,c(1,5)],
                 plotNum = n,
                 group = 0,
                 barPlot = 1,
                 quantiles = 2,
                 dygraphTitle = colnames(mergeData)[5])
eval(parse(text = paste0('dygraphPlot', n, ' %>% ', potus_dygraph)))
```

***
#### Whether the sign is the same or not

```{r warning=F,error=F,message=F,echo=F,results='asis'}
table01 <- data.frame()
sameN <- length(grep('same',mergeData$Sign,ignore.case = T))
diffN <- length(grep('difference',mergeData$Sign,ignore.case = T))
table01[1,1] <- '○:Same'
table01[1,2] <- sameN
table01[1,3] <- round(sameN/nrow(mergeData)*100,2)
table01[2,1] <- '×:Difference'
table01[2,2] <- diffN
table01[2,3] <- round(diffN/nrow(mergeData)*100,2)
table01[3,1] <- 'Total'
table01[3,2] <- sameN + diffN
table01[3,3] <- round(sameN + diffN/nrow(mergeData)*100,2)
colnames(table01) <- c('Sign','n','%')
fun_markdownTable(obj = table01)
```

***
#### DOL minus ADP(Unit:thousands)

```{r warning=F,error=F,message=F,echo=F,results='asis'}
table02 <- data.frame()
positiveN <- nrow(subset(mergeData, 0 < mergeData$`DOL minus ADP`))
negativeN <- nrow(subset(mergeData, 0 > mergeData$`DOL minus ADP`))
equalN <- nrow(subset(mergeData, 0 == mergeData$`DOL minus ADP`))
table02[1,1] <- 'Positive'
table02[1,2] <- positiveN
table02[1,3] <- round(positiveN/nrow(mergeData)*100,2)
table02[2,1] <- 'Negative'
table02[2,2] <- negativeN
table02[2,3] <- round(negativeN/nrow(mergeData)*100,2)
table02[3,1] <- 'Equal'
table02[3,2] <- equalN
table02[3,3] <- round(equalN/nrow(mergeData)*100,2)
colnames(table02) <- c('DOL minus ADP','n','%')
fun_markdownTable(obj = table02)
```

***

```{r warning=F,error=F,message=F,echo=F,results='asis'}
fun_transposeDataFrame(obj = mergeData,dateFormat = '%Y-%m',tailN = 3)
fun_markdownTable(obj = na.omit(tDF))
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fun_transposeDataFrame(obj = ADPreport,dateFormat = '%Y-%m',tailN = 5)
fun_markdownTable(obj = tDF)
```

***
<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
