---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');htmlName<-'NICHIGINTANKAN';rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-',htmlName,'.html')) })

title : "Bank of Japan - TANKAN "
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 4
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers
    includes:
       in_header: insertHeader.html
    self_contained: false
---

```{r setup, include=FALSE}
# https://stackoverflow.com/questions/43329230/r-markdown-add-tag-to-head-of-html-output/43334558#43334558
insertFile <- file("insertHeader.html")
writeLines('
<link rel="shortcut icon" href="http://knowledgevault.saecanet.com/charts/indicator/favicon-bar-chart.ico">
',
insertFile)
close(insertFile)
```

<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 1000px;}</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options,echo=F,cache=F}
options(width = 1000)
```

```{r warning = F, error = F, message = F, echo = F}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r,warning=F,error=F,message=F,echo=F}
script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/importTANKAN-2017.r",
    ssl.verifypeer = F
  )
eval(parse(text = script))
```

```{r,warning=F,error=F,message=F,echo=F}
for(iii in 1:8){
  tmp <- get(paste0('NICHIGINTANKAN_',iii))
  if(iii == 1){allData <- tmp}else{allData <- merge(allData,tmp,by='Date',all=T)}
}
```

```{r warning=F,error=F,message=F,echo=F,results='hold'}
dateFormat <- '%Y年%m月期'
fun_latestResult(obj = na.omit(NICHIGINTANKAN_1),dateFormat = dateFormat,objColumn = c(2,6,10))
dataTitle <-
  paste0('日銀短観:',latestResult)
dataSource <- '日本銀行'
windowsFonts(Meiryo = windowsFont("Meiryo"))
options(scipen = 999)
library(knitr)
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`

***

```{r warning=F,error=F,message=F,echo=F,results='asis'}
timeSeriesDF <- allData[c(1,grep('.+業況.+実績',colnames(allData)))]
texDygraph <- vector()
cnt <- 0
for(iii in 2:ncol(timeSeriesDF)){
  obj <- 
    na.omit(timeSeriesDF[,c(1,iii)])
  cnt <- cnt + 1
  fun_generateKnit(objDF = obj, 
                   plotNum = cnt, 
                   barPlot = 1,
                   quantiles = 2,
                   group = 0, 
                   colors = c('blue','red','green'), 
                   dygraphTitle = colnames(obj)[2])
  assign(paste0('knit_expanded', cnt),
         paste0("\n```{r warning=F, error=F, message=F, echo=F, results='asis'}\n\n",
                "eval(parse(text = paste0('dygraphPlot", cnt," %>% ', primeMinisterOfJapan_dygraph)))",
                "\n\ncat('<hr>')\n\n```"),envir = .GlobalEnv)
  texDygraph <- 
    c(texDygraph, paste0('knit_expanded', cnt))
}
```

`r paste(knitr::knit(text = sapply(texDygraph,get)), collapse = '\n')`

```{r warning=F,error=F,message=F,echo=F,results='asis'}
fun_markdownTable(obj = fun_transposeDataFrame(obj = allData,tailN = 3,dateFormat = dateFormat))
```

***
#### 前期比

```{r warning=F,error=F,message=F,echo=F,results='asis'}
fun_markdownTable(obj = fun_transposeDataFrame(obj = fun_makeDiffTable(obj = na.omit(allData),lag = 1),
                                               tailN = 3,dateFormat = dateFormat))
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fun_preparePlot()
pngFile <-
  paste0(htmlName, "1.png")
png(file = pngFile, width = 1000, height = 600)
obj <- na.omit(allData[,c(1,2,6,10)])
lineCol <- c('black','red','blue')
ylim <- c(min(obj[,-1]),max(obj[,-1]))
par(mar=c(4,3,4,1),font.main=1,cex.main=1.2,cex.axis=1.1,family='Meiryo')
plot(obj[,c(1,2)],type='o',pch=20,ylim=ylim,xlab='',ylab='',col=lineCol[1],
     main=paste0('日銀短観\n',paste0(format(range(obj[,1]),dateFormat),collapse = '~')))
lines(obj[,c(1,3)],type='o',pch=20,col=lineCol[2])
lines(obj[,c(1,4)],type='o',pch=20,col=lineCol[3])
grid(nx = NULL, ny = NULL, col = "lightgray", lty = "dotted")
abline(h=0)
graphics::legend(x = 'topleft',col = lineCol,lty = 1,legend = colnames(obj)[-1],cex = 0.9,bty = 'n',lwd = 2)
fun_addTxtToChart(obj = obj,cexTxt = 1,funType = 'min',col = 'black')
dev.off()
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fun_outputMD(tags = '日銀短観',
             objDF = fun_transposeDataFrame(obj = obj,dateFormat = dateFormat,tailN = 3),
             htmlName = htmlName,
             image1 = 1,
             title = dataTitle,
             tableTitle = '直近3期',
             tableName = '日銀短観')
fun_updateURLcsv()
```

***

<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
