---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');htmlName<-'MilitaryExpenditureGDP';rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-',htmlName,'.html')) })

title : 'Military expenditure by country as percentage of gross domestic product'
author: 'アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp'
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 4
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 1000px;}</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000)
```

```{r warning = F, error = F, message = F, echo = F}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r warning=F,error=F,message=F,echo=F}
library(knitr)
script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/importMilitaryExpenditureGDP.r",
    ssl.verifypeer = F
  )
eval(parse(text = script))
```

```{r warning=F,error=F,message=F,results='hold',echo=F}
dateFormat <- '%Y年'
fun_latestResult(obj = MilitaryExpenditureByCountryAsPercentageOfGrossDomesticProduct,
                 objColumn = grep('usa|japan|china',
                                  colnames(MilitaryExpenditureByCountryAsPercentageOfGrossDomesticProduct),
                                  ignore.case = T)
                 ,dateFormat = dateFormat)
dataTitle <- 
  paste0("国別軍事費対GDP比(%):",latestResult)
dataSource <- 
  "Stockholm International Peace Research Institute"
windowsFonts(Meiryo = windowsFont("Meiryo"))
options(scipen = 999)
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- Source https://www.sipri.org/databases/milex
- -9999:data unavailable

***

#### USA / アメリカ

```{r warning=F, error=F, message=F, echo=F,results='asis'}
obj <- 
  MilitaryExpenditureByCountryAsPercentageOfGrossDomesticProduct
titleTxt <- 
  'Military expenditure by country as percentage of gross domestic product'
objColumn <- 
  c(1,grep('usa',colnames(obj),ignore.case = T))
obj <- na.omit(obj[,objColumn])
n <- 1
fun_generateKnit(objDF = obj,
                 plotNum = n,
                 group = 0,
                 quantiles = 2,
                 barPlot = 1,
                 dygraphTitle = paste0(titleTxt,':',colnames(obj)[2]))
eval(parse(text = paste0('dygraphPlot', n)))
cat('<hr>')
summaryDF <- cbind(summary(obj[,2]))
colnames(summaryDF)[1] <- paste0(titleTxt,':',colnames(obj)[2])
cat(paste0('<b>',paste0(format(range(obj[,1]),dateFormat),collapse = '~'),'</b>\n\n'))
fun_markdownTable(obj = summaryDF,rownames = T)
cat('<hr>')
```

#### Japan / 日本

```{r warning=F, error=F, message=F, echo=F,results='asis'}
obj <- 
  MilitaryExpenditureByCountryAsPercentageOfGrossDomesticProduct
objColumn <- 
  c(1,grep('japan',colnames(obj),ignore.case = T))
obj <- na.omit(obj[,objColumn])
n <- 1
fun_generateKnit(objDF = obj,
                 plotNum = n,
                 group = 0,
                 quantiles = 2,
                 barPlot = 1,
                 dygraphTitle = paste0(titleTxt,':',colnames(obj)[2]))
eval(parse(text = paste0('dygraphPlot', n)))
cat('<hr>')
summaryDF <- cbind(summary(obj[,2]))
colnames(summaryDF)[1] <- paste0(titleTxt,':',colnames(obj)[2])
cat(paste0('<b>',paste0(format(range(obj[,1]),dateFormat),collapse = '~'),'</b>\n\n'))
fun_markdownTable(obj = summaryDF,rownames = T)
cat('<hr>')
```

#### China, P.R. / 中国

```{r warning=F, error=F, message=F, echo=F,results='asis'}
obj <- 
  MilitaryExpenditureByCountryAsPercentageOfGrossDomesticProduct
objColumn <- 
  c(1,grep('china',colnames(obj),ignore.case = T))
obj <- na.omit(obj[,objColumn])
n <- 1
fun_generateKnit(objDF = obj,
                 plotNum = n,
                 group = 0,
                 quantiles = 2,
                 barPlot = 1,
                 dygraphTitle = paste0(titleTxt,':',colnames(obj)[2]))
eval(parse(text = paste0('dygraphPlot', n)))
cat('<hr>')
summaryDF <- cbind(summary(obj[,2]))
colnames(summaryDF)[1] <- paste0(titleTxt,':',colnames(obj)[2])
cat(paste0('<b>',paste0(format(range(obj[,1]),dateFormat),collapse = '~'),'</b>\n\n'))
fun_markdownTable(obj = summaryDF,rownames = T)
cat('<hr>')
```

#### 韓国

```{r warning=F, error=F, message=F, echo=F,results='asis'}
obj <- 
  MilitaryExpenditureByCountryAsPercentageOfGrossDomesticProduct
objColumn <- 
  c(1,grep('Korea, South',colnames(obj),ignore.case = T))
obj <- na.omit(obj[,objColumn])
n <- 1
fun_generateKnit(objDF = obj,
                 plotNum = n,
                 group = 0,
                 quantiles = 2,
                 barPlot = 1,
                 dygraphTitle = paste0(titleTxt,':',colnames(obj)[2]))
eval(parse(text = paste0('dygraphPlot', n)))
cat('<hr>')
summaryDF <- cbind(summary(obj[,2]))
colnames(summaryDF)[1] <- paste0(titleTxt,':',colnames(obj)[2])
cat(paste0('<b>',paste0(format(range(obj[,1]),dateFormat),collapse = '~'),'</b>\n\n'))
fun_markdownTable(obj = summaryDF,rownames = T)
cat('<hr>')
```

#### ドイツ

```{r warning=F, error=F, message=F, echo=F,results='asis'}
obj <- 
  MilitaryExpenditureByCountryAsPercentageOfGrossDomesticProduct
objColumn <- 
  c(1,grep('Germany',colnames(obj),ignore.case = T))
obj <- na.omit(obj[,objColumn])
n <- 1
fun_generateKnit(objDF = obj,
                 plotNum = n,
                 group = 0,
                 quantiles = 2,
                 barPlot = 1,
                 dygraphTitle = paste0(titleTxt,':',colnames(obj)[2]))
eval(parse(text = paste0('dygraphPlot', n)))
cat('<hr>')
summaryDF <- cbind(summary(obj[,2]))
colnames(summaryDF)[1] <- paste0(titleTxt,':',colnames(obj)[2])
cat(paste0('<b>',paste0(format(range(obj[,1]),dateFormat),collapse = '~'),'</b>\n\n'))
fun_markdownTable(obj = summaryDF,rownames = T)
cat('<hr>')
```

#### Military expenditure by country as percentage of gross domestic product:Top 10 

```{r warning=F,error=F,message=F,echo=F,results='asis'}
library(rAmCharts);library(pipeR)
obj0 <- 
  MilitaryExpenditureByCountryAsPercentageOfGrossDomesticProduct
fun_transposeDataFrame(obj = obj0,tailN = 1,dateFormat = dateFormat,colName = 'Country/Region')
obj1 <- 
  tDF[-which(is.na(tDF[,2]) | tDF[,2] == -9999),]
colnames(obj1)[2] <- 
  paste0(colnames(obj1)[2],':',titleTxt)
obj2 <-
  obj1[order(obj1[,2],decreasing = T),]
obj3 <- head(obj2,10)
amBarplot(
  x = colnames(obj3)[1],
  y = colnames(obj3)[2],
  data = obj3,
  horiz = T,
  stack_type = 'regular',
  main = titleTxt,
  mainColor = "#68838B",
  mainSize = 15,
  creditsPosition = "top-right",
  legendPosition = "bottom",
  show_values = T) %>>% amOptions(legend = T, 
                                  legendPosition = "right", 
                                  labelRotation = 0, 
                                  zoom = F)
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
obj4 <- 
  obj2[grep('japan|usa|\\buk\\b|france|canada|germany|italy',obj2[,1],ignore.case = T),]
fun_outputMD(tags = 'SIPRI,国別軍事費対GDP比(%)',
             objDF = obj4,
             htmlName = htmlName,
             tableTitle = paste0(titleTxt,':国別軍事費対GDP比(%):G7各国'),
             tableName = '国別軍事費対GDP比(%):G7各国')
```

***
<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
