---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-CentralLimitTheorem.html')) })
title : "Central Limit Theorem"
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 4
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet"> 
<style>
.main-container {max-width : 1000px; margin-left : auto; margin-right : auto;}
table{white-space : nowrap;}
td.negative {color : red;}
table.amcc tr:nth-child(odd) {background-color: #F5F5F5;}
table.amcc tr:nth-child(even){background-color: #FFFFFF;}
</style>

<script>
<!-- # Reference http://www.hanselman.com/blog/MakingNegativeNumbersTurnRedUsingCSSAndJavascript.aspx -->
function MakeNegative() {
  TDs = document.getElementsByTagName('td');
  for (var i=0; i<TDs.length; i++) {
    var temp = TDs[i];
    if (temp.firstChild.nodeValue.indexOf('-') == 0) temp.className = "negative";
  }
}
</script>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan

本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000)
```

```{r warning=F, error=F, message=F, echo=F}
sampleSize <- c(10,30,100,1000)
repeatCount <- c(10,30,100,1000)
windowsFonts(Meiryo=windowsFont("Meiryo"))
options(scipen = 999)
```

```{r,warning=F,error=F,message=F,results='hold',echo=F}
dataTitle <- paste0('中心極限定理')
Author <- 'アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp'
cat(paste('Title       : ',dataTitle,'\n'))
cat(paste('Author      : ',Author,'\n'))
```
- Normality Test:shapiro.test {stats}. Null hypothesis:"The sample data come from a normal distribution." 

***
### 一様分布

```{r warning=F, error=F, message=F, echo=F, results='asis'}
resultTable <- data.frame()
for(sss in 1:length(sampleSize)) {
  for (rrr in 1:length(repeatCount)) {
    means <- sapply(seq(repeatCount[rrr]), function(x) {distribution <<- runif(sampleSize[sss]);mean(distribution)})
    title <- paste("サンプルサイズ = ", sampleSize[sss],"\n試行回数 = ", repeatCount[rrr])
    par(mfrow=c(1,3),family='Meiryo')
    plot(distribution,main = paste0('サンプルサイズ = ',sampleSize[sss],'\n試行',repeatCount[rrr],'回目'))
    panel.first = grid(nx = NULL, ny = NULL, lty = 2, equilogs = T)
    hist(means, main = title, breaks = 20, col = 'powderblue')
    qqnorm(means, main = title)
    qqline(means, col = "red", lwd = 2)
    panel.first = grid(nx = NULL, ny = NULL, lty = 2, equilogs = T)
    cat('<hr>')
    resultTable[sss, rrr] <- shapiro.test(means)$p.value
  }
}
resultTable <- data.frame(as.integer(sampleSize),resultTable)
colnames(resultTable) <- c("サンプルサイズ", paste0("試行回数:", repeatCount))
cat('shapiro.test p-value\n')
knitr::kable(resultTable, row.names=F)
```

***
### ベータ分布

```{r warning=F, error=F, message=F, echo=F, results='asis'}
alpha <- 0.5;beta <- 0.5
resultTable <- data.frame()
for(sss in 1:length(sampleSize)) {
  for (rrr in 1:length(repeatCount)) {
    means <- sapply(seq(repeatCount[rrr]), function(x) {distribution <<- rbeta(sampleSize[sss],alpha,beta);mean(distribution)})
    title <- paste("サンプルサイズ = ", sampleSize[sss],"\n試行回数 = ", repeatCount[rrr])
    par(mfrow=c(1,3),family='Meiryo')
    plot(distribution,main = paste0('サンプルサイズ = ',sampleSize[sss],'\n試行',repeatCount[rrr],'回目'))
    panel.first = grid(nx = NULL, ny = NULL, lty = 2, equilogs = T)
    hist(means, main = title, breaks = 20, col = 'powderblue')
    qqnorm(means, main = title)
    qqline(means, col = "red", lwd = 2)
    panel.first = grid(nx = NULL, ny = NULL, lty = 2, equilogs = T)
    cat('<hr>')
    resultTable[sss, rrr] <- shapiro.test(means)$p.value
  }
}
resultTable <- data.frame(as.integer(sampleSize),resultTable)
colnames(resultTable) <- c("サンプルサイズ", paste0("試行回数:", repeatCount))
cat('shapiro.test p-value\n')
knitr::kable(resultTable, row.names=F)
```

***
### ガンマ分布

```{r warning=F, error=F, message=F, echo=F, results='asis'}
shape <- 5;rate <- 0.1
resultTable <- data.frame()
for(sss in 1:length(sampleSize)) {
  for (rrr in 1:length(repeatCount)) {
    means <- sapply(seq(repeatCount[rrr]), function(x) {distribution <<- rgamma(sampleSize[sss], shape, rate);mean(distribution)})
    title <- paste("サンプルサイズ = ", sampleSize[sss],"\n試行回数 = ", repeatCount[rrr])
    par(mfrow=c(1,3),family='Meiryo')
    plot(distribution,main = paste0('サンプルサイズ = ',sampleSize[sss],'\n試行',repeatCount[rrr],'回目'))
    panel.first = grid(nx = NULL, ny = NULL, lty = 2, equilogs = T)
    hist(means, main = title, breaks = 20, col = 'powderblue')
    qqnorm(means, main = title)
    qqline(means, col = "red", lwd = 2)
    panel.first = grid(nx = NULL, ny = NULL, lty = 2, equilogs = T)
    cat('<hr>')
    resultTable[sss, rrr] <- shapiro.test(means)$p.value
  }
}
resultTable <- data.frame(as.integer(sampleSize),resultTable)
colnames(resultTable) <- c("サンプルサイズ", paste0("試行回数:", repeatCount))
cat('shapiro.test p-value\n')
knitr::kable(resultTable, row.names=F)
```

***
### コーシー分布

```{r warning=F, error=F, message=F, echo=F, results='asis'}
x0 <- 0;gamma <- 0.5
resultTable <- data.frame()
for(sss in 1:length(sampleSize)) {
  for (rrr in 1:length(repeatCount)) {
    means <- sapply(seq(repeatCount[rrr]), function(x) {distribution <<- rcauchy(sampleSize[sss],x0,gamma);mean(distribution)})
    title <- paste("サンプルサイズ = ", sampleSize[sss],"\n試行回数 = ", repeatCount[rrr])
    par(mfrow=c(1,3),family='Meiryo')
    plot(distribution,main = paste0('サンプルサイズ = ',sampleSize[sss],'\n試行',repeatCount[rrr],'回目'))
    panel.first = grid(nx = NULL, ny = NULL, lty = 2, equilogs = T)
    hist(means, main = title, breaks = 20, col = 'powderblue')
    qqnorm(means, main = title)
    qqline(means, col = "red", lwd = 2)
    panel.first = grid(nx = NULL, ny = NULL, lty = 2, equilogs = T)
    cat('<hr>')
    resultTable[sss, rrr] <- shapiro.test(means)$p.value
  }
}
resultTable <- data.frame(as.integer(sampleSize),resultTable)
colnames(resultTable) <- c("サンプルサイズ", paste0("試行回数:", repeatCount))
cat('shapiro.test p-value\n')
knitr::kable(resultTable, row.names=F)
```

***

<script>MakeNegative()</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
