---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-MonthlyStatementOfThePublicDebtOfTheUnitedStates.html')) })

title : 'Monthly Statement Of The Public Debt Of The United States'
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 5
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<style>
.main-container {max-width : 1000px; margin-left : auto; margin-right : auto;}
table{white-space : nowrap;}
td.negative {color : red;}
</style>

<script>
<!-- # Reference http://www.hanselman.com/blog/MakingNegativeNumbersTurnRedUsingCSSAndJavascript.aspx -->
function MakeNegative() {
  TDs = document.getElementsByTagName('td');
  for (var i=0; i<TDs.length; i++) {
    var temp = TDs[i];
    if (temp.firstChild.nodeValue.indexOf('-') == 0) temp.className = "negative";
  }
}
</script>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan

本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000)
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
library(RCurl);library(knitr)
script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/importMonthlyStatementOfThePublicDebtOfTheUnitedStates.r",
    ssl.verifypeer = F
  )
eval(parse(text = script))

script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/timeSeriesForecast.r",
    ssl.verifypeer = F
  )
eval(parse(text = script))

script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/plotTimeSeries.r",
    ssl.verifypeer = F
  )
eval(parse(text = script))

script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/R-dygraphsFunction.r",
    ssl.verifypeer = F
  )
eval(parse(text = script))

script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/transposeDataFrame.r",
    ssl.verifypeer = F
  )
eval(parse(text = script))

script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/timeSeriesDataFundamentalStatistics.r",
    ssl.verifypeer = F
  )
eval(parse(text = script))

script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/Rscript/master/importMajorForeignHoldersUSTreasury.r",
    ssl.verifypeer = F
  )
eval(parse(text = script))

windowsFonts(Meiryo=windowsFont("Meiryo"))
options(scipen=100)
dateFormat <- '%Y-%m'
```

```{r warning=F,error=F,message=F,echo=F,results='hold'}
fun_MSPD(startYear = 2005, breakYear = 2016, breakMonth = 12)
```

```{r warning=F,error=F,message=F,echo=F,results='hold'}
dataTitle <- 
  paste0('THE PUBLIC DEBT OF THE UNITED STATES / 米国の公的債務 - ', 
         paste0(format(range(MSPD[, 1]), '%Y年%m月'),collapse='~'))
dataSource <- 'U.S. Department of the Treasury'
notes <- '複数のワードで検索する際は半角スペースで区切ってください'
notes0 <- '表中、-9999はNAを意味します'
Author <- 'アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp'
cat(paste('Title       : ', dataTitle, '\n'))
cat(paste('Data Source : ', dataSource, '\n'))
cat(paste('Author      : ', Author, '\n'))
cat(paste('特  記      : ', notes, '\n'))
cat(paste('特  記      : ', notes0, '\n'))
```

#### Time Series

```{r warning=F,error=F,message=F,echo=F,results='hide'}
tmpDF <- MSPD
tmpDF[,-1] <- tmpDF[,-1] * 10^-6 
fun_dygraph(obj = tmpDF,colors = 'blue',plotNum = 1,group = 0,legendWidth = 300,
            mainTitle = 'THE PUBLIC DEBT OF THE UNITED STATES(Trillion $) / 米国の公的債務(兆ドル)')
dygraphPlot1
```

***

```{r warning=F,error=F,message=F,echo=F,results='hide'}
mergeData <- merge(MSPD, allData[,grep('date|grand|japan|china',colnames(allData),ignore.case = T)],by='Date')
mergeData$`U.S. citizens and American entities` <-
  round((mergeData[,2]-mergeData[,5])/mergeData[,2]*100,1)
```

***
<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
