---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');htmlName<-'ConsumptionActivityIndex';rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[4,1],'am-consulting.co.jp-',htmlName,'.html')) })

title : 'Consumption Activity Index'
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 4
    fig_width: 9
    keep_md: no
    md_extensions: -ascii_identifiers 
    includes:
       in_header: insertHeader.html
    self_contained: false
---

```{r setup, include=FALSE}
tag <-
  read.csv(file = 'https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/components/insertHeader.csv',header = F,fileEncoding = 'UTF8')
tagTxt <- ''
for(rrr in 1:nrow(tag)){
  tagTxt <- paste0(tagTxt,tag[rrr,1],'\n')
}
insertFile <- file("insertHeader.html")
writeLines(text = tagTxt,con = insertFile)
close(insertFile)
```

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

<link rel="stylesheet" href="http://rawgit.com/am-consulting/am-consulting.github.io/master/components/jquery-responsive-tables/responsive-tables.css" type="text/css">

```{r set-options, echo=F, cache=F}
options(width = 1000)
```

```{r warning = F, error = F, message = F, echo = F}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r warning=F,error=F,message=F,echo=F}
importAMCC <- 
  c('importConsumptionActivityIndex.r')
script <- 
  getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                importAMCC[1]),
         ssl.verifypeer = F)
eval(parse(text = script))
```

```{r,warning=F,error=F,message=F,results='asis',echo=F}
dateFormat <- '%Y年%m月'
fun_latestResult(obj = ConsumptionActivityIndex,objColumn = 2,dateFormat = dateFormat)
dataTitle <- 
  paste0('消費活動指数:',
         latestResult)
dataSource <- 
  '日本銀行'
windowsFonts(Meiryo = windowsFont("Meiryo"))
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- http://www.boj.or.jp/research/research_data/cai/index.htm/
- 指数個別ウエイト http://knowledgevault.saecanet.com/charts/am-consulting.co.jp-IndexWeights.html

***

```{r warning=F,error=F,message=F,echo=F,results='asis'}
timeSeriesDF <- ConsumptionActivityIndex
texDygraph <- vector()
cnt <- 0
for(iii in 2:ncol(timeSeriesDF)){
  obj <- 
    na.omit(timeSeriesDF[,c(1,iii)])
  obj$FittedCurve <-
    predict(loess(obj[,2] ~ as.numeric(obj[,1]),degree = 2))
  cnt <- cnt + 1
  fun_generateKnit(objDF = obj, 
                   plotNum = cnt, 
                   group = 0, 
                   colors = c('blue','red','green'), 
                   dygraphTitle = colnames(obj)[2])
  assign(paste0('knit_expanded', cnt),
         paste0("\n```{r warning=F, error=F, message=F, echo=F, results='asis'}\n\n",
                "eval(parse(text = paste0('dygraphPlot", cnt," %>% ', primeMinisterOfJapan_dygraph)))",
                "\n\ncat('<hr>')\n\n```"),envir = .GlobalEnv)
  texDygraph <- 
    c(texDygraph, paste0('knit_expanded', cnt))
}
```

`r paste(knitr::knit(text = sapply(texDygraph,get)), collapse = '\n')`

#### レベル

```{r warning=F,error=F,message=F,echo=F,results='asis'}
obj <- fun_transposeDataFrame(obj = ConsumptionActivityIndex,dateFormat = dateFormat,tailN = 3)
cat(fun.html.table(obj = obj))
```

***

#### 前月比(%)

```{r warning=F,error=F,message=F,echo=F,results='asis'}
obj <- fun_transposeDataFrame(obj = fun_makeDiffRatioTable(obj = ConsumptionActivityIndex,lag = 1),
                              tailN = 3,dateFormat = dateFormat)
cat(fun.html.table(obj = obj))
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
username <- Sys.info()['user']
pathToFile <- paste0('C:/Users/', username,'/Desktop/pathToCSV/')
setwd(pathToFile)
fileName <- 'defaultPath.csv'
buf <-
  read.csv(file = fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,
           fileEncoding = 'utf-8',quote = "\"")
pathOutputTOchart <- paste0("C:/Users/", username, buf[4,1])
setwd(pathOutputTOchart)
#---------------------------------------------------
library(ggplot2)
obj <- na.omit(ConsumptionActivityIndex[,c(1,2,3)])
for(ccc in 2:ncol(obj)){
  tmp <- obj[,c(1,ccc)]
  tmp$name <- colnames(tmp)[2]
  colnames(tmp)[2] <- 'value'
  if(ccc == 2){data.set <- tmp}else{data.set <- rbind(data.set,tmp)}
}
caption.subtitle.size <- 14
plot.text.size <- 13
base.size <- 11
date.range <- paste0(format(range(data.set[,1]),dateFormat),collapse = '~')
g <- ggplot(data = data.set,aes(x = Date,y = value,col = name))
g <- g + geom_line() + geom_point(size = 1) + geom_smooth()
g <- g + theme_grey(base_size = base.size,base_family = 'Meiryo')
g <- g + ggtitle(label = paste0('消費活動指数\n',date.range,'\nSource:',dataSource))
g <- g + scale_y_continuous(name = '',breaks = scales::pretty_breaks(20),sec.axis = dup_axis())
g <- g + xlab(label = '')
g <- g + theme(plot.title = element_text(hjust = 0.5))
g <- g + theme(axis.text.x = element_text(size = plot.text.size,angle = 0))
g <- g + theme(axis.text.y = element_text(size = plot.text.size,angle = 0))
g <- g + theme(plot.subtitle = element_text(size = caption.subtitle.size,angle = 0))
g <- g + theme(plot.caption = element_text(size = caption.subtitle.size,angle = 0))
g <- g + theme(legend.position = 'top')
g <- g + theme(legend.text = element_text(size = plot.text.size,angle = 0))
pngFile <- paste0(htmlName, "1.png")
png(file = pngFile, width = 1000, height = 600)
print(g)
dev.off()
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
obj <- ConsumptionActivityIndex[,c(1,2)]
fun_outputMD(tags = '消費活動指数',
             objDF = fun_summaryByName(obj = obj,omitFirst = 1,dateFormat = dateFormat),
             htmlName = htmlName,
             image1 = 1,image2 = 0,
             title = dataTitle,
             tableTitle = colnames(obj)[2],
             buf.row = 4)
fun_updateURLcsv()
fun_updateURLcsv.olive()
```

<script src="http://rawgit.com/am-consulting/am-consulting.github.io/master/components/jquery-responsive-tables/jquery.responsive-tables.js"></script>
<script src="http://rawgit.com/am-consulting/am-consulting.github.io/master/components/jquery-responsive-tables/app.js"></script>

***
<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
