---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-JapaneseLaws.html')) })

title : "Japanese Laws"
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 4
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<style>.main-container {max-width : 1000px;}</style>
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan

本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000)
```

<script src="https://ajax.googleapis.com/ajax/libs/jquery/2.2.4/jquery.min.js"></script>
<link  href="https://cdn.datatables.net/1.10.12/css/jquery.dataTables.min.css" rel="stylesheet">
<script src="https://cdn.datatables.net/1.10.12/js/jquery.dataTables.min.js"></script>
<script src="https://bartaz.github.io/sandbox.js/jquery.highlight.js"></script>
<script src="https://cdn.datatables.net/plug-ins/1.10.12/features/searchHighlight/dataTables.searchHighlight.min.js"></script>
<link  href="https://cdn.datatables.net/plug-ins/1.10.12/features/searchHighlight/dataTables.searchHighlight.css" rel="stylesheet">
<script>
$(document).ready(function() {
  $('table').DataTable( {
    "order"          : [[ 0, "asc" ]],
    "lengthMenu"     : [[5, -1],[5, "All"]],
    "searching"      : true,
    "paging"         : true,
    "ordering"       : true,
    "info"           : true,
    "scrollX"        : true,
    "retrieve"       : true,
    "searchHighlight": true
  } );
} );
</script>




```{r warning=F,error=F,message=F,echo=F,results='hide'}
library(RCurl);library(knitr)
functionList <-
  read.csv(
    file = 'https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/functionList.csv',
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(
      paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", functionList[iii,1]),
      ssl.verifypeer = F
      )
  eval(parse(text = script))
}
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
# 括弧内の文字列のみ抽出
# http://stackoverflow.com/questions/24534782/how-do-skip-or-f-work-on-regex
# http://stackoverflow.com/questions/8613237/extract-info-inside-all-parenthesis-in-r
# http://stackoverflow.com/questions/36176442/highlight-search-result-in-datatables
url <- 
  "http://law.e-gov.go.jp/htmldata/S25/S25HO201.html"
htmlLines <- 
  readLines(url,skipNul = F,encoding = 'shift_jis')
# lawText <- ''
# for(iii in 1:length(htmlLines)){
#   lawText <- paste0(lawText,htmlLines[iii])
# }
lawText <- 
  Reduce(function(x, y) paste0(x, y), htmlLines)
pattern <- 
  '<DIV class=".*?">(\\s|\\S)*?</div>'
items <- 
  regmatches(lawText, 
             gregexpr(pattern = pattern,
                      text = lawText,
                      ignore.case = T))[[1]]
lawTable <- 
  data.frame()
# for(iii in 1:length(items)){
for(iii in 1:50){
  pattern <- 
    '<div(\\s|\\S)*?>|</div>|<a(\\s)*?name.*?>[\\s]*?</a>'
  buf0 <- 
    gsub(pattern,
         '',
         items[iii],
         ignore.case = T)
  buf1 <-
    gsub('<b>',
         '<br><b>',
         buf0,
         ignore.case = T)
  buf2 <-
    gsub('</b>',
         '</b><br>',
         buf1,
         ignore.case = T)
  pattern <-
    '<a(\\s)*?href.*?>'
  if(length(grep(pattern,buf2,ignore.case = T))!=0){
    buf2 <-
      enc2native(gsub('HREF=\"/','HREF=\"http://law.e-gov.go.jp/',buf2))
  }
  lawTable[iii,1] <-
    gsub('^<br>',
         '',
         buf2,
         ignore.case = T)
}
```

```{r warning=F,error=F,message=F,echo=F,results='asis'}
```

```{r warning=F,error=F,message=F,echo=F,results='asis'}
lawTable <- 
  data.frame(seq(nrow(lawTable)),
             lawTable,
             stringsAsFactors = F)
colnames(lawTable) <-
  c('No.', '条文')
knitr::kable(lawTable,
             escape = F,
             format = 'html',
             table.attr = "class = 'display compact' width = '100%'")
```

***
<script>MakeNegative()</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
