---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');htmlName<-'CountriesOfTheWorld';ISOcode<-'JPN';rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-',htmlName,'_',ISOcode,'.html')) })

title : "`r paste0('Countries Of The World:',ISOcode)`"
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 5
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 1000px;}</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r warning = F,error = F,message = F,echo = F,results = 'hide'}
fileName <- 
  'functionList.csv'
baseURL <- 
  'https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/'
functionList <- 
  read.csv(
    file = paste0(baseURL,'csv/',fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    RCurl::getURL(paste0(baseURL,functionList[iii,1]),ssl.verifypeer = F)
  eval(parse(text = script))
}
```

### Economic Data From World Economic Outlook Databases(IMF)
- Source http://www.imf.org/external/ns/cs.aspx?id=28

```{r warning = F,error = F,message = F,echo = F,results = 'asis'}
aspxFile <-
  'https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/WorldEconomicOutlook/201704/weoreptc.aspx'
tmp0 <-
  read.table(file = aspxFile,header = T,sep = '\t',stringsAsFactor = F,
             na.strings = c('','n/a'),
             check.names = F,fill = T,quote = "\"")
buf0 <- tmp0
objColumn0 <- 
  grep('^country$',colnames(buf0),ignore.case = T)
buf0[grep('stp',buf0$ISO,ignore.case = T),objColumn0] <- "São Tomé and Príncipe"
buf0[grep('civ',buf0$ISO,ignore.case = T),objColumn0] <- "Côte d'Ivoire"
objColumnYear <-
  grep('^[0-9]{4}$',colnames(buf0))
yearRange <-
  paste0(range(colnames(buf0)[objColumnYear]),collapse = '~')
buf0[,objColumnYear] <- 
  apply(buf0[,objColumnYear],2,function(x)as.numeric(gsub(',','',x)))
buf0 <- buf0[!is.na(buf0$ISO),]
WEO <- buf0
```

```{r warning = F,error = F,message = F,echo = F,results = 'hide'}
ISO <- unique(WEO$ISO)
WEO$`DesAndUnit` <- paste0(WEO$`Subject Descriptor`,'.Unit:',WEO$Units)
SubjectList <- unique(WEO$DesAndUnit)
isoN <- grep(ISOcode,unique(WEO$ISO),ignore.case = T)
forcastYear <- c(2018,2022)
```

```{r warning = F,error = F,message = F,echo = F,results = 'asis'}
fun_extractWEO <- function(objCountry,Subject){
  buf0 <- WEO[WEO$ISO==objCountry,]
  buf1 <-
    subset(buf0,buf0$DesAndUnit==Subject)
  if(nrow(buf1)!=0){
    objColYear <-
      grep('^[0-9]{4}$',colnames(buf1))
    buf2 <- t(buf1[,objColYear])
    buf3 <-
      data.frame(Date=as.Date(paste0(row.names(buf2),'-1-1')),
                 buf2[,1],stringsAsFactors = F,row.names = NULL)
    colnames(buf3)[2] <-
      buf1$`Subject Descriptor`
    buf4 <-
      buf3[forcastYear[1]<=year(buf3[,1]) & year(buf3[,1])<=forcastYear[2],]
    returnList <-
          list('tsUnit' = buf1$Units,
               'tsData' = na.omit(buf4),
               'tsNote' = buf1$`Subject Notes`,
               'tsScale' = buf1$Scale,
               'tsCountry' = buf1$Country)
    return(returnList)
  }else{
    returnList <- NA
    return(returnList)
  }
}
```

```{r warning = F,error = F,message = F,echo = F,results = 'asis'}
cnt <- 1
for(iii in seq(length(SubjectList))){
  returnOBJ <- fun_extractWEO(objCountry = ISO[isoN],Subject = SubjectList[iii])
  if(!is.na(returnOBJ)){
    obj <- returnOBJ$tsData
    if(nrow(obj)==(diff(forcastYear)+1)){
      buf <-
        fun_transposeDataFrame(obj = obj,dateFormat = '%Y',
                               colName = paste0(returnOBJ$tsCountry,':Subject'))
      buf$Unit <- returnOBJ$tsUnit
      buf$Scale <- returnOBJ$tsScale
      if(cnt==1){IMFData <- buf}else{IMFData <- rbind(IMFData,buf)}
      cnt <- cnt + 1
    }
  }
}
IMFData[is.na(IMFData)] <- ''
fun_markdownTable(obj = IMFData)
```

### Economic Data From OECD
- Source https://stats.oecd.org/

```{r warning = F,error = F,message = F,echo = F,results = 'hide'}
userName <-
  Sys.info()['user']
pathToFile <-
  paste0('C:/Users/',userName,'/Desktop/pathToCSV/')
setwd(pathToFile)
fileName <-
  'defaultPath.csv'
buf <-
  read.csv(file = fileName,
           header = F,
           skip = 0,
           stringsAsFactor = F,
           check.names = F,
           fileEncoding = 'utf-8',quote = "\"")
pathOutputTOcsv <-
  paste0("C:/Users/",userName,buf[2,1],'csv/OECDFactbook/2015-2016/')
setwd(pathOutputTOcsv)
getwd()
csvFile <- dir()
tmp0 <-
  read.csv(file = csvFile,header = T,check.names = F,stringsAsFactors = F)
buf0 <- tmp0
colnames(buf0) <- iconv(colnames(buf0),from = 'utf8',to = 'utf8')
OECD <- buf0
```

```{r warning = F,error = F,message = F,echo = F,results = 'asis'}
ISO <- unique(OECD$LOCATION)
OECD$`DesAndUnit` <- paste0(OECD$Subject,'.Unit:',OECD$Unit)
SubjectList <- unique(OECD$DesAndUnit)
isoN <- grep(ISOcode,unique(OECD$Country),ignore.case = T)
```

```{r warning = F,error = F,message = F,echo = F,results = 'asis'}
fun_extractOECD <- function(objCountry,Subject){
  buf0 <- OECD[OECD$LOCATION==objCountry,]
  buf1 <-
    buf0[buf0$DesAndUnit==Subject,]
  if(nrow(buf1)!=0){
    buf2 <-
      data.frame(Date=as.Date(paste0(buf1$Year,'-1-1')),buf1$Value,stringsAsFactors = F)
    colnames(buf2)[2] <- unique(buf1$Subject)
    buf2$col <- 'blue'
    buf2$cex <- 1.1
    returnList <-
          list('tsUnit' = unique(buf1$Unit),
               'tsData' = na.omit(buf2),
               'tsCountry' = unique(buf1$Country))
    return(returnList)
  }else{
    returnList <- NA
    return(returnList)
  }
}
```

```{r warning = F,error = F,message = F,echo = F,results = 'asis'}
cnt <- 1
for(iii in seq(length(SubjectList))){
  returnOBJ <- fun_extractOECD(objCountry = ISO[isoN],Subject = SubjectList[iii])
  if(!is.na(returnOBJ)){
    if(10<=nrow(returnOBJ$tsData)){
      cat(paste0('\n- ',cnt,'. ',colnames(returnOBJ$tsData)[2],'\n'))
      fun_plot(obj = returnOBJ$tsData,
               Unit = returnOBJ$tsUnit,
               Country = returnOBJ$tsCountry)
      cat('\n\n<hr>\n\n')
      cnt <- cnt + 1
    }
  }
}
```

### CIA Factbook
- Source https://www.cia.gov/index.html

```{r warning = F,error = F,message = F,echo = F,results = 'asis'}
script <-
  RCurl::getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/importCIA-the-world-factbook.r",
    ssl.verifypeer = F)
eval(parse(text = script))
```

```{r warning = F,error = F,message = F,echo = F,results = 'asis'}
cia <- data.frame()
cnt <- 1
for(iii in seq(length(tableTitle))){
  obj <- get(paste0('comparisonTable',iii))
  objRaw <- grep(ISOcode,obj$Country,ignore.case = T)
  if(length(objRaw)!=0){
    cia[cnt,1] <- tableTitle[iii]
    cia[cnt,2] <- obj[objRaw,3]
    cia[cnt,3] <- obj[objRaw,4]
    cnt<-cnt+1
  }
}
colnames(cia) <- c('Subject','Value','Date')
fun_markdownTable(obj = cia)
```

