---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');htmlName<-'WorldEconomicOutlook';rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-',htmlName,'.html')) })

title : 'World Economic Outlook'
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
output: 
  html_document:
    fig_height: 10
    fig_width: 12
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 1600px;}</style>
<style>table:not(#amcc) {font-size: 80%;}</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000)
```

```{r warning = F, error = F, message = F, echo = F}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

<!--

Download WEO Data
By Countries(country-level data)
1.Select Country Group → All countries
2.Select Countries → Select All
3.Select Subjects → Select All
4.Select Date Range → ISO Alpha-3 Code
weoreptc.aspxをテキストエディタで開きANSIに変換後すべて選択からコピーでread.table()。

-->

```{r warning=F, error=F, message=F, echo=F, results='hide'}
library(sparkline)
library(DT)
library(lubridate)
library(knitr)
# Reference https://github.com/htmlwidgets/sparkline/issues/3
# http://www.imf.org/external/ns/cs.aspx?id=28
tmp0 <-
  read.table(file = 'clipboard',
             header = T,
             sep = '\t',
             stringsAsFactor = F,
             na.strings = c('','n/a'),
             check.names = F,
             fill = T,
             quote = "\"")
buf0 <- tmp0
objColumn0 <- 
  grep('^country$',colnames(buf0),ignore.case = T)
buf0[grep('stp',buf0[,1],ignore.case = T),objColumn0] <- "São Tomé and Príncipe"
buf0[grep('civ',buf0[,1],ignore.case = T),objColumn0] <- "Côte d'Ivoire"
objColumnYear <-
  grep('^[0-9]{4}$',colnames(buf0))
yearRange <-
  paste0(range(colnames(buf0)[objColumnYear]),collapse = '~')
buf0[,objColumnYear] <- 
  apply(buf0[,objColumnYear],2,function(x)as.numeric(gsub(',','',x)))
```

```{r,warning=F,error=F,message=F,results='hold',echo=F}
dataTitle <- 
  paste0('世界経済の見通し / 『World Economic Outlook Database』(International Monetary Fund):',yearRange)
subTitle <- 
  'World Economic Outlook Database April 2017'
dataSource <- 
  'International Monetary Fund'
windowsFonts(Meiryo = windowsFont("Meiryo"))
options(scipen = 999)
```

***

- `r paste0("タイトル : ",dataTitle,':',subTitle)`
- `r paste0("データ出所 : ",dataSource)`
- Source http://www.imf.org/external/ns/cs.aspx?id=28
- at current prices : 名目
- at constant prices : 実質

***

#### `r countryName <- 'Japan';countryName` / 日本

```{r warning=F, error=F, message=F, echo=F, results='asis'}
buf1 <-
  buf0[grep(paste0('^',countryName,'$'),buf0[,objColumn0],ignore.case = T),]
objColumn <-
  c(2,6,15)
buf2 <-
  buf1[,-objColumn]
fun_dataTable(obj = buf2,orderDirection = 'asc',dateFormat = 0,needID = 1,menuLength = 25)
```

***

#### `r countryName <- 'United States';countryName` / アメリカ合衆国

```{r warning=F, error=F, message=F, echo=F, results='asis'}
buf1 <-
  buf0[grep(paste0('^',countryName,'$'),buf0[,objColumn0],ignore.case = T),]
objColumn <-
  c(2,6,15)
buf2 <-
  buf1[,-objColumn]
fun_dataTable(obj = buf2,orderDirection = 'asc',dateFormat = 0,needID = 1,menuLength = 25)
```

***

#### `r countryName <- 'China';countryName` / 中国

```{r warning=F, error=F, message=F, echo=F, results='asis'}
buf1 <-
  buf0[grep(paste0('^',countryName,'$'),buf0[,objColumn0],ignore.case = T),]
objColumn <-
  c(2,6,15)
buf2 <-
  buf1[,-objColumn]
fun_dataTable(obj = buf2,orderDirection = 'asc',dateFormat = 0,needID = 1,menuLength = 25)
```

***

#### `r countryName <- 'Germany';countryName` / ドイツ

```{r warning=F, error=F, message=F, echo=F, results='asis'}
buf1 <-
  buf0[grep(paste0('^',countryName,'$'),buf0[,objColumn0],ignore.case = T),]
objColumn <-
  c(2,6,15)
buf2 <-
  buf1[,-objColumn]
fun_dataTable(obj = buf2,orderDirection = 'asc',dateFormat = 0,needID = 1,menuLength = 25)
```

***

#### `r countryName <- 'India';countryName` / インド

```{r warning=F, error=F, message=F, echo=F, results='asis'}
buf1 <-
  buf0[grep(paste0('^',countryName,'$'),buf0[,objColumn0],ignore.case = T),]
objColumn <-
  c(2,6,15)
buf2 <-
  buf1[,-objColumn]
fun_dataTable(obj = buf2,orderDirection = 'asc',dateFormat = 0,needID = 1,menuLength = 25)
```

***

#### `r countryName <- 'United Kingdom';countryName` / イギリス

```{r warning=F, error=F, message=F, echo=F, results='asis'}
buf1 <-
  buf0[grep(paste0('^',countryName,'$'),buf0[,objColumn0],ignore.case = T),]
objColumn <-
  c(2,6,15)
buf2 <-
  buf1[,-objColumn]
fun_dataTable(obj = buf2,orderDirection = 'asc',dateFormat = 0,needID = 1,menuLength = 25)
```

```{r warning=F, error=F, message=F, echo=F, results='hide'}
objColumn0 <- 
  grep('^Subject Descriptor$',colnames(buf0),ignore.case = T)
buf1 <-
  buf0[grep('Unemployment rate',buf0[,objColumn0],ignore.case = T),]
buf2 <-
  buf1[,c(2,(max(objColumnYear)-5):max(objColumnYear))]
buf3 <-
  buf2[!is.na(buf2[,ncol(buf2)]),]
buf4 <-
  buf3[order(buf3[,ncol(buf3)],decreasing = T),]
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fun_outputMD(tags = 'IMF,World Economic Outlook',
             objDF = buf4,
             htmlName = htmlName,
             tableTitle = 'Unemployment rate(Percent of total labor force) / 失業率(%)',
             tableName = '世界経済の見通し(2017年04月版) 2022年までの予測')
```

***
<script>MakeNegative()</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
