---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-dailyFinancialDataTrend.html')) })
title : "Historical Trend Analyses for Daily Financial Data"
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 5
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<style>.main-container {max-width : 1000px;}</style>
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000)
```

```{r warning = F, error = F, message = F, echo = F}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r warning=F, error=F, message=F, echo=F}
library(quantmod)
# USD/JPY
buf <-
  na.omit(getSymbols(Symbols = 'DEXJPUS',src = 'FRED',auto.assign = F))
USDJPY <-
  data.frame(Date = index(buf),buf,stringsAsFactors = F,check.names = F,row.names = NULL)
colnames(USDJPY)[2] <- 'USD/JPY'
# EUR/USD
buf <-
  na.omit(getSymbols(Symbols = 'DEXUSEU',src = 'FRED',auto.assign = F))
EURUSD <-
  data.frame(Date = index(buf),buf,stringsAsFactors = F,check.names = F,row.names = NULL)
colnames(EURUSD)[2] <- 'EUR/USD'
# GBP/USD
buf <-
  na.omit(getSymbols(Symbols = 'DEXUSUK',src = 'FRED',auto.assign = F))
GBPUSD <-
  data.frame(Date = index(buf),buf,stringsAsFactors = F,check.names = F,row.names = NULL)
colnames(GBPUSD)[2] <- 'GBP/USD'
```

```{r,warning=F,error=F,message=F,results='hold',echo=F}
dateFormat <- '%Y年%m月%d日'
fun_latestResult(USDJPY,dateFormat = dateFormat)
dataTitle <- 
  paste0('日次金融指標の月別トレンド:',latestResult)
dataSource <- 'Federal Reserve Bank of St. Louis'
windowsFonts(Meiryo=windowsFont("Meiryo"))
options(scipen = 999)
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`

***

#### Trend By Month

```{r warning=F, error=F, message=F, echo=F, results='asis', fig.height=10}
par(mfrow=c(4,3),oma=c(0,0,0,0))
fun_monthlyTSbyYear(obj0 = USDJPY,mainTitle = colnames(USDJPY)[2])
cat('<hr>')
par(mfrow=c(4,3),oma=c(0,0,0,0))
fun_monthlyTSbyYear(obj0 = EURUSD,mainTitle = colnames(EURUSD)[2])
cat('<hr>')
par(mfrow=c(4,3),oma=c(0,0,0,0))
fun_monthlyTSbyYear(obj0 = GBPUSD,mainTitle = colnames(GBPUSD)[2])
```

***
#### Time Series Chart

```{r warning=F, error=F, message=F, echo=F,results='asis',fig.height=4}
lineColor <- c('blue','red','green')
n <- 1
obj <- USDJPY
fun_fit(obj = obj)
fun_MovingAverage(obj = obj,n = 20*6)
mergeData <- 
  merge(fittedDF,MovingAverageDF[,-2],by = 'Date')
fun_generateKnit(objDF = mergeData[,-c(4,5,7)],
                 plotNum = n,
                 group = 0,
                 dygraphTitle = colnames(obj)[2],colors = lineColor)
eval(parse(text = paste0('dygraphPlot', n)))
cat('<hr>')
n <- 2
obj <- EURUSD
fun_fit(obj = obj)
fun_MovingAverage(obj = obj,n = 20*6)
mergeData <- 
  merge(fittedDF,MovingAverageDF[,-2],by = 'Date')
fun_generateKnit(objDF = mergeData[,-c(4,5,7)],
                 plotNum = n,
                 group = 0,
                 dygraphTitle = colnames(obj)[2],colors = lineColor)
eval(parse(text = paste0('dygraphPlot', n)))
cat('<hr>')
n <- 3
obj <- GBPUSD
fun_fit(obj = obj)
fun_MovingAverage(obj = obj,n = 20*6)
mergeData <- 
  merge(fittedDF,MovingAverageDF[,-2],by = 'Date')
fun_generateKnit(objDF = mergeData[,-c(4,5,7)],
                 plotNum = n,
                 group = 0,
                 dygraphTitle = colnames(obj)[2],colors = lineColor)
eval(parse(text = paste0('dygraphPlot', n)))
```

***
#### Simulation
- USD/JPY

```{r warning=F, error=F, message=F, echo=F, results='asis'}
fun_makeDiffRatioTable(obj = USDJPY,lag = 1,roundDigits = 5)
x <- diffRatioDF[,2]
startValue <- tail(USDJPY[,2],1)
fun_doSimulation(x = x,finalbreaksBy = 2.5,startValue = startValue,simulationNumber = 200)
```

***
- EUR/USD

```{r warning=F, error=F, message=F, echo=F, results='asis'}
fun_makeDiffRatioTable(obj = EURUSD,lag = 1,roundDigits = 5)
x <- diffRatioDF[,2]
startValue <- tail(EURUSD[,2],1)
fun_doSimulation(x = x,finalbreaksBy = 0.025,startValue = startValue,simulationNumber = 200)
```

***
- GBP/USD

```{r warning=F, error=F, message=F, echo=F, results='asis'}
fun_makeDiffRatioTable(obj = GBPUSD,lag = 1,roundDigits = 5)
x <- diffRatioDF[,2]
startValue <- tail(GBPUSD[,2],1)
fun_doSimulation(x = x,finalbreaksBy = 0.025,startValue = startValue,simulationNumber = 200)
```

***

<script>MakeNegative()</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
