---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-BusinessConditions.html')) })
title : "Business Conditions of Japan"
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 5
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<style>.main-container {max-width : 1000px;}</style>
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan

本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
# ―,ソ,噂,欺,圭,構,蚕,十,申,貼,能,表,暴,予,禄,兔
options(width = 1000)
```

```{r,warning=F,error=F,message=F,echo=F}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", functionList[iii,1]),
    ssl.verifypeer = F
  )
  eval(parse(text = script))
}
```

```{r warning=F,error=F,message=F,echo=F}
library(XML);library(XLConnect);library(lubridate);library(Nippon)
username <- Sys.info()['user']
pathOutput <- paste0("C:/Users/", username, "/Desktop/R_Data_Write/")
setwd(pathOutput)
url <- "http://www.esri.cao.go.jp/jp/stat/di/di.html"
htmlMarkup <- htmlParse(url)
links <- xpathSApply(htmlMarkup, "//a/@href")
files <- links[grep('.xls',links)]
urlToData <- paste0('http://www.esri.cao.go.jp/jp/stat/di/', files)
for(iii in 1:length(files)){
  download.file(urlToData[iii], files[iii], mode = 'wb')
  assign(paste0('CI',iii), readWorksheetFromFile(paste0(pathOutput, files[iii]), sheet = 1, check.names = F, header = F))
}
```

```{r warning=F,error=F,message=F,echo=F}
fun_reshapeData <- function(iii){
  buf0 <- get(paste0('CI',iii))
  keyWord <- 'ＣＩ指数'
  bufR1 <- which(apply(buf0,1,function(x){(length(grep(keyWord,x)))})!=0)
  tmp <- ''
  for(ccc in 1:ncol(buf0)){
    tmp0 <- buf0[bufR1,ccc]
    if(!is.na(tmp0)){tmp <- tmp0}
    buf0[bufR1,ccc] <- tmp  
  }
  keyWord <- '和暦'
  bufR2 <- which(apply(buf0,1,function(x){(length(grep(keyWord,x)))})!=0)
  keyWord <- '外れ'
  bufC3 <- which(apply(buf0,2,function(x){(length(grep(keyWord,x)))})!=0)
  bufR3 <- which(apply(buf0,1,function(x){(length(grep(keyWord,x)))})!=0)
  colnames(buf0) <- sapply(gsub(' ','',paste0(buf0[bufR1,],'-',buf0[bufR2,])),zen2han)
  add <- buf0[bufR3,bufC3]
  buf1 <- buf0[-c(1:(bufR2+1)),]
  keyWord <- '西暦'
  bufC1 <- grep(keyWord,colnames(buf1))
  keyWord <- '月'
  bufC2 <- grep(keyWord,colnames(buf1))
  buf1[,1] <- as.Date(paste0(buf1[,bufC1],'-',buf1[,bufC2],'-1'))
  buf2 <- buf1[,-c(bufC1,bufC2)]
  colnames(buf2)[1] <- 'Date'
  buf2[,-1] <- apply(buf2[,-1],2,as.numeric)
  colnames(buf2) <- gsub('\\.1',add,colnames(buf2))
  dataSet <<- buf2
}
```

```{r warning=F,error=F,message=F,echo=F,results='hold'}
fun_reshapeData(iii = 1)
dateFormat <- '%Y年%m月'
obj <- 
  dataSet[,1:4]
fun_makeDiffTable(obj = obj)
fun_latestResult(obj = diffDF,
                 objColumn = c(2:4),
                 dateFormat = dateFormat)
dataTitle <- paste0('景気動向指数:前月差:', latestResult)
dataSource <- '内閣府'
windowsFonts(Meiryo=windowsFont("Meiryo"))
options(scipen = 999)
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`

***

```{r warning=F, error=F, message=F, echo=F}
fun_plotTimeSeries <- function(obj,ccc = 2) {
  obj <- na.omit(obj[,c(1,ccc)])
  title <- paste0(colnames(obj)[2],' - ',paste0(format(range(obj[,1]),dateFormat),collapse = '~'))  
  par(family='Meiryo',mar=c(4,4,4,2))
  plot(obj[,1],obj[,2],type='l',col='blue',xlab='',ylab='',xaxt='n',
       cex.axis=1.2,cex.lab=1.2,cex.main=1.2,lwd=1,main = title)
  Date <- as.numeric(obj[,1])
  Value <- obj[,2]
  lo <- lm(Value ~ Date)
  lines(obj[,1] , predict(lo) , col = 'red', lwd = 1, lty = 2)
  panel.first = grid(nx = NULL, ny = NULL, lty = 2, equilogs = T)
  axis.Date(side=1, at=obj[,1],format=dateFormat,padj=1,cex.axis=1.0)
  # 民主党パート
  rectDateL <- as.numeric(as.Date('2009-09-16'))
  rectDateR <- as.numeric(as.Date('2012-12-26'))
  if(as.numeric(obj[1,1]) < rectDateR){
    rectText <- '民主党政権'
    rect(xleft  = rectDateL, ybottom = par('usr')[3], 
         xright = rectDateR, ytop    = par('usr')[4], 
         col    = 'dimgray', density = 10, angle = 45)
    text(rectDateL, par('usr')[4], labels = paste0('\n\n',rectText), pos = 4)
  }
  # 民主党パート
  # 3%パート
  rectDateL <- as.numeric(as.Date('1989-04-01'))
  rectDateR <- as.numeric(as.Date('1997-03-31'))
  if(as.numeric(obj[1,1]) < rectDateR){
    rectText <- '消費税\n3%'
    rect(xleft  = rectDateL, ybottom = par('usr')[3], 
         xright = rectDateR, ytop    = par('usr')[4], 
         col    = 'darksalmon', density = 10, angle = 135)
    text(rectDateL, par('usr')[3], labels = paste0(rectText,'\n\n\n'), pos = 4)
  }
  # 3%パート
  # 5%パート
  rectDateL <- as.numeric(as.Date('1997-04-01'))
  rectDateR <- as.numeric(as.Date('2014-03-31'))
  if(as.numeric(obj[1,1]) < rectDateR){
    rectText <- '消費税\n5%'
    rect(xleft  = rectDateL, ybottom = par('usr')[3], 
         xright = rectDateR, ytop    = par('usr')[4], 
         col    = 'yellowgreen', density = 10, angle = 135)
    text(rectDateL, par('usr')[3], labels = paste0(rectText,'\n\n\n'), pos = 4)
  }
  # 5%パート
  # 8%パート
  rectDateL <- as.numeric(as.Date('2014-04-01'))
  rectDateR <- tail(obj[,1],1)
  if(as.numeric(obj[1,1]) < rectDateR){
    rectText <- '消費税\n8%'
    rect(xleft  = rectDateL, ybottom = par('usr')[3], 
         xright = rectDateR, ytop    = par('usr')[4], 
         col    = 'skyblue', density = 10, angle = 135)
    text(rectDateL, par('usr')[3], labels = paste0(rectText,'\n\n\n'), pos = 4)
  }
  # 8%パート
  cat(title)
  print(summary(lo))
  print(confint(lo, 'Date', level=0.95))
  cat('\n\n\n\n\n')
}
```

```{r warning=F, error=F, message=F, echo=F}
fun_plotTimeSeries(obj = dataSet, ccc = 2)
fun_plotTimeSeries(obj = dataSet, ccc = 3)
fun_plotTimeSeries(obj = dataSet, ccc = 4)
```

```{r warning=F, error=F, message=F, echo=F}
n1 <- 1
obj <- na.omit(dataSet[,c(1,2)])
buf <- data.frame(tail(obj[,1],-1),diff(obj[,2]),check.names = F,stringsAsFactors = F)
colnames(buf) <- colnames(obj)
fun_generateKnit(objDF = buf, plotNum = n1, colors = 'green', 
                 barPlot = 1, dygraphTitle = paste0(colnames(buf)[2], '-前月差(ポイント)'))
eval(parse(text = paste0('dygraphPlot',n1,' %>% ', ConsumptionTax)))
```

***

```{r warning=F, error=F, message=F, echo=F}
n1 <- 2
obj <- na.omit(dataSet[,c(1,3)])
buf <- data.frame(tail(obj[,1],-1),diff(obj[,2]),check.names = F,stringsAsFactors = F)
colnames(buf) <- colnames(obj)
fun_generateKnit(objDF = buf, plotNum = n1, colors = 'green', 
                 barPlot = 1, dygraphTitle = paste0(colnames(buf)[2], '-前月差(ポイント)'))
eval(parse(text = paste0('dygraphPlot',n1,' %>% ', ConsumptionTax)))
```

***

```{r warning=F, error=F, message=F, echo=F}
n1 <- 3
obj <- na.omit(dataSet[,c(1,4)])
buf <- data.frame(tail(obj[,1],-1),diff(obj[,2]),check.names = F,stringsAsFactors = F)
colnames(buf) <- colnames(obj)
fun_generateKnit(objDF = buf, plotNum = n1, colors = 'green', 
                 barPlot = 1, dygraphTitle = paste0(colnames(buf)[2], '-前月差(ポイント)'))
eval(parse(text = paste0('dygraphPlot',n1,' %>% ', ConsumptionTax)))
```

```{r warning=F, error=F, message=F, echo=F, results='asis'}
cat('<hr>\n\n')
dataSet0 <- dataSet
fun_dataTable(obj = dataSet0,title = dataTitle,dateFormat = dateFormat)
```

***
#### 前月差

```{r warning=F, error=F, message=F, echo=F, results='asis'}
fun_makeDiffTable(obj = dataSet)
fun_markdownTable(obj = fun_transposeDataFrame(obj = diffDF, dateFormat = dateFormat, tailN = 5))
```

***
<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
