---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');htmlName<-'NaturalGasStorage';rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-',htmlName,'.html')) })

title : 'Natural Gas Storage'
author: 'アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp'
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 6
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 1000px;}</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000,scipen = 999)
```

```{r warning = F, error = F, message = F, echo = F}
fileName <- 
  'functionList.csv'
baseURL <- 
  'https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/'
functionList <- 
  read.csv(
    file = paste0(baseURL,'csv/',fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    RCurl::getURL(paste0(baseURL,functionList[iii,1]),ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
importData <- c('importNaturalGasStorage.r')
script <-
  RCurl::getURL(paste0(baseURL,importData[1]),ssl.verifypeer = FALSE)
eval(parse(text = script))
```

```{r warning=F,error=F,message=F,results='hold',echo=F}
dateFormat <- '%Y-%m-%d'
fun_latestResult(obj = NaturalGasStorage,objColumn = ncol(NaturalGasStorage),dateFormat = dateFormat)
dataTitle <- 
  paste0(sheetTitle,":",latestResult,' ',sheetUnit)
dataSource <- "U.S. Energy Information Administration(EIA)"
windowsFonts(Meiryo = windowsFont("Meiryo"))
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- Unit/単位:`r sheetUnit`
- Source http://ir.eia.gov/ngs/ngs.html

***

```{r warning=F, error=F, message=F, echo=F, results='asis'}
for(ccc in 2:ncol(NaturalGasStorage)){
  obj <- na.omit(NaturalGasStorage[,c(1,ccc)])
  fun_plotTimeSeries(obj = obj,chartType = 0,dateFormat = dateFormat,
                     dataTitle = paste0(sheetTitle,'\n',sheetUnit),mar = c(4,4,6,1),
                     dataSource = dataSource,needLefLab = 0,typeL = 'o',fitLcolor = 2)
  fun_markdownTable(obj = fun_transposeDataFrame(obj = obj,tailN = 7,colName = 'Subject'))
  fun_markdownTable(obj = apply(obj[,2,drop=F],2,summary),rownames = T)
  cat('\n<hr>\n')
}
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fun_preparePlot()
pngFile <- 
  paste0(htmlName, "1.png")
png(file = pngFile, width = 1000, height = 600)
obj <- 
  fun_makeDiffTable(obj = na.omit(NaturalGasStorage[,c(1,ncol(NaturalGasStorage))]),lag = 1)
colnames(obj)[2] <- paste0(colnames(obj)[2],':WeekOverWeek(billion cubic feet)')
obj$col <- ifelse(0<=obj[,2],'#4169e1','#dc143c')
obj <- tail(obj,40)
par(mar=c(7,4,6,1),family='Meiryo')
barplot(height = obj[,2],col = obj$col,names.arg = obj[,1],las=2,
        main = paste0(sheetTitle,'\n',colnames(obj)[2],'\nSource:EIA'))
dev.off()
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fun_outputMD(tags = 'International Organization of Motor Vehicle Manufacturers',
             objDF = fun_transposeDataFrame(obj = obj[,c(1,2)],colName = 'Subject'),
             htmlName = htmlName,
             image1 = 1,
             image2 = 0,
             title = dataTitle,
             tableTitle = colnames(obj)[2],
             tableName = sheetTitle)
fun_updateURLcsv()
```

<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
