---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');htmlName<-'Michigan';rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-',htmlName,'.html')) })

title : 'Surveys of Consumers By University of Michigan'
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 4
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 1000px;}</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000)
```

```{r warning = F, error = F, message = F, echo = F}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r,warning=F,error=F,message=F,echo=F}
script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/importMichiganData.r",
    ssl.verifypeer = F
  )
eval(parse(text = script))
```

```{r,warning=F,error=F,message=F,results='hold',echo=F}
dateFormat <- '%Y-%m'
fun_latestResult(IndexOfConsumerSentiment)
dataTitle <- 
  paste0('University of Michigan Consumer Sentiment Index/ミシガン大学消費者信頼感指数:',latestResult)
dataSource <- 'University of Michigan'
windowsFonts(Meiryo = windowsFont("Meiryo"))
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- Source http://www.sca.isr.umich.edu/

***

#### Index Of Consumer Sentiment
- Moving Average:`r monthS <- 6;monthS`months

```{r,warning=F,error=F,message=F,results='asis',echo=F}
lineColor <- c('blue','green','red')
mergeData <- 
  merge(x = fun_fit(obj = IndexOfConsumerSentiment),
        y = fun_MovingAverage(obj = IndexOfConsumerSentiment,n = monthS,dateFormat = dateFormat)[,-2],
        by = 'Date')
n <- 1
fun_generateKnit(objDF = mergeData[,c(1,2,3,6)],plotNum = n,group = 0,quantiles = 2,colors = lineColor)
eval(parse(text = paste0('dygraphPlot', n, ' %>% ', potus_dygraph)))
cat('<hr>')
fun_markdownTable(obj = fun_transposeDataFrame(obj = IndexOfConsumerSentiment,dateFormat = dateFormat,tailN = 8))
cat('<hr>')
dammy <- fun_acf(obj = IndexOfConsumerSentiment,lag.max = 12*10)
fun_timeSeriesDataFundamentalStatistics(obj = IndexOfConsumerSentiment)
fun_markdownTable(obj = statisticsTable,rownames = T)
cat('<hr>')
cat('<h5>Month Over Month(point)</h5>')
diffDF <- fun_makeDiffTable(obj = IndexOfConsumerSentiment,lag = 1)
fun_generateKnit(objDF = diffDF,plotNum = n,group = 0,quantiles = 2,barPlot = 1)
eval(parse(text = paste0('dygraphPlot', n, ' %>% ', potus_dygraph)))
cat('<hr>')
fun_markdownTable(obj = fun_transposeDataFrame(obj = diffDF,dateFormat = dateFormat,tailN = 8))
```

***
#### Components Of The Index Of Consumer Sentiment

```{r,warning=F,error=F,message=F,results='asis',echo=F}
n <- 2
fun_generateKnit(objDF = ComponentsOfTheIndexOfConsumerSentiment,plotNum = n,group = 0)
eval(parse(text = paste0('dygraphPlot', n, ' %>% ', potus_dygraph)))
cat('<hr>')
fun_markdownTable(obj = fun_transposeDataFrame(obj = ComponentsOfTheIndexOfConsumerSentiment,
                                               dateFormat = dateFormat,tailN = 8))
```

***
#### Expected Changes In InflationRates

```{r,warning=F,error=F,message=F,results='asis',echo=F}
n <- 3
obj0 <- na.omit(ExpectedChangesInInflationRates)
row.names(obj0) <- NULL
obj <- obj0[-c(1:tail(which(31<diff(obj0[,1])),1)),]
fun_generateKnit(objDF = obj,plotNum = n,group = 0)
eval(parse(text = paste0('dygraphPlot', n, ' %>% ', potus_dygraph)))
cat('<hr>')
fun_markdownTable(obj = fun_transposeDataFrame(obj = obj,
                                               dateFormat = dateFormat,tailN = 8))
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fun_PlotStrawAnd4charts(obj = IndexOfConsumerSentiment,varType = 2)
dev.off();dev.off()
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
buf <-
  merge(IndexOfConsumerSentiment,ComponentsOfTheIndexOfConsumerSentiment,by='Date',all=T)
obj <-
  merge(buf,ExpectedChangesInInflationRates,by='Date',all=T)
fun_outputMD(tags = 'State,Employment,Unemployment',
             objDF = fun_transposeDataFrame(obj = obj,dateFormat = dateFormat),
             htmlName = htmlName,
             image1 = 1,image2 = 1,
             title = dataTitle,
             tableTitle = 'Latest 5 months',
             tableName = 'University of Michigan Consumer Sentiment Index')
fun_updateURLcsv()
```

***
<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
