---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-GDPGapInJapan.html')) })

title : 'GDP Gap In Japan'
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 4
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 1000px;}</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000)
```

```{r warning = F, error = F, message = F, echo = F}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r warning=F, error=F, message=F, echo=F}
fileName <- '1632gap.xls'
```

```{r warning=F, error=F, message=F, echo=F}
library(XLConnect);library(Nippon)
username <- Sys.info()['user']
pathOutput <- paste0("C:/Users/", username, "/Desktop/R_Data_Write/")
setwd(pathOutput)
baseURL <- 'http://www5.cao.go.jp/keizai3/getsurei/'
if(!file.exists(paste0(pathOutput, fileName))) {
  download.file(paste0(baseURL,fileName), fileName , mode = 'wb')
}
buf0 <- 
  readWorksheetFromFile(paste0(pathOutput, fileName), sheet = 1, header = F)
tmp <- NA
for(ccc in 1:ncol(buf0)){
  if(!is.na(buf0[1,ccc])){tmp <- buf0[1,ccc]}
  buf0[1,ccc] <- tmp
}
tmp <- NA
for(ccc in 1:ncol(buf0)){
  if(!is.na(buf0[3,ccc])){tmp <- buf0[3,ccc]}
  buf0[3,ccc] <- tmp
}
colnames(buf0) <-
  sapply(paste0(buf0[1,],':',buf0[5,],buf0[3,]),zen2han)
buf1 <-
  buf0[!is.na(as.numeric(sapply(buf0[,4],zen2han))),]
tmp <- NA
for(rrr in 1:nrow(buf1)){
  if(!is.na(buf1[rrr,1])){tmp <- buf1[rrr,1]}
  buf1[rrr,1] <- tmp
}
buf1[,2] <-
  sapply(buf1[,2],
       function(x){
         ifelse(x == 'Ⅰ',
                '-3-31',
                ifelse(x == 'Ⅱ',  
                       '-6-30',
                       ifelse(x == 'Ⅲ', 
                              '-9-30','-12-31')))})
buf1[,1] <- 
  as.Date(paste0(buf1[,1],buf1[,2]))
buf1 <- 
  buf1[,-c(2,3)]
colnames(buf1)[1] <- 
  'Date'
buf2 <- buf1[,c(1,2)]
buf2[,-1] <-
  as.vector(apply(buf2[,-1,drop=F],2,as.numeric))
assign('gdpGAP',buf2,envir = .GlobalEnv)
```

```{r,warning=F,error=F,message=F,results='hold',echo=F}
dateFormat <- '%Y年%m月期'
fun_latestResult(obj = gdpGAP,dateFormat = dateFormat)
dataTitle <- paste0('日本のGDPギャップ(内閣府版):', latestResult)
dataSource <- '内閣府'
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- Source http://www5.cao.go.jp/keizai3/getsurei/getsurei-index.html

***

```{r warning=F, error=F, message=F, echo=F, results='asis'}
n <- 1
fun_generateKnit(objDF = gdpGAP,
                 plotNum = n,
                 group = 0,
                 barPlot = 1,
                 dygraphTitle = colnames(gdpGAP)[2],
                 quantiles = 2)
eval(parse(text = paste0('dygraphPlot', n, ' %>% ', ConsumptionTax)))
cat('<hr>')
eval(parse(text = paste0('dygraphPlot', n, ' %>% ', primeMinisterOfJapan_dygraph)))
cat('<hr>')
eval(parse(text = paste0('dygraphPlot', n, ' %>% ', boj_dygraph)))
cat('<hr>')
eval(parse(text = paste0('dygraphPlot', n, ' %>% ', event_dygraph_point,' %>%  ',event_dygraph_range)))
```

```{r warning=F, error=F, message=F, echo=F, results='hold'}
paste0(format(range(gdpGAP[,1]),dateFormat),collapse = ' ~ ')
cat('\n\n')
summary(gdpGAP[,2])
```

***

```{r warning=F, error=F, message=F, echo=F, results='asis'}
fun_dataTable(obj = gdpGAP,dateFormat = dateFormat)
```

***

```{r warning=F, error=F, message=F, echo=F, results='asis'}
fun_turningPoint(obj = gdpGAP,
                 dateFormat = dateFormat,
                 unit = '期',
                 judge=c('マイナスギャップ','プラスギャップ'))
cat(paste0('<h5>',texInclude0,'</h5>'))
```

***

<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
