---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-ForecastForTimeSeriesForexData.html')) })
title : "Forecast For Time Series Forex Data"
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 10
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---

<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet"> 
<style>
.main-container {max-width : 1000px; margin-left : auto; margin-right : auto;}
table{white-space : nowrap;}
td.negative {color : red;}
</style>

<script>
<!-- # Reference http://www.hanselman.com/blog/MakingNegativeNumbersTurnRedUsingCSSAndJavascript.aspx -->
function MakeNegative() {
  TDs = document.getElementsByTagName('td');
  for (var i=0; i<TDs.length; i++) {
    var temp = TDs[i];
    if (temp.firstChild.nodeValue.indexOf('-') == 0) temp.className = "negative";
  }
}
</script>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan

本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options,echo=F,cache=F}
options(width = 1000)
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
library(RCurl);library(knitr)
script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/timeSeriesForecast.r",
    ssl.verifypeer = F
  )
eval(parse(text = script))

script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/plotTimeSeries.r",
    ssl.verifypeer = F
  )
eval(parse(text = script))

script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/R-dygraphsFunction.r",
    ssl.verifypeer = F
  )
eval(parse(text = script))

script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/transposeDataFrame.r",
    ssl.verifypeer = F
  )
eval(parse(text = script))

script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/timeSeriesDataFundamentalStatistics.r",
    ssl.verifypeer = F
  )
eval(parse(text = script))

windowsFonts(Meiryo=windowsFont("Meiryo"))
options(scipen=100)
```

```{r warning=F,error=F,message=F,echo=F}
library(quantmod)
fredData <- list()
cnt <- 0
timseSeriesData <- 
  c(
    'EXJPUS','Japan / U.S. Foreign Exchange Rate',
    'Averages of daily figures. Noon buying rates in New York City for cable transfers payable in foreign currencies.',
    'EXUSEU','U.S. / Euro Foreign Exchange Rate',
    'Averages of daily figures. Noon buying rates in New York City for cable transfers payable in foreign currencies.',
    'EXUSUK','U.S. / U.K. Foreign Exchange Rate',
    'Averages of daily figures. Noon buying rates in New York City for cable transfers payable in foreign currencies.',
    'EXSFUS','South Africa / U.S. Foreign Exchange Rate',
    'Averages of daily figures. Noon buying rates in New York City for cable transfers payable in foreign currencies.'
  )
for (iii in seq(1, length(timseSeriesData), by = 3)) {
  cnt <- cnt + 1
  tmp <- getSymbols(timseSeriesData[iii], src = 'FRED', auto.assign = F)
  tmp <-
    data.frame(
      Date = as.Date(index(tmp)),
      tmp[, 1],
      check.names = F,
      row.names = NULL,
      stringsAsFactors = F
    )
  colnames(tmp)[2] <- timseSeriesData[iii + 1]
  fredData[[cnt]] <- tmp
  tail(fredData[[cnt]])
  if(iii == 1){allData <- tmp}else{allData <- merge(allData, tmp, by='Date', all=T)}
}
```

```{r warning=F,error=F,message=F,echo=F,results='hold'}
dateFormat <- '%Y-%m'
dataTitle <-
  paste0('Forecast for JPY,EURO,POUND and ZAR',
         ' - ',format(as.Date(tail(allData[,1],1)), dateFormat))
dataSource <- 'Federal Reserve Bank of St. Louis'
notes <- '複数のワードで検索する際は半角スペースで区切ってください'
notes0 <- "表中、-9999はNAを意味します"
Author <- "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
cat(paste("Title       : ", dataTitle, "\n"))
cat(paste("Data Source : ", dataSource, "\n"))
cat(paste("Author      : ", Author, "\n"))
cat(paste("特  記      : ", notes, "\n"))
cat(paste("特  記      : ", notes0, "\n"))
windowsFonts(Meiryo = windowsFont("Meiryo"))
options(scipen = 999)
```

```{r warning=F,error=F,message=F,echo=F,results='asis'}
for(iii in 1:cnt){
  tsData <- fredData[[iii]]
  tsData <- na.omit(tsData)
  cat(paste0('<h2>',colnames(tsData)[2],'</h2>'))
  par(mfrow = c(2,1))
  fun_plotTimeSeries(obj = tsData,chartType = 0,dateFormat = dateFormat,mar = c(4,5,4,2))
  fun_timeSeriesForecast(obj = tsData[,2], surrogatePlot = T, 
                         nnetarP = 12, surrogateK = 1, surrogateSignificance = 0.05)
  # surrogate
  cat(paste0('<h5><I>K=',1,', significance=',0.05,'</I></h5>'))
  surrogateMin <- min(result_surrogateTest$surrogates.statistics)
  surrogateMax <- max(result_surrogateTest$surrogates.statistics)
  if(surrogateMin <= result_surrogateTest$data.statistic & result_surrogateTest$data.statistic <= surrogateMax) { 
    result <- 'Null Hypothesis: Data comes from a linear stochastic process<br>Accept Null hypothesis'
    } else {
      result <- 'Null Hypothesis: Data comes from a linear stochastic process<br>Reject Null hypothesis'
    }
  cat(paste0('<h5>',result,'</h5>'))
  cat('<hr>')
  # surrogate
  confidenceInterval <- c(60,95)
  h <- 12
  # nnetar
  par(mfrow = c(2,1),family = 'Meiryo',mar = c(4,4,2,2))
  forecastResult <- forecast(result_nnetar, h=h)
  plot(forecastResult)
  panel.first = grid(nx = NULL,ny = NULL,lty = 2,equilogs = T)
  ylim <- c(min(forecastResult$mean),max(forecastResult$mean))
  xlim <- c(length(forecastResult$x) + 1,length(forecastResult$x) + h)
  plot(forecastResult,xlim=xlim,ylim=ylim,xaxt='n')
  axis(1, at = seq(xlim[1],xlim[2]), 
       labels = format(seq(as.Date(tail(tsData[,1],1)), by = "month", length.out = 13)[-1],dateFormat), las = 1)
  panel.first = grid(nx = NULL,ny = NULL,lty = 2,equilogs = T)
  cat('<hr>')
  # nnetar
  # arima
  par(mfrow = c(2,1),family = 'Meiryo',mar = c(4,4,2,2))
  forecastResult <- forecast(result_arima, h=h, level=confidenceInterval)
  plot(forecastResult)
  panel.first = grid(nx = NULL,ny = NULL,lty = 2,equilogs = T)
  ylim <- c(min(forecastResult$lower),max(forecastResult$upper))
  xlim <- c(length(forecastResult$x) + 1,length(forecastResult$x) + h)
  plot(forecastResult,xlim=xlim,ylim=ylim,xaxt='n')
  axis(1, at = seq(xlim[1],xlim[2]), 
       labels = format(seq(as.Date(tail(tsData[,1],1)), by = "month", length.out = 13)[-1],dateFormat), las=1)
  panel.first = grid(nx = NULL,ny = NULL,lty = 2,equilogs = T)
  cat('<hr>')
  # arima
  # arfima
  par(mfrow = c(2,1),family = 'Meiryo',mar = c(4,4,2,2))
  forecastResult <- forecast(result_arfima,level=confidenceInterval,h=12)
  plot(forecastResult)
  panel.first = grid(nx = NULL,ny = NULL,lty = 2,equilogs = T)
  ylim <- c(min(forecastResult$lower),max(forecastResult$upper))
  xlim <- c(length(forecastResult$x) + 1,length(forecastResult$x) + h)
  plot(forecastResult,xlim=xlim,ylim=ylim,xaxt='n')
  axis(1, at = seq(xlim[1],xlim[2]), 
       labels = format(seq(as.Date(tail(tsData[,1],1)), by = "month", length.out = 13)[-1],dateFormat), las=1)
  panel.first = grid(nx = NULL,ny = NULL,lty = 2,equilogs = T)
  # arfima
  cat('<hr>')
}
```

<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
