---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');htmlName<-'BusinessConfidence';rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-',htmlName,'.html')) })

title : 'Business Confidence In Japan'
author: 'アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp'
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 5
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 1000px;}</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000,scipen = 999)
```

```{r warning = F, error = F, message = F, echo = F}
fileName <- 
  'functionList.csv'
baseURL <- 
  'https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/'
functionList <- 
  read.csv(
    file = paste0(baseURL,'csv/',fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    RCurl::getURL(paste0(baseURL,functionList[iii,1]),ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
importData <- c('importBusinessConfidence.r')
script <-
  RCurl::getURL(paste0(baseURL,importData[1]),ssl.verifypeer = FALSE)
eval(parse(text = script))
```

```{r warning=F,error=F,message=F,results='hold',echo=F}
dataTitle <- 
  paste0("中小企業景況調査:",paste0(tail(businessConfidence[[1]][,1:2],1),collapse = '年'))
dataSource <- "中小企業庁"
windowsFonts(Meiryo = windowsFont("Meiryo"))
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- Source http://www.chusho.meti.go.jp/koukai/chousa/keikyo/

***

```{r warning=F, error=F, message=F, echo=F, results='asis'}
for(iii in seq(length(businessConfidence))){
  obj0 <- 
    tail(businessConfidence[[iii]],12*4)
  objCol <- 
    grep('di',colnames(obj0),ignore.case = T)[1]
  if(is.na(objCol)){objCol <- 3}
  obj <- 
    obj0[,c(1,2,objCol)]
  obj$col <- 
    ifelse(0<=obj[,3],'#4169e1','#dc143c')
  obj$Date <-
    paste0(obj[,1],'年',obj[,2])
  imageTitle <- 
    gsub('-業種:|-NA|-注意.+','',sheetTitle[iii])
  cat(paste0('#### ',imageTitle,'\n\n'))
  par(mar=c(10,4,3,1),family='Meiryo',font.main=1,cex.main=1)
  barplot(height = obj[,3],names.arg = obj$Date,las=2,
          col = obj$col,main = paste0(imageTitle,'\nSource:',dataSource),cex.names = 0.8)
  df <-
    data.frame(Date=paste0(obj0[,1],'年',obj0[,2]),obj0[,-c(1,2)],check.names = F,stringsAsFactors = F)
  fun_markdownTable(obj = fun_transposeDataFrame(obj = df,dateFormat = 0))
  cat('\n<hr>\n')
}
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fun_preparePlot()
pngFile <- 
  paste0(htmlName, "1.png")
png(file = pngFile, width = 1000, height = 600)
iii <- 3
obj0 <-
  businessConfidence[[iii]]
imageTitle <- 
  gsub('-業種:|-NA|-注意.+','',sheetTitle[iii])
obj0$Date <-
  as.Date(paste0(obj0[,1],'-',gsub('.+~([0-9]+)月期','\\1',obj0[,2]),'-1'))
obj <- obj0[,c(ncol(obj0),4:(ncol(obj0)-1))]
lineColors <-
  RColorBrewer::brewer.pal(8, 'Dark2')
ylim <- 
  c(floor(min(obj[,-1])),ceiling(max(obj[,-1])))
par(mar=c(4,3,4,1),family='Meiryo',font.main=1,cex.main=1.1)
colN <- 1
plot(x = obj[,1],y = obj[,2],type = 'o',ylim = ylim,xaxt = 'n',xlab = '',ylab = '',
     pch = 20,cex = 1,col = lineColors[colN],
     panel.first = grid(nx = NA,ny = NULL,lty = 2,equilogs = T),lwd = 1,
     main = paste0(imageTitle,'\nSource:中小企業庁'))
lines(x = obj[,1],y = obj[,3],type = 'o',col = lineColors[colN+1],pch = 20,cex = 1,lwd = 1)
lines(x = obj[,1],y = obj[,4],type = 'o',col = lineColors[colN+2],pch = 20,cex = 1,lwd = 1)
lines(x = obj[,1],y = obj[,5],type = 'o',col = lineColors[colN+3],pch = 20,cex = 1,lwd = 1)
lines(x = obj[,1],y = obj[,6],type = 'o',col = lineColors[colN+4],pch = 20,cex = 1,lwd = 1)
lines(x = obj[,1],y = obj[,7],type = 'o',col = lineColors[colN+5],pch = 20,cex = 1,lwd = 1)
lines(x = obj[,1],y = obj[,8],type = 'o',col = lineColors[colN+6],pch = 20,cex = 1,lwd = 1)
axis(side = 1,at = obj[,1],labels = format(obj[,1],'%Y-%m'),las=1)
graphics::legend(x = 'top',col = lineColors[colN:(colN+6)],lty = 1,
                 legend = colnames(obj)[-1],cex = 1.2,bty = 'n',lwd = 4)
dev.off()
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fun_outputMD(tags = '中小企業景況調査',
             objDF = fun_transposeDataFrame(obj = obj,dateFormat = '%Y-%m',colName = '項目',tailN=8),
             htmlName = htmlName,
             image1 = 1,
             image2 = 0,
             title = dataTitle,
             tableTitle = '直近8期',
             tableName = imageTitle)
fun_updateURLcsv()
```

<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
