---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-OECD-CompositeLeadingIndicators.html')) })

title : 'OECD:Composite Leading Indicators'
author: 'アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp'
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 5
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<style>
.main-container {max-width : 1000px; margin-left : auto; margin-right : auto;}
table{white-space : nowrap;}
td.negative {color : red;}
</style>

<script>
<!-- # Reference http://www.hanselman.com/blog/MakingNegativeNumbersTurnRedUsingCSSAndJavascript.aspx -->
function MakeNegative() {
  TDs = document.getElementsByTagName('td');
  for (var i=0; i<TDs.length; i++) {
    var temp = TDs[i];
    if (temp.firstChild.nodeValue.indexOf('-') == 0) temp.className = "negative";
  }
}
</script>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan

本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000)
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
library(RCurl);library(knitr)
script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/importOECDStatisticData.r",
    ssl.verifypeer = F
  )
eval(parse(text = script))

script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/timeSeriesForecast.r",
    ssl.verifypeer = F
  )
eval(parse(text = script))

script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/plotTimeSeries.r",
    ssl.verifypeer = F
  )
eval(parse(text = script))

script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/R-dygraphsFunction.r",
    ssl.verifypeer = F
  )
eval(parse(text = script))

script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/transposeDataFrame.r",
    ssl.verifypeer = F
  )
eval(parse(text = script))

script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/timeSeriesDataFundamentalStatistics.r",
    ssl.verifypeer = F
  )
eval(parse(text = script))

windowsFonts(Meiryo=windowsFont("Meiryo"))
options(scipen=100)
```

```{r warning=F, error=F, message=F, echo=F, results='asis'}
mm <- 10
sdmxURL <- paste0("http://stats.oecd.org/restsdmx/sdmx.ashx/GetData/MEI_CLI/LOLITOTR_GYSA.AUS+AUT+BEL+CAN+CHL+CZE+DNK+EST+FIN+FRA+DEU+GRC+HUN+IRL+ISR+ITA+JPN+KOR+LVA+LUX+MEX+NLD+NZL+NOR+POL+PRT+SVK+SVN+ESP+SWE+CHE+TUR+GBR+USA+EA19+G4E+G-7+NAFTA+OECDE+OECD+ONM+A5M+NMEC+BRA+CHN+IND+IDN+RUS+ZAF.M/all?startTime=1947-02&endTime=2016-",mm)
importOECDStatisticData(sdmxURL = sdmxURL)
oecd01 <- allOECDData
oecd01[,-1] <- apply(oecd01[,-1],2,function(x)round(x,1))
sdmxTitle01 <- '12-month rate of change of the trend restored CLI'

sdmxURL <- paste0("http://stats.oecd.org/restsdmx/sdmx.ashx/GetData/MEI_CLI/LOLITOAA.AUS+AUT+BEL+CAN+CHL+CZE+DNK+EST+FIN+FRA+DEU+GRC+HUN+IRL+ISR+ITA+JPN+KOR+LVA+LUX+MEX+NLD+NZL+NOR+POL+PRT+SVK+SVN+ESP+SWE+CHE+TUR+GBR+USA+EA19+G4E+G-7+NAFTA+OECDE+OECD+ONM+A5M+NMEC+BRA+CHN+IND+IDN+RUS+ZAF.M/all?startTime=1947-02&endTime=2016-",mm)
importOECDStatisticData(sdmxURL = sdmxURL)
oecd02 <- allOECDData
oecd02[,-1] <- apply(oecd02[,-1],2,function(x)round(x,1))
sdmxTitle02 <- 'Amplitude adjusted'
```

```{r warning=F, error=F, message=F, echo=F, results='hold'}
dateFormat <- '%Y-%m'
dataTitle <- paste0('OECD 景気先行指数 - ', format(tail(allOECDData[,1],1),dateFormat))
dataSource <- 'Organisation for Economic Co-operation and Development：経済協力開発機構'
Author <- 'アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp'
cat(paste('Title       : ',dataTitle,'\n'))
cat(paste('Data Source : ',dataSource,'\n'))
cat(paste('Author      : ',Author,'\n'))
windowsFonts(Meiryo=windowsFont('Meiryo'))
```

```{r warning=F, error=F, message=F, echo=F, results='asis'}
tsData <-
  tail(na.omit(oecd01[,grep('date|jpn|chn|usa', colnames(oecd01), ignore.case = T)]),12*10)
fun_dygraph(obj = tsData, colors = c('blue','red','green'),
            mainTitle = paste0(sdmxTitle01,' - ', 
                               paste0(format(range(tsData[,1]), dateFormat), collapse = '~')),
            plotNum = 1, legendWidth = '300', barPlot0 = 0, group = 0)
tsData <-
  tail(na.omit(oecd02[,grep('date|jpn|chn|usa', colnames(oecd02), ignore.case = T)]),12*10)
fun_dygraph(obj = tsData, colors = c('blue','red','green'),
            mainTitle = paste0(sdmxTitle02,' - ', 
                               paste0(format(range(tsData[,1]), dateFormat), collapse = '~')),
            plotNum = 2, legendWidth = '300', barPlot0 = 0, group = 0)
```

```{r warning=F, error=F, message=F, echo=F, results='asis'}
dygraphPlot1
```

***

```{r warning=F, error=F, message=F, echo=F, results='asis'}
dygraphPlot2
```

***
#### `r sdmxTitle01` 
```{r warning=F, error=F, message=F, echo=F, results='asis'}
knitr::kable(fun_transposeDataFrame(obj = oecd01,dateFormat = dateFormat,colName = 'Country/Region'),row.names = F)
```

***
#### `r sdmxTitle02` 
```{r warning=F, error=F, message=F, echo=F, results='asis'}
knitr::kable(fun_transposeDataFrame(obj = oecd02,dateFormat = dateFormat,colName = 'Country/Region'),row.names = F)
```

***
<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
