---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-TREASTandMBST.html')) })

title : 'U.S. Treasury Securities and Mortgage-backed Securities held by the Federal Reserve'
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 4
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 1000px;}</style>
<style>table:not(#amcc) {font-size: 85%;}</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000)
```

```{r warning = F, error = F, message = F, echo = F}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r warning=F,error=F,message=F,echo=F}
library(lubridate);library(quantmod)
cnt <- 0
importData <-
  c('TREAST','U.S. Treasury securities held by the Federal Reserve: All Maturities',
    'MBST','Mortgage-backed securities held by the Federal Reserve: All Maturities')
for (lll in seq(1, length(importData), by = 2)) {
  cnt <- cnt + 1
  tmp <- getSymbols(importData[lll], src = 'FRED', auto.assign = F)
  tmp <-
    data.frame(Date = as.Date(index(tmp)), tmp[, 1], 
               check.names = F, 
               row.names = NULL, 
               stringsAsFactors = F)
  colnames(tmp)[2] <- 
    paste0(importData[lll + 1],'(',importData[lll],')')
  if(lll == 1){
    totalSecurities <- tmp
  }else{
      totalSecurities <- merge(totalSecurities,tmp,by='Date',all=T)
  }
}
totalSecurities[,-1] <- 
  apply(totalSecurities[,-1],2,function(x) x*10^-6)
totalSecurities$Total <-
  totalSecurities[,2]+totalSecurities[,3]
```

```{r,warning=F,error=F,message=F,results='asis',echo=F}
fun_latestResult(obj = totalSecurities,objColumn = 4,dateFormat = '%Y-%m-%d')
dataTitle <- 
  paste0('U.S. Treasury Securities and Mortgage-backed Securities held by the Federal Reserve(T$):',
         latestResult)
dataSource <- 
  'Federal Reserve Bank of St.Louis'
windowsFonts(Meiryo = windowsFont("Meiryo"))
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- Trillions of Dollars,Not Seasonally Adjusted

***

```{r warning=F,error=F,message=F,echo=F,results='asis'}
n <- 1
fun_generateKnit(objDF = totalSecurities,plotNum = n)
eval(parse(text = paste0('dygraphPlot', n)))
```

***

```{r warning=F,error=F,message=F,echo=F,results='asis'}
fun_dataTable(obj = tail(totalSecurities,5*12),dateFormat = '%Y-%m-%d')
```

***

#### Week over Week(%)

```{r warning=F,error=F,message=F,echo=F,results='asis'}
fun_makeDiffRatioTable(obj = totalSecurities,lag = 1)
fun_markdownTable(obj = fun_transposeDataFrame(obj = diffRatioDF,tailN = 4))
```

***
<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
