---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-EconomyWatchersSurvey.html')) })
title : "Economy Watchers Survey"
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 3
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 1000px;}</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
# ―,ソ,噂,欺,圭,構,蚕,十,申,貼,能,表,暴,予,禄,兔
options(width = 1000)
```

```{r warning = F, error = F, message = F, echo = F}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r warning=F,error=F,message=F,echo=F}
library(XML);library(XLConnect);library(lubridate);library(Nippon)
username <- Sys.info()['user']
pathOutput <- paste0("C:/Users/", username, "/Desktop/R_Data_Write/")
url <- "http://www5.cao.go.jp/keizai3/watcher.html"
htmlMarkup <- htmlParse(url)
links <- xpathSApply(htmlMarkup, "//a/@href")
files <- links[grep('.xls',links)]
files <-  gsub('/keizai3','',files)
files <- gsub('/watcher','',files)
urlToData <- paste0('http://www5.cao.go.jp/keizai3/watcher/', files)
```

```{r warning=F,error=F,message=F,echo=F}
setwd(pathOutput)
fileName <- 'watcher3'
download.file(urlToData[grep(fileName,urlToData)], paste0(fileName,'.xls'), mode = 'wb')
assign(fileName, readWorksheetFromFile(paste0(pathOutput,fileName,'.xls'), sheet = 1, check.names = F, header = F))
```

```{r warning=F,error=F,message=F,echo=F}
buf0 <- get(fileName)
keyWord <- '家計動向'
bufR <- which(apply(buf0,1,function(x){(length(grep(keyWord,x)))})!=0)
tmp1 <- NA
tmp2 <- NA
for(ccc in 1:ncol(buf0)){
  tmp01 <- buf0[bufR,ccc]
  tmp02 <- buf0[bufR+1,ccc]
  if(!is.na(tmp01)){tmp1 <- tmp01}
  if(!is.na(tmp02)){tmp2 <- tmp02}
  buf0[bufR,ccc] <- tmp1  
  buf0[bufR+1,ccc] <- tmp2  
}
keyWord <- '合計'
bufC <- which(apply(buf0,2,function(x){(length(grep(keyWord,x)))})!=0)
cNames <- 
  ifelse(!is.na(buf0[bufR+1,]),
       ifelse(!is.na(buf0[bufR+2,]),paste0(buf0[bufR,],'-',buf0[bufR+1,],'-',buf0[bufR+2,]),
              paste0(buf0[bufR,],'-',buf0[bufR+1,])),buf0[bufR,])
cNames <- gsub('\n','',cNames)
colnames(buf0) <- cNames
title <- zen2han(paste0(buf0[2,1],'-',buf0[3,1]))
bufC <- which(!is.na(as.numeric(substring(buf0[,1],1,4))))[1]
buf1 <- buf0[-c(1:(bufC-1)),]
dateStart <- as.Date(paste0(gsub('年','-',buf1[1,1]),zen2han(gsub('月','-1',buf1[1,2]))))
buf1[,1] <- seq(dateStart,by = 'month',length.out = nrow(buf1))  
buf2 <- buf1[,-2]
colnames(buf2)[1] <- 'Date'
buf2[,-1] <- apply(buf2[,-1],2,as.numeric)
buf3 <- buf2[!is.na(buf2[,2]),]
dataSet <- buf3
```

```{r warning=F,error=F,message=F,echo=F,results='hold'}
dateFormat <- '%Y年%m月'
fun_latestResult(obj = dataSet,dateFormat = dateFormat,objColumn = c(3,23))
dataTitle <- 
  paste0('景気ウォッチャー調査(原数値):', latestResult)
dataSource <- '内閣府'
windowsFonts(Meiryo=windowsFont("Meiryo"))
options(scipen = 999)
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- Source http://www5.cao.go.jp/keizai3/watcher/watcher_menu.html

***

```{r warning=F, error=F, message=F, echo=F}
texDygraph <- vector()
for(iii in 2:ncol(dataSet)){
  fun_generateKnit(objDF = na.omit(dataSet[,c(1,iii)]), 
                   plotNum = iii, 
                   group = 0, 
                   colors = c('blue','red','green'), 
                   dygraphTitle = colnames(dataSet)[iii])
  assign(paste0('knit_expanded', iii),
         paste0("\n```{r warning=F, error=F, message=F, echo=F, results='asis'}\n\n",
                "eval(parse(text = paste0('dygraphPlot", iii," %>% ', primeMinisterOfJapan_dygraph)))",
                "\n\ncat('<hr>')\n\n```"),envir = .GlobalEnv)
  texDygraph <- 
    c(texDygraph, paste0('knit_expanded', iii))
}
```

`r paste(knitr::knit(text = sapply(texDygraph,get)), collapse = '\n')`

```{r warning=F, error=F, message=F, echo=F, results='asis'}
fun_dataTable(obj = tail(dataSet,5*12),dateFormat = dateFormat)
```

***
#### 前年同月差(ポイント)

```{r warning=F,error=F,message=F,echo=F,results='asis'}
fun_markdownTable(obj = fun_transposeDataFrame(obj = fun_makeDiffTable(obj = dataSet,
                                                                       lag = 12),
                                               dateFormat = dateFormat))
```

***
<script>MakeNegative()</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
