---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');htmlName<-'QuantitativeAnalysisForBitcoin';rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[4,1],'am-consulting.co.jp-',htmlName,'.html')) })

title : 'Quantitative Analysis For Bitcoin'
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 4
    fig_width: 9
    keep_md: no
    md_extensions: -ascii_identifiers 
    includes:
       in_header: insertHeader.html
    self_contained: false
---

```{r setup, include=FALSE}
tag <-
  read.csv(file = 'https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/components/insertHeader.csv',header = F,fileEncoding = 'UTF8')
tagTxt <- ''
for(rrr in 1:nrow(tag)){
  tagTxt <- paste0(tagTxt,tag[rrr,1],'\n')
}
insertFile <- file("insertHeader.html")
writeLines(text = tagTxt,con = insertFile)
close(insertFile)
```

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo = F, cache = F}
options(width = 900)
```

```{r warning = F, error = F, message = F, echo = F}
windowsFonts(Meiryo = windowsFont("Meiryo"))
options(scipen = 100)
```

```{r warning = F, error = F, message = F, echo = F, results = 'hide'}
fileName <-
  'defaultPath.csv'
username <- 
  Sys.info()['user']
pathToFile <- 
  paste0('C:/Users/', username,'/Desktop/pathToCSV/')
setwd(pathToFile)
buf000 <- 
  read.csv(fileName, header = F, skip = 0, stringsAsFactor = F, check.names = F, fileEncoding = 'utf-8')
pathOutput <- 
  paste0("C:/Users/", username, buf000[2,1],'csv/')
setwd(pathOutput)
bitCoinCSV <- 'bitCoin.csv'
bitCoinOld <- 
  read.csv(file = bitCoinCSV, header = T, as.is = T, check.names = F)
bitCoinOld[,1] <-
  as.Date(bitCoinOld[,1])
head(bitCoinOld);tail(bitCoinOld)
```

```{r warning = F, error = F, message = F, echo = F, results='hide'}
library(quantmod)
tmp <- getSymbols('BTC/USD', 
                  src = "oanda", 
                  auto.assign = F, 
                  from = Sys.Date() - 365 * 10, to = Sys.Date())
bitCoinNew <- 
  data.frame(Date = as.Date(index(tmp)),
             tmp,
             check.names = F,
             stringsAsFactors = F,
             row.names = NULL)
colnames(bitCoinNew)[2] <- 
  gsub('\\.','/',colnames(bitCoinNew)[2])
head(bitCoinNew);tail(bitCoinNew)
bitCoinNew <- 
  subset(bitCoinNew, tail(bitCoinOld[,1],1) < bitCoinNew[,1])
if(nrow(bitCoinNew) != 0){
  bitCoin <- 
    rbind(bitCoinOld,bitCoinNew)
  setwd(pathOutput)
  write.csv(x = bitCoin, file = bitCoinCSV, quote = F, row.names = F, append = F, fileEncoding = 'utf8')
}else{
  bitCoin <- bitCoinOld
}
```

```{r warning = F, error = F, message = F, echo = F, results='hide'}
# GOLD
setwd(pathOutput)
GoldPriceCSV <- 'GoldPrice.csv'
GoldPriceOld <- 
  read.csv(file = GoldPriceCSV, header = T, as.is = T, check.names = F)
GoldPriceOld[,1] <-
  as.Date(GoldPriceOld[,1])
head(GoldPriceOld);tail(GoldPriceOld)
tmp <- getSymbols('XAU/USD', 
                  src = "oanda", 
                  auto.assign = F, 
                  from = Sys.Date() - 365 * 10, to = Sys.Date())
GoldPriceNew <- 
  data.frame(Date = as.Date(index(tmp)),
             tmp,
             check.names = F,
             stringsAsFactors = F,
             row.names = NULL)
colnames(GoldPriceNew)[2] <- 
  gsub('\\.','/',colnames(GoldPriceNew)[2])
head(GoldPriceNew);tail(GoldPriceNew)
GoldPriceNew <- 
  subset(GoldPriceNew, tail(GoldPriceOld[,1],1) < GoldPriceNew[,1])
if(nrow(GoldPriceNew) != 0){
  GoldPrice <- 
    rbind(GoldPriceOld,GoldPriceNew)
  write.csv(x = GoldPrice, file = GoldPriceCSV, quote = F, row.names = F, append = F, fileEncoding = 'utf8')
}else{
  GoldPrice <- GoldPriceOld
}
mergeData <- merge(bitCoin,GoldPrice,by = 'Date')
```

```{r warning = F, error = F, message = F, echo = F}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r warning = F, error = F, message = F, results = 'hide', echo = F}
fun_latestResult(obj = bitCoin,dateFormat = '%Y-%m-%d')
dataTitle <- 
  paste0('-仮想通貨それは時代の要請あるいは狂乱に花咲くチューリップ-ビットコインの計量分析:',latestResult)
dataSource <- 
  'OANDA Corporation'
appendTxt <-
  ' %>% dyEvent(\'2014-2-28\', \'Mt. Gox filed for bankruptcy protection in Tokyo\', labelLoc = \'bottom\')'
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- Source https://www.oanda.com/
- 『On 28 February 2014 Mt. Gox filed for bankruptcy protection in Tokyo』(Source https://en.wikipedia.org/wiki/Mt._Gox)

***

#### Comparing between Bitcoin and Gold

```{r warning = F, error = F, message = F, echo = F, results='asis'}
n <- 10
fun_generateKnit(objDF = mergeData, 
                 plotNum = n, 
                 group = 0,
                 dygraphTitle = 'Unit:$')
eval(parse(
  text =
    paste0('dygraphPlot',
           n,
           appendTxt)))
cat('<hr>')
fun_markdownTable(obj = fun_transposeDataFrame(obj = mergeData,tailN = 7))
cat('<hr>')
tDF <- fun_transposeDataFrame(obj = rbind(head(mergeData,1),tail(mergeData,1)))
fun_markdownTable(obj = data.frame(tDF,
                                   `Change(%)`=round((tDF[,3]/tDF[,2]-1)*100,2),
                                   stringsAsFactors = F,
                                   check.names = F))
```

***
#### Historical Volatility of Bitcoin

```{r warning = F, error = F, message = F, echo = F, results='asis'}
width <- 30
cat(paste0('- Width:',width))
n <- 100
fun_generateKnit(objDF = fun_historicalVolatility(obj = bitCoin,width = width), 
                 plotNum = n, 
                 group = 0,
                 dygraphTitle = 'Unit:%',
                 quantiles = 2)
eval(parse(
  text =
    paste0('dygraphPlot',
           n,
           appendTxt)))
```

***
#### `r paste0(colnames(bitCoin)[2], ':', paste0(range(bitCoin[,1]), collapse = ' ~ '))`

- Highest & Lowest

```{r warning = F, error = F, message = F, echo = F, results='asis'}
tmp <-
  subset(bitCoin, max(bitCoin[,2]) == bitCoin[,2] | min(bitCoin[,2]) == bitCoin[,2])
fun_markdownTable(obj = tmp)
```

***

```{r warning = F, error = F, message = F, echo = F}
n <- 1
fun_generateKnit(objDF = bitCoin, 
                 plotNum = n, 
                 group = 0,
                 dygraphTitle = 'Unit:$',
                 colors = RColorBrewer::brewer.pal(3, "Set2")[n],
                 quantiles = 2)
eval(parse(
  text =
    paste0('dygraphPlot',
           n,
           appendTxt)))
```

***

```{r warning = F, error = F, message = F, echo = F}
n <- 2
diffDF <- fun_makeDiffTable(obj = bitCoin)
fun_generateKnit(objDF = diffDF, 
                 plotNum = n, 
                 barPlot = 1, 
                 group = 0, 
                 dygraphTitle = 'In comparison with the previous day(Unit:$)',
                 colors = RColorBrewer::brewer.pal(3, "Set2")[n],
                 quantiles = 2)
eval(parse(
  text =
    paste0('dygraphPlot',
           n,
           appendTxt)))
```

***

```{r warning = F, error = F, message = F, echo = F}
n <- 3
diffRatioDF <- fun_makeDiffRatioTable(obj = bitCoin)
fun_generateKnit(objDF = diffRatioDF, 
                 plotNum = n, 
                 barPlot = 1, 
                 group = 0, 
                 dygraphTitle = 'In comparison with the previous day(Unit:%)',
                 colors = RColorBrewer::brewer.pal(3, "Set2")[n],
                 quantiles = 2)
eval(parse(
  text =
    paste0('dygraphPlot',
           n,
           appendTxt)))
```

***

```{r warning = F, error = F, message = F, echo = F}
fun_hist <- 
  function(obj,
           objColumn = 2,
           histWidth = 10, 
           color = RColorBrewer::brewer.pal(8, "Set2")[n], 
           main = colnames(obj)[objColumn],
           xlab = '',
           labels = F,
           mar = c(4,5,2,2),
           font.axis = 1,
           font.main = 1,
           font.lab = 1,
           font.sub = 1,
           cex.main = 1,
           cex.lab = 1.0,
           cex.axis = 1.0){
    breaks <-
      seq(floor(min(obj[,objColumn]) / histWidth) * histWidth, 
          ceiling(max(obj[,objColumn]) / histWidth) * histWidth, 
          histWidth)
    par(mar = mar,
        family = 'Meiryo',
        font.axis = font.axis,
        font.main = font.main,
        font.lab = font.lab,
        font.sub = font.sub,
        cex.main = cex.main,
        cex.lab = cex.lab,
        cex.axis = cex.axis
        )
    histogram <-
      hist(obj[,objColumn],
         breaks = breaks, 
         col = color,
         xlab = xlab,
         main = paste0(main,'. Bin:',histWidth),
         plot = T)
    panel.first = grid(nx = NULL,
                       ny = NULL,
                       lty = 3,
                       equilogs = T)
    if(labels == T){    
      text(histogram$mids,
           histogram$counts,
           labels = paste0(histogram$counts,'\n'),
           cex = 1.3,
           font = 3)
    }
  }
```

```{r warning = F, error = F, message = F, echo = F, results='asis',fig.height=5}
par(mfrow = c(1,3))
dataSet <- bitCoin
n <- 1
fun_hist(obj = dataSet, histWidth = 100.0, main =  paste0(colnames(dataSet)[2],'(Unit:$)'))
dataSet <- diffDF
n <- 2
fun_hist(obj = dataSet, histWidth = 10.0, main =  paste0(colnames(dataSet)[2],':In comparison with the previous day(Unit:$)'))
dataSet <- diffRatioDF
n <- 3
fun_hist(obj = dataSet, histWidth = 1.0, main =  paste0(colnames(dataSet)[2],':In comparison with the previous day(Unit:%)'))
```

***
#### Fundamental Statistics
- `r colnames(bitCoin)[2]`

```{r warning = F, error = F, message = F, echo = F, results='asis'}
fun_timeSeriesDataFundamentalStatistics(obj = bitCoin)
fun_markdownTable(obj = data.frame(Item = row.names(statisticsTable), 
                                   statisticsTable, check.names = F, stringsAsFactors = F))

```

***
#### Fundamental Statistics By Year
- `r colnames(bitCoin)[2]`

```{r warning = F, error = F, message = F, echo = F, results='asis'}
library(lubridate)
fun_statYearly <- 
  function(obj){
    obj$YYYY <- 
      year(obj[,1])
    obj$mm <-
      month(obj[,1])
    for(yyyy in seq(range(obj$YYYY)[1],range(obj$YYYY)[2])){
      obj0 <-
        subset(obj,obj$YYYY == yyyy)
      sampleStandardDeviation <-
        sqrt(var(obj0[,2]) * (length(obj0[,2]) - 1) / length(obj0[,2]))
      n <- 
        length(obj0[,2])
      obj1 <-
        as.data.frame(cbind(summary(obj0[,2])))
      obj2 <-
        rbind(`n` = n, obj1, `Sample Standard Deviation` = round(sampleStandardDeviation,2))
      colnames(obj2)[1] <- paste0('Year',yyyy)
      if(yyyy == range(obj$YYYY)[1]){
        statDF <- obj2
      }else{
        statDF <- cbind(statDF,obj2)
      }
    }
    assign('statDF',
           data.frame(Item = row.names(statDF), statDF, check.names = F, stringsAsFactors = F),
           envir = .GlobalEnv)
}
fun_statYearly(obj = bitCoin)
fun_markdownTable(statDF)
```

***
##### `r paste0(colnames(bitCoin)[2],':In comparison with the previous day(Unit:%)')`

```{r warning = F, error = F, message = F, echo = F, results='asis'}
fun_statYearly(obj = diffRatioDF)
fun_markdownTable(statDF)
```

***
#### Autocorrelation
- Lag = 0:Dropped

```{r warning = F, error = F, message = F, echo = F, results='asis',fig.height=5}
fun_plotACF <- 
  function(obj, acfLag, acfType = 'correlation', plot = T, acfMainTitle = '', drop0 = F){
    acf(x = obj,
        lag.max = acfLag,
        type = acfType,
        drop.lag.0 = drop0,
        plot = plot,
        main = acfMainTitle
        )
    panel.first = grid(nx = NULL,
                       ny = NULL,
                       lty = 2,
                       equilogs = T)
  }
par(family = 'Meiryo', cex.main = 1.0, cex.lab = 1.0, cex.axis = 1.0, font.main = 1,mfrow = c(1,2))
fun_plotACF(obj = bitCoin[,2],
            acfLag = 365 * 2,
            acfMainTitle = colnames(bitCoin)[2],
            drop0 = T)
fun_plotACF(obj = diffRatioDF[,2],
            acfLag = 365 * 2,
            acfMainTitle = paste0(colnames(bitCoin)[2],':In comparison with the previous day(Unit:%)'),
            drop0 = T)
```

```{r warning=F,error=F,message=F,echo=F}
read.fun <- 
  c('fun.plot.ggplot.timeseries.r','fun.create.html.table.r','fun.plot.ggplot.ann.line.text.r','fun.create.diff.ma.data.r','fun.plot.ggplot.bar.r')
base.url <- 'https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/public.code/'
for(iii in seq(length(read.fun))){
  code <- RCurl::getURL(url = paste0(base.url,read.fun[iii]),ssl.verifypeer = F);eval(parse(text = code))
}
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
username <- Sys.info()['user']
pathToFile <- paste0('C:/Users/', username,'/Desktop/pathToCSV/')
setwd(pathToFile)
fileName <- 'defaultPath.csv'
buf <-
  read.csv(file = fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,
           fileEncoding = 'utf-8',quote = "\"")
pathOutputTOchart <- paste0("C:/Users/", username, buf[4,1])
setwd(pathOutputTOchart)
#---------------------------------------------------
pngFile <-
  paste0(htmlName, "1.png")
png(file = pngFile, width = 1000, height = 600)
obj <- mergeData[2016<=year(mergeData$Date),]
g <- fun.plot.ggplot.timeseries(load.library = T,obj = obj,y.breaks = 30,lab.title = 'The crypto currency is a revolutionary asset or a tulip 400 years ago?',lab.caption = 'Unit:$\nData source:OANDA Corporation',x.label.date.format = '%Y-%m-%d',point = F,x.breaks = 6)
data <- rbind(bitCoin[which.max(bitCoin[,2]),],tail(bitCoin,1))
data[,2] <- round(data[,2])
g <- fun.plot.ggplot.text.repel(data = data,load.library = T,size = 5,col = '#696969')
print(g)
dev.off()
pngFile <-
  paste0(htmlName, "2.png")
png(file = pngFile, width = 1000, height = 600)
diff.df0 <- fun.create.diff.ma.data(obj = obj)
diff.df <- tail(diff.df0[,c(1,7)],40)
colnames(diff.df)[2] <- gsub('\\(比,1,1\\)','\\(comparison with the previous day,%\\)',colnames(diff.df)[2])
g <- fun.plot.ggplot.bar(load.library = T,obj = diff.df)
print(g)
dev.off()
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fun_outputMD(tags = 'ビットコイン,バブル経済',
             objDF = fun_transposeDataFrame(obj = bitCoin),
             htmlName = htmlName,
             image1 = 1,image2 = 1,
             title = dataTitle,
             tableTitle = '直近5日分',
             tableName = 'ビットコイン価格',
             buf.row = 4)
fun_updateURLcsv.olive()
fun_updateURLcsv()
```

***
<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
