---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-BreakevenInflationRate.html')) })

title : "Breakeven Inflation Rate,Treasury Constant Maturity Securities"
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 3
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 1000px;}</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000)
```

```{r warning = F, error = F, message = F, echo = F}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
library(lubridate);library(quantmod)
fredData <- list()
cnt <- 0
importData <- c(
    'DEXJPUS', 'Japan / U.S. Foreign Exchange Rate',
    'DGS10',   '10-Year Treasury Constant Maturity Rate',
    'T10YIE',  '10-Year Breakeven Inflation Rate',
    'T5YIFR',  '5-Year, 5-Year Forward Inflation Expectation Rate')
for (lll in seq(1, length(importData), by = 2)) {
  cnt <- 
    cnt + 1
  tmp <- 
    getSymbols(importData[lll], src = 'FRED', auto.assign = F)
  tmp <-
    data.frame(Date = as.Date(index(tmp)), tmp[, 1], check.names = F, row.names = NULL, stringsAsFactors = F)
  colnames(tmp)[2] <- 
    importData[lll + 1]
  fredData[[cnt]] <- 
    tmp
  if(lll == 1){
    allDataUSA <- 
      tmp
  }else{
    allDataUSA <- 
      merge(allDataUSA, tmp, by = 'Date', all = T)
  }
}
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/Rscript/master/Rscript_JGBInterestRate.r",
    ssl.verifypeer = F)
eval(parse(text = script))
colnames(jgbData)[-1] <- 
  paste0('JGB-',colnames(jgbData)[-1],'(%)')
allData <- 
  merge(allDataUSA, jgbData, by = 'Date', all = T)
colnames(allData)
```

```{r warning=F,error=F,message=F,echo=F,results='hold'}
fun_latestResult(obj = allData,objColumn = c(4),dateFormat = '%Y-%m-%d')
dataTitle <- 
  paste0('期待インフレ率(米国)、米国財務省証券利回り、日本国債利回りおよびドル円為替レート:',latestResult)
dataSource <- 
  'Federal Reserve Bank of St. Louis、財務省'
windowsFonts(Meiryo=windowsFont("Meiryo"))
options(scipen=9999)
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`

***

#### Treasury Constant Maturity Rate,Breakeven Inflation Rate and Forward Inflation Expectation Rate(%)

```{r warning=F,error=F,message=F,echo=F,results='asis'}
n <- 1
obj <- allData[,c(1,3:5)]
fun_generateKnit(objDF = obj,plotNum = n,group = 0)
eval(parse(text = paste0('dygraphPlot', n)))
```

***
#### Japan / U.S. Foreign Exchange Rate

```{r warning=F,error=F,message=F,echo=F,results='asis'}
n <- 2
obj <- allData[,c(1,2)]
fun_generateKnit(objDF = obj,plotNum = n,group = 0)
eval(parse(text = paste0('dygraphPlot', n)))
```

***
#### Japanese Government Bonds Interest Rate(%)

```{r warning=F,error=F,message=F,echo=F,results='asis'}
n <- 3
obj <- allData[,c(1,10,15)]
fun_generateKnit(objDF = obj,plotNum = n,group = 0)
eval(parse(text = paste0('dygraphPlot', n)))
```

***
#### Gap In Interest Rates Between Japanese Government Bonds Interest Rate and Treasury Constant Maturity Rate
- Gap(%):`r ccc01 <- 3;ccc02 <- 15;paste0(colnames(allData)[c(ccc01,ccc02)],collapse = ' between ')`

```{r warning=F,error=F,message=F,echo=F,results='asis'}
n <- 4
obj <- data.frame(Date =allData[,1], 
                  Gap = allData[,ccc01]-allData[,ccc02], 
                  stringsAsFactors = F, 
                  check.names = F)
fun_generateKnit(objDF = obj,plotNum = n,group = 0)
eval(parse(text = paste0('dygraphPlot', n)))
```

***
#### Normalized chart
- Center:subtracting the means
- Scale:dividing the centered vector by their standard deviations 
- Gap(%):`r ccc01 <- 3;ccc02 <- 5;paste0(colnames(allData)[c(ccc01,ccc02)],collapse = ' between ')`

```{r warning=F,error=F,message=F,echo=F,results='asis'}
obj <- 
  na.omit(allData[,c(1,2,3,4,15)])
obj <-
  data.frame(obj[,c(1,2,4)], Gap = obj[,ccc01]-obj[,ccc02],stringsAsFactors = F,check.names = F)
obj0 <-
  data.frame(obj[,1,drop=F], scale(obj[,-1]), stringsAsFactors = F, check.names = F)
n <- 5
fun_generateKnit(objDF = obj0,plotNum = n,group = 0)
eval(parse(text = paste0('dygraphPlot', n)))
```

```{r warning=F,error=F,message=F,echo=F,results='asis'}
library(corrplot)
library(PerformanceAnalytics)
fun_makeDiffTable(obj = obj,lag = 1)
```

***
#### Correlation coefficients between the first difference of each time series.
- Latest `r days <- 30*12;days`days.

```{r warning=F,error=F,message=F,echo=F,results='asis',fig.height=5}
chart.Correlation(
  tail(diffDF[,-1],days),
  method = 'pearson')
```

***
- Latest `r days <- 30*6;days`days.

```{r warning=F,error=F,message=F,echo=F,results='asis',fig.height=5}
chart.Correlation(
  tail(diffDF[,-1],days),
  method = 'pearson')
```

***
- Latest `r days <- 30*3;days`days.

```{r warning=F,error=F,message=F,echo=F,results='asis',fig.height=5}
chart.Correlation(
  tail(diffDF[,-1],days),
  method = 'pearson')
```

***
- Latest `r days <- 30*1;days`days.

```{r warning=F,error=F,message=F,echo=F,results='asis',fig.height=5}
chart.Correlation(
  tail(diffDF[,-1],days),
  method = 'pearson')
```

***
<script>MakeNegative()</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
