---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-SP500andVIX.html')) })

title : 'S&P 500, VIX(VOLATILITY S&P 500) and thier moving average'
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 4
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<style>.main-container {max-width : 1000px;}</style>
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000)
```

```{r,warning=F,error=F,message=F,echo=F}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", functionList[iii,1]),
    ssl.verifypeer = F
  )
  eval(parse(text = script))
}
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/importSP500andVIX.r",
    ssl.verifypeer = F
  )
eval(parse(text = script))
```

```{r warning=F,error=F,message=F,echo=F,results='asis'}
mergeData <- merge(SP500[,c(1,5)],VIX[,c(1,5)],by = 'Date')
```

```{r warning=F,error=F,message=F,echo=F,results='hold'}
dateFormat <- '%Y-%m-%d'
fun_latestResult(obj = mergeData, dateFormat = dateFormat, objColumn = -1)
dataTitle <- 
  paste0('S&P 500, VIX(VOLATILITY S&P 500) and their moving average:',latestResult)
dataSource <- 'Chicago Board Options Exchange, Standard & Poor\'s'
windowsFonts(Meiryo = windowsFont("Meiryo"))
options(scipen = 999)
lineColors <- c('blue','red','green')
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`

***

```{r warning=F,error=F,message=F,echo=F,results='asis'}
library(dygraphs)
tailN <- 10^5
dygraph(tail(SP500xts[,c(1,2,3,4)],tailN),main = 'S&P500') %>% dyCandlestick() %>% dyRangeSelector()
cat('<hr>')
dygraph(tail(VIXxts[,c(1,2,3,4)],tailN),main = 'VIX') %>% dyCandlestick() %>% dyRangeSelector()
```

***
#### Moving Average
##### <b>S&P 500</b>

```{r warning=F,error=F,message=F,echo=F,results='asis'}
n <- 2
maN <- 125
obj <- SP500[,c(1,5)]
fun_MovingAverage(obj = obj,n = maN)
fun_generateKnit(objDF = MovingAverageDF[,c(1,2,3)],
                 plotNum = n,
                 colors = lineColors,
                 dygraphTitle = paste0(colnames(MovingAverageDF)[2],
                                       ' and Moving Average during the last ',maN,' trading days'),
                 group = 0,
                 quantiles = 2)
eval(parse(text = paste0('dygraphPlot', n, ' %>% ', potus_dygraph)))
cat('<hr>')
n <- 3
MovingAverageDF$Gap <- MovingAverageDF[,2]-MovingAverageDF[,3]
fun_generateKnit(objDF = MovingAverageDF[,c(1,5)],
                 plotNum = n,
                 colors = lineColors[1],
                 dygraphTitle = 'Gap between Index and Moving Average',
                 group = 0,
                 barPlot = 1,
                 quantiles = 2)
eval(parse(text = paste0('dygraphPlot', n, ' %>% ', potus_dygraph)))
```

***
##### <b>VIX(VOLATILITY S&P 500)</b>

```{r warning=F,error=F,message=F,echo=F,results='asis'}
remove(MovingAverageDF)
n <- 4
maN <- 50
obj <- VIX[,c(1,5)]
fun_MovingAverage(obj = obj,n = maN)
fun_generateKnit(objDF = MovingAverageDF[,c(1,2,3)],
                 plotNum = n,
                 colors = lineColors,
                 dygraphTitle = paste0(colnames(MovingAverageDF)[2],
                                       ' and Moving Average during the last ',maN,' trading days'),
                 group = 0,
                 quantiles = 2)
eval(parse(text = paste0('dygraphPlot', n, ' %>% ', potus_dygraph)))
cat('<hr>')
n <- 5
MovingAverageDF$Gap <- MovingAverageDF[,2]-MovingAverageDF[,3]
fun_generateKnit(objDF = MovingAverageDF[,c(1,5)],
                 plotNum = n,
                 colors = lineColors[1],
                 dygraphTitle = 'Gap between Index and Moving Average',
                 group = 0,
                 barPlot = 1,
                 quantiles = 2)
eval(parse(text = paste0('dygraphPlot', n, ' %>% ', potus_dygraph)))
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fun_transposeDataFrame(obj = mergeData)
fun_markdownTable(obj = tDF)
```

***

<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
