---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-POTUS.html')) })

title : "Economic Indices by POTUS and Party"
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 4
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 1000px;}</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000)
```

```{r warning = F, error = F, message = F, echo = F}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r warning=F,error=F,message=F,echo=F,results='hold'}
dataTitle <- paste0('アメリカ合衆国大統領および政党(民主党、共和党)毎の経済指標')
dataSource <- 'Federal Reserve Bank of St. Louis'
windowsFonts(Meiryo=windowsFont("Meiryo"))
options(scipen=9999)
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`

***

```{r warning=F,error=F,message=F,echo=F,results='hide'}
library(lubridate);library(quantmod)
# Reference https://en.wikipedia.org/wiki/List_of_Presidents_of_the_United_States
potusList <- c(
  "1933-03-04",    "Franklin Delano Roosevelt", "blue",
  "1945-04-12",    "Harry S. Truman",           "blue",
  "1953-01-20",    "Dwight David Eisenhower",   "red",
  "1961-01-20",    "John Fitzgerald Kennedy",   "blue",
  "1963-11-22",    "Lyndon Baines Johnson",     "blue",
  "1969-01-20",    "Richard Milhouse Nixon",    "red",
  "1974-08-09",    "Gerald Rudolph Ford Jr.",   "red",
  "1977-01-20",    "James Earl Carter",         "blue",
  "1981-01-20",    "Ronald Wilson Reagan",      "red",
  "1989-01-20",    "George H.W Bush",           "red",
  "1993-01-20",    "Bill Clinton",              "blue",
  "2001-01-20",    "George W. Bush",            "red",
  "2009-01-20",    "Barack Obama",              "blue",
  "2017-01-20",    "Donald Trump",              "red"
)
Inauguration <- potusList[seq(1,length(potusList),by = 3)]
Retirement <- c(tail(Inauguration,-1),as.character(Sys.Date()))
ThePresident <- potusList[seq(2,length(potusList),by = 3)]
Party <- potusList[seq(3,length(potusList),by = 3)]
potusDF <- data.frame(Inauguration,Retirement,ThePresident,Party,stringsAsFactors = F,check.names = F)
potusDF[nrow(potusDF),2] <- as.character(Sys.Date())
colnames(potusDF)[2] <- paste0(colnames(potusDF),'(or Incumbent)')
```

```{r warning=F,error=F,message=F,echo=F,results='asis'}
fun_markdownTable(obj = potusDF)
```

- `r potusDF[nrow(potusDF),3]` is the current president.

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fredData <- list()
cnt <- 0
importData <- c(
    'DGS10','10-Year Treasury Constant Maturity Rate',
    'DEXJPUS','Japan / U.S. Foreign Exchange Rate',
    'UNRATE','Civilian Unemployment Rate',
    'IC4WSA','4-Week Moving Average of Initial Claims',
    'DJIA','Dow Jones Industrial Average©'
  )
for (lll in seq(1, length(importData), by = 2)) {
  cnt <- cnt + 1
  tmp <- getSymbols(importData[lll], src = 'FRED', auto.assign = F)
  tmp <-
    data.frame(Date = as.Date(index(tmp)), tmp[, 1], check.names = F, row.names = NULL, stringsAsFactors = F)
  colnames(tmp)[2] <- importData[lll + 1]
  fredData[[cnt]] <- tmp
  if(lll == 1){allData <- tmp}else{allData <- merge(allData,tmp,by='Date',all = T)}
  tail(fredData[[cnt]])
}
```

```{r warning=F,error=F,message=F,echo=F}
fun_plotTimeSeries <- function(ddd=2){
  DemocraticParty <- RepublicanParty <- data.frame()
  obj <- na.omit(fredData[[ddd]])
  ifelse(length(unique(day(obj[,1]))) == 1,dateFormat <- '%Y-%m',dateFormat <- '%Y-%m-%d')
  par(family='Meiryo',mar=c(3,3,3,1),font.main = 1)
  plot(obj[,1],
       obj[,2],
       type='l',
       col='black',
       xlab='',
       ylab='',
       xaxt='n',
       cex.axis=1.0,cex.lab=1.0,cex.main=1.1,
       lwd=1,
       main = paste0(colnames(obj)[2],'\n',paste0(format(range(obj[,1]),dateFormat),collapse = '~')))
  panel.first = grid(nx = NULL, ny = NULL, lty = 2, equilogs = T)
  axis.Date(side=1, at=obj[,1],format=dateFormat,padj=1,cex.axis=1.0)  
  cnt <- 0
  for(rrr in 1:nrow(potusDF)){
    rectDateL <- as.numeric(max(as.Date(potusDF[rrr,1]),obj[1,1]))
    rectDateR <- as.numeric(min(as.Date(potusDF[rrr,2]),obj[nrow(obj),1]))
    if(as.numeric(obj[1,1]) < rectDateR){
      rect(xleft  = rectDateL, ybottom = par('usr')[3], 
           xright = rectDateR, ytop    = par('usr')[4], 
           col    = potusDF[rrr,4], 
           density = 5, 
           angle = 45, 
           lty = 2, 
           lwd = 1,
           border = T)
    }
    buf <- subset(obj,potusDF[rrr,1] <= obj[,1] & obj[,1] < potusDF[rrr,2])
    if(nrow(buf)!=0){
      cnt <- cnt + 1
      buf$POTUS <- potusDF[rrr,3]
      ifelse(potusDF[rrr,4]=='blue',
             DemocraticParty <-
               rbind(DemocraticParty,buf),
             RepublicanParty <- 
               rbind(RepublicanParty,buf))
      lo <- loess(buf[, 2] ~ as.numeric(buf[, 1])) 
      lo <- lm(buf[, 2] ~ as.numeric(buf[, 1])) 
      lines(buf[, 1] , predict(lo) , col = 'steelblue', lwd = 3, lty = 1)
      bufBox <- buf[,2,drop=F]
      colnames(bufBox)[1] <- unique(buf$POTUS)
      ifelse(cnt == 1,boxData <- bufBox,boxData <- qpcR:::cbind.na(boxData, bufBox))
    }
  }
  boxDataParty <- qpcR:::cbind.na(DemocraticParty[,2], RepublicanParty[,2])
  colnames(boxDataParty) <- c('DemocraticParty','RepublicanParty')
  boxData <<- boxData
  boxDataParty <<- boxDataParty
}  
```

***
#### 10-Year Treasury Constant Maturity Rate / 米国財務省証券10年もの利回り

```{r warning=F,error=F,message=F,echo=F,results='asis'}
ddd <- 1
fun_plotTimeSeries(ddd = ddd)
cat('<hr>')
fun_generateKnit(objDF = fredData[[ddd]],plotNum = ddd,group = 0)
eval(parse(text = paste0('dygraphPlot', ddd)))
cat('<hr>')
rAmCharts::amBoxplot(boxData,horiz=T)
cat('<hr>')
rAmCharts::amBoxplot(boxDataParty,horiz=T)
cat('<hr>')
fun_markdownTable(obj = fun_transposeDataFrame(obj = fredData[[ddd]],dateFormat = '%Y-%m-%d'))
```

***
#### Japan / U.S. Foreign Exchange Rate / ドル円為替レート

```{r warning=F,error=F,message=F,echo=F,results='asis'}
ddd <- 2
fun_plotTimeSeries(ddd = ddd)
cat('<hr>')
fun_generateKnit(objDF = fredData[[ddd]],plotNum = ddd,group = 0)
eval(parse(text = paste0('dygraphPlot', ddd)))
cat('<hr>')
rAmCharts::amBoxplot(boxData,horiz=T)
cat('<hr>')
rAmCharts::amBoxplot(boxDataParty,horiz=T)
cat('<hr>')
fun_markdownTable(obj = fun_transposeDataFrame(obj = fredData[[ddd]],dateFormat = '%Y-%m-%d'))
```

***
#### Civilian Unemployment Rate / 米国失業率

```{r warning=F,error=F,message=F,echo=F,results='asis'}
ddd <- 3
fun_plotTimeSeries(ddd = ddd)
cat('<hr>')
fun_generateKnit(objDF = fredData[[ddd]],plotNum = ddd,group = 0)
eval(parse(text = paste0('dygraphPlot', ddd)))
cat('<hr>')
rAmCharts::amBoxplot(boxData,horiz=T)
cat('<hr>')
rAmCharts::amBoxplot(boxDataParty,horiz=T)
cat('<hr>')
fun_markdownTable(obj = fun_transposeDataFrame(obj = fredData[[ddd]],dateFormat = '%Y-%m'))
```

***
#### 4-Week Moving Average of Initial Claims / 米国失業保険申請件数4週間移動平均

```{r warning=F,error=F,message=F,echo=F,results='asis'}
ddd <- 4
fun_plotTimeSeries(ddd = ddd)
cat('<hr>')
fun_generateKnit(objDF = fredData[[ddd]],plotNum = ddd,group = 0)
eval(parse(text = paste0('dygraphPlot', ddd)))
cat('<hr>')
rAmCharts::amBoxplot(boxData,horiz=T)
cat('<hr>')
rAmCharts::amBoxplot(boxDataParty,horiz=T)
cat('<hr>')
fun_markdownTable(obj = fun_transposeDataFrame(obj = fredData[[ddd]],dateFormat = '%Y-%m-%d'))
```

***
#### Dow Jones Industrial Average© / ダウ工業株30種平均

```{r warning=F,error=F,message=F,echo=F,results='asis'}
ddd <- 5
fun_plotTimeSeries(ddd = ddd)
cat('<hr>')
fun_generateKnit(objDF = fredData[[ddd]],plotNum = ddd,group = 0)
eval(parse(text = paste0('dygraphPlot', ddd)))
cat('<hr>')
rAmCharts::amBoxplot(boxData,horiz=T)
cat('<hr>')
rAmCharts::amBoxplot(boxDataParty,horiz=T)
cat('<hr>')
fun_markdownTable(obj = fun_transposeDataFrame(obj = fredData[[ddd]],dateFormat = '%Y-%m-%d'))
```

***
<script>MakeNegative()</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
