---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');htmlName <- 'BigMacIndex';rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-',htmlName,'.html')) })

title : "Big Mac Index"
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 5
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers
    includes:
       in_header: insertHeader.html
    self_contained: false
---

```{r setup, include=FALSE}
# https://stackoverflow.com/questions/43329230/r-markdown-add-tag-to-head-of-html-output/43334558#43334558
insertFile <- file("insertHeader.html")
writeLines('
<link rel="shortcut icon" href="http://knowledgevault.saecanet.com/charts/indicator/favicon-bar-chart.ico">
',
insertFile)
close(insertFile)
```

<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 1000px;}</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000)
```

```{r warning = F, error = F, message = F, echo = F}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r,warning=F,error=F,message=F,echo=F}
script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/importBigMacIndex.r",
    ssl.verifypeer = F
  )
eval(parse(text = script))
```

```{r,warning=F,error=F,message=F,results='hold',echo=F}
dateFormat <- '%Y-%m'
dataTitle <- paste0('ビッグマック指数:',format(head(bigMacIndex[,1],1),dateFormat))
dataSource <- ' The Economist Newspaper Limited'
windowsFonts(Meiryo = windowsFont("Meiryo"))
options(scipen = 999)
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- Source http://www.economist.com/content/big-mac-index

***

#### Big Mac Index / ビッグマック指数

```{r warning=F,error=F,message=F,echo=F,results='asis'}
fun_extractCountryData <- function(country){
  buf <- bigMacIndex[grep(country,bigMacIndex[,2],ignore.case = T),c(1,5)]
  colnames(buf)[2] <- paste0(country,':Big Mac Price:',colnames(buf)[2])
  buf <- buf[order(buf$Date,decreasing = F),]
  return(buf)
}
fun_plotBMI <- function(obj1,obj2){
  mergeData <- merge(obj1,obj2)
  fun_plotTimeSeries(obj = mergeData,typeL = 'o',typeR = 'o',chartType = 1,dateFormat = dateFormat,dataTitle = 'Big Mac Index',mar = c(4,3,5,1),dataSource = dataSource,needLefLab = 0,cexL = 1.5,cexR = 1.5)
}
USA <- fun_extractCountryData(country = 'United States')
JPN <- fun_extractCountryData(country = 'Japan')
EUR <- fun_extractCountryData(country = 'Euro area')
CHN <- fun_extractCountryData(country = 'China')
GBP <- fun_extractCountryData(country = 'Britain')
AUS <- fun_extractCountryData(country = 'Australia')
SWZ <- fun_extractCountryData(country = 'Switzerland')
```

```{r warning=F,error=F,message=F,echo=F,results='asis'}
country <- 'Japan'
cat(paste0('<h5><b>',country,'</b></h5>\n'))
fun_plotBMI(obj1 = USA,obj2 = JPN)
cat('<hr>')
fun_markdownTable(obj = fun_transposeDataFrame(obj = JPN,dateFormat = dateFormat))
cat('<hr>')
```

```{r warning=F,error=F,message=F,echo=F,results='asis'}
country <- 'Euro area'
cat(paste0('<h5><b>',country,'</b></h5>\n'))
fun_plotBMI(obj1 = USA,obj2 = EUR)
cat('<hr>')
fun_markdownTable(obj = fun_transposeDataFrame(obj = EUR,dateFormat = dateFormat))
cat('<hr>')
```

```{r warning=F,error=F,message=F,echo=F,results='asis'}
country <- 'China'
cat(paste0('<h5><b>',country,'</b></h5>\n'))
fun_plotBMI(obj1 = USA,obj2 = CHN)
cat('<hr>')
fun_markdownTable(obj = fun_transposeDataFrame(obj = CHN,dateFormat = dateFormat))
cat('<hr>')
```

```{r warning=F,error=F,message=F,echo=F,results='asis'}
country <- 'Britain'
cat(paste0('<h5><b>',country,'</b></h5>\n'))
fun_plotBMI(obj1 = USA,obj2 = GBP)
cat('<hr>')
fun_markdownTable(obj = fun_transposeDataFrame(obj = GBP,dateFormat = dateFormat))
cat('<hr>')
```

```{r warning=F,error=F,message=F,echo=F,results='asis'}
country <- 'Australia'
cat(paste0('<h5><b>',country,'</b></h5>\n'))
fun_plotBMI(obj1 = USA,obj2 = AUS)
cat('<hr>')
fun_markdownTable(obj = fun_transposeDataFrame(obj = AUS,dateFormat = dateFormat))
cat('<hr>')
```

```{r warning=F,error=F,message=F,echo=F,results='asis'}
country <- 'Switzerland'
cat(paste0('<h5><b>',country,'</b></h5>\n'))
fun_plotBMI(obj1 = USA,obj2 = SWZ)
cat('<hr>')
fun_markdownTable(obj = fun_transposeDataFrame(obj = SWZ,dateFormat = dateFormat))
cat('<hr>')
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
objDate <- bigMacIndex[1,1]
obj <- subset(bigMacIndex,bigMacIndex[,1]==objDate)[,c(2,3,4,5,6)]
colnames(obj)[-1] <- paste0(format(objDate,dateFormat),':',colnames(obj)[-1])
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fun_preparePlot()
pngFile <-
  paste0(htmlName, "1.png")
png(file = pngFile, width = 1000, height = 600)
##################
obj <- obj[order(obj[,4],decreasing = T),]
obj0 <- obj[1:20,]
obj0$Color <- '#4169e1'
obj0$Color[which(obj0$Country=='United States')] <- '#dc143c'
par(mar=c(4,8,4,2),family='Meiryo',font.main=1,cex.main=1)
barplot(height = obj0[,4],names.arg = obj0$Country,horiz = T,col = obj0$Color,
        las=1,main = paste0('Big Mac Price:',colnames(obj0)[4],'\nSource:',dataSource))
dev.off()
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fun_outputMD(tags = 'ビッグマック指数',
             objDF = obj,
             htmlName = htmlName,
             image1 = 1,
             title = dataTitle,
             tableTitle = 'Latest Data',
             tableName = 'Big Mac Index')
fun_updateURLcsv()
```

<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
