---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-OverviewOfTheWorldEconomicOutlookProjections.html')) })

title : 'Overview Of The World Economic Outlook Projections(Source:IMF)'
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 4
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<style>.main-container {max-width : 1000px;}</style>
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan

本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>


```{r warning=F,error=F,message=F,echo=F,results='hold'}
dataTitle <- 'IMF『世界経済の見通しの概要』:2017年1月16日アップデート版'
dataSource <- 'International Monetary Fund (IMF)'
windowsFonts(Meiryo = windowsFont("Meiryo"))
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- Source https://www.imf.org/external/pubs/ft/weo/2017/update/01/index.htm
- Please be sure to check notes in above source page.

***

```{r warning=F,error=F,message=F,echo=F,results='hide'}
library(rvest)
htmlMarkup <-
  read_html('https://www.imf.org/external/pubs/ft/weo/2017/update/01/index.htm',
            encoding = "utf-8")
trList <-
  htmlMarkup %>% html_nodes(xpath = "//table[@class = 't1']") %>% html_nodes('tr')
for(iii in grep('World Output',trList)[1]:grep('Japanese Yen',trList)){
  valueList <-
    trList[iii] %>% html_nodes('td') %>% html_text()
  bufDF <- 
    gsub('\r|\n','',valueList)
  if(iii == grep('World Output',trList)[1]){
    valueDF0 <- bufDF
  }else{
    valueDF0 <- rbind(valueDF0,bufDF)
  }
}
valueDF0[,-1] <- 
  apply(valueDF0[,-1],2,as.numeric)
valueDF0[,1] <-
  gsub('\\s${1,}','',gsub('<U+00A0>|^\\s{2,}|[0-9]{1,}/','',valueDF0[,1]))
valueDF0 <-
  valueDF0[-grep('Memorandum',valueDF0[,1],ignore.case = T),]
colnames(valueDF0) <-
  as.numeric(trList[grep('World Output',trList)[1]-1] %>% html_nodes('td') %>% html_text())
bufColumn <-
  which(apply(valueDF0,2,function(x)sum(is.na(x))) == nrow(valueDF0))
valueDF1 <-
  valueDF0[,-c(bufColumn[1]:bufColumn[2])]
addColnames <- 
  c('Country/Region','',':YoY(Estimates)',rep(':YoY(Projections)',2),':Q4oQ4(Estimates)',rep(':Q4oQ4(Projections)',2))
colnames(valueDF1) <-
  gsub('na','',paste0(colnames(valueDF1),addColnames),ignore.case = T)
row.names(valueDF1) <- NULL
bufColumn <-
  which(is.na(valueDF1[,2]))
valueDF1[bufColumn,1] <- paste0('<b>',valueDF1[bufColumn,1],'</b>')
WorldEconomicOutlookProjections <- 
  data.frame(valueDF1[,1,drop=F], apply(valueDF1[,-1],2,as.numeric),check.names = F,stringsAsFactors = F)
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
library(RCurl)
functionList <-
  read.csv(
    file = 'https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/functionList.csv',
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(
      paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", functionList[iii,1]),
      ssl.verifypeer = F
      )
  eval(parse(text = script))
}
```

```{r warning = F,error = F,message = F,echo = F,results = 'asis'}
fun_dataTable(obj = WorldEconomicOutlookProjections,
              dateFormat = 0,
              needID = 1,
              orderDirection = 'asc',
              menuLength = 15,
              leftcolumns = 2)
```

***

<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
