---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');htmlName<-'CreditToTheNonfinancialSector';rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-',htmlName,'.html')) })

title : "Credit To The Nonfinancial Sector"
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 5
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 1000px;}</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000)
```

```{r warning = F, error = F, message = F, echo = F}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r warning=F,error=F,message=F,echo=F}
script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/importCreditToTheNonfinancialSector.r",
    ssl.verifypeer = FALSE
  )
eval(parse(text = script))
dataSet <- CreditToTheNonfinancialSector
```

```{r warning=F,error=F,message=F,echo=F,results='hold'}
dateFormat <- '%Y-%m-%d'
dataTitle <- 
  paste0('Credit To The Nonfinancial Sector/世界各国の非金融部門債務残高対国内総生産比:',
         format(tail(dataSet[,1],1),dateFormat))
dataSource <- 
  'Bank for International Settlements'
windowsFonts(Meiryo = windowsFont("Meiryo"))
options(scipen = 999)
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- Source http://www.bis.org/statistics/totcredit.htm?m=6%7C326
- 『They capture the outstanding amount of credit at the end of the reference quarter. 』(BIS)
- Non financial sector =  General government + Households and NPISHs + Non-financial corporations 
- NPISHs:対家計民間非営利団体/Non-profit institution serving households 

***

```{r warning=F,error=F,message=F,echo=F,results='asis'}
colnamesShort <- 
  gsub('([^-]+)\\s-(.+)','\\1',colnames(dataSet)[-1])
commonTxt <- 
  unique(gsub('([^-]+)\\s-\\s(.+)','\\2',colnames(dataSet)[-1]))
colnames(dataSet)[-1] <- colnamesShort
obj0 <- 
  fun_transposeDataFrame(obj = dataSet,tailN = 5,dateFormat = dateFormat)
obj <-
  obj0[order(obj0[,ncol(obj0)],decreasing = T),]
cat('#### ',commonTxt,'\n')
fun_markdownTable(obj = obj)
```

***

```{r warning=F, error=F, message=F, echo=F, results='asis'}
objCol <- 
  grep('japan|greece|china|united states',colnames(dataSet),ignore.case = T)
obj <- na.omit(dataSet[,c(1,objCol)])
n <- 1
fun_generateKnit(objDF = obj,plotNum = n,dygraphTitle = commonTxt,group = 0)
eval(parse(text = paste0('dygraphPlot', n, ' %>% ', primeMinisterOfJapan_dygraph)))
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
objCol <- 
  grep('japan',colnames(dataSet),ignore.case = T)
obj <- na.omit(dataSet[,c(1,objCol)])
fun_PlotStrawAnd4charts(obj = obj,varType = 2,tailN = c(10^10,4*10,4*5,4*3))
dev.off();dev.off()
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fun_outputMD(tags = '非金融部門債務残高対国内総生産比,BIS',
             objDF = fun_summaryByName(obj = obj),
             htmlName = htmlName,
             image1 = 1,image2 = 1,
             dataTitle = dataTitle,
             tableTitle = colnames(obj)[2])
fun_updateURLcsv()
```

***
<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
