---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');htmlName<-'RealEarningsUSA';rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-',htmlName,'.html')) })

title : 'Real Earnings In USA'
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 4
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 1300px;}</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000,scipen = 999)
```

```{r warning = F, error = F, message = F, echo = F}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r,warning=F,error=F,message=F,echo=F,results='hide'}
importAMCC <-c('importRealEarningsUSA.r')
for(iii in 1:length(importAMCC)){
  script <-
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/",
                  importAMCC[iii]),
           ssl.verifypeer = F
  )
  eval(parse(text = script))
}
```

```{r warning=F,error=F,message=F,echo=F,results='hold'}
dateFormat <- '%Y-%m'
objDate <- gsub('(.+)\\(.+\\)','\\1',tail(colnames(RealEarnings[[1]]),1))
dataTitle <- 
  paste0('Real Earnings In USA:',objDate)
dataSource <- 'U.S. Bureau of Labor Statistics'
windowsFonts(Meiryo = windowsFont("Meiryo"))
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- Source https://www.bls.gov/bls/newsrels.htm

***

```{r warning=F, error=F, message=F, echo=F,results='asis'}
fun_CPI <- function(iii = 1){
  cat('#### ',captionS[iii],'\n\n')
  obj0 <- RealEarnings[[iii]]
  objCol1 <- head(grep('unadjusted percent change',colnames(obj0),ignore.case = T),1)
  objCol2 <- tail(grep('\\sadjusted percent change',colnames(obj0),ignore.case = T),1)
  if(iii==4|iii==5|iii==6|iii==7){objCol1 <- 3;objCol2 <- 5}
  obj1 <- obj0[,c(1,objCol1,objCol2)]
  return(obj1)
}
```

```{r warning=F, error=F, message=F, echo=F,results='asis'}
iii <- 1
cat('#### ',captionS[iii],'\n\n')
fun_dataTable(obj = RealEarnings[[iii]],orderDirection = 'asc',dateFormat = 0,
              menuLength = 15,needID = 1,leftcolumns = 2)
cat('\n\n<hr>\n\n')
```

```{r warning=F, error=F, message=F, echo=F,results='asis'}
iii <- 2
cat('#### ',captionS[iii],'\n\n')
fun_dataTable(obj = RealEarnings[[iii]],orderDirection = 'asc',dateFormat = 0,
              menuLength = 15,needID = 1,leftcolumns = 2)
cat('\n\n<hr>\n\n')
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fun_preparePlot()
pngFile <-
  paste0(htmlName, "1.png")
png(file = pngFile, width = 1000, height = 600)
ddd <- 1
obj <- RealEarnings[[ddd]]
obj <- obj[grep('year percent change.+(earnings|consumers)',obj[,1],ignore.case = T),c(1,ncol(obj))]
mainTxt <- gsub('(.+):.+','\\1',obj[1,1])
obj[,1] <- gsub('.+:(.+)','\\1',obj[,1])
obj$Col <- ifelse(0<=obj[,2],'#4169e1','#dc143c')
par(mar=c(4,21,5,1),family='Meiryo',font.main=1,cex.main=1,oma=c(2,0,0,0))
barplot(height = obj[,2],names.arg = obj[,1],horiz = T,las = 1,
        col = obj$Col,
        main = paste0(mainTxt,':',colnames(obj)[2]))
mtext(text = paste0(captionS[ddd],'\nSource:',dataSource),side = 1,outer = T)
dev.off()
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fun_outputMD(tags = 'Real Earnings',
             objDF = obj[,-3],
             htmlName = htmlName,
             image1 = 1,image2 = 0,
             title = dataTitle,
             tableTitle = paste0(mainTxt,':',colnames(obj)[2]),
             tableName = captionS[ddd])
fun_updateURLcsv()
```

<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
