---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-OECD-UnemploymentRate.html')) })

title : 'OECD:Unemployment Rate:Quarterly Data'
author: 'アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp'
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 5
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 1000px;}</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000)
```

```{r warning = F, error = F, message = F, echo = F}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
library(RCurl);library(knitr)
script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/importOECDStatisticData.r",
    ssl.verifypeer = F
  )
eval(parse(text = script))
windowsFonts(Meiryo=windowsFont("Meiryo"))
options(scipen=100)
```

```{r warning=F, error=F, message=F, echo=F, results='asis'}
q <- 4
sdmxURL <- paste0("http://stats.oecd.org/restsdmx/sdmx.ashx/GetData/STLABOUR/AUS+AUT+BEL+CAN+CHL+CZE+DNK+EST+FIN+FRA+DEU+GRC+HUN+ISL+IRL+ISR+ITA+JPN+KOR+LVA+LUX+MEX+NLD+NZL+NOR+POL+PRT+SVK+SVN+ESP+SWE+CHE+TUR+GBR+USA+EA19+EU28+G-7+OECD.LRUN25TT.STSA.Q/all?startTime=1953-Q1&endTime=2020-Q",q)
fun_OECDStatisticData(sdmxURL = sdmxURL, period = 4)
oecd01 <- allOECDData
oecd01[,-1] <- apply(oecd01[,-1],2,function(x)round(x,1))
sdmxTitle01 <- 'Aged 25-54,All persons'
```

```{r warning=F, error=F, message=F, echo=F, results='hold'}
dateFormat <- '%Y年%m月期'
dataTitle <- paste0('OECD 季節調整失業率:' , format(tail(allOECDData[,1],1) , dateFormat))
dataSource <- 'Organisation for Economic Co-operation and Development：経済協力開発機構'
windowsFonts(Meiryo=windowsFont("Meiryo"))
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- Source https://stats.oecd.org/
- Labour:Labour Force Statistics:Short-Term Statistics:Short-Term Labour Market Statistics:Unemployment Rates by age and gender

***
#### `r sdmxTitle01` 

```{r warning=F, error=F, message=F, echo=F, results='asis'}
tsData <-
  tail(na.omit(oecd01[ ,grep(pattern = 'date|jpn|usa|fra|austra|deu|esp',
                             x = colnames(oecd01),
                             ignore.case = T)]),
       12*100)
n <- 1
fun_generateKnit(objDF = tsData,plotNum = n,dygraphTitle = colnames(tsData)[-1])
eval(parse(text = paste0('dygraphPlot',n)))
```

***

```{r warning=F, error=F, message=F, echo=F, results='asis'}
fun_markdownTable(obj = fun_transposeDataFrame(obj = oecd01,
                                               dateFormat = dateFormat,
                                               colName = 'Country/Region'))
```

***
<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
