---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');htmlName<-'OfficeData';rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-',htmlName,'.html')) })

title : 'Office Data of Japan'
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 4
    fig_width: 9  
    keep_md: no
    md_extensions: -ascii_identifiers 
    includes:
       in_header: insertHeader.html
    self_contained: false
---

```{r setup, include=FALSE}
tag <-
  read.csv(file = 'https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/components/insertHeader.csv',header = F,fileEncoding = 'UTF8')
tagTxt <- ''
for(rrr in 1:nrow(tag)){
  tagTxt <- paste0(tagTxt,tag[rrr,1],'\n')
}
insertFile <- file("insertHeader.html")
writeLines(text = tagTxt,con = insertFile)
close(insertFile)
```

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
# ―,ソ,噂,欺,圭,構,蚕,十,申,貼,能,表,暴,予,禄,兔
options(width = 900,scipen = 999)
```

```{r,warning=F,error=F,message=F,echo=F}
windowsFonts(Meiryo = windowsFont("Meiryo"))
```

```{r warning=F,error=F,message=F,echo=F}
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    RCurl::getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
needImport <- 1
if(needImport==1){
  script <-
    RCurl::getURL(
      "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/importOfficeData.r",
      ssl.verifypeer = F
    )
  eval(parse(text = script))
}
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
userName <- Sys.info()['user']
pathToFile <-
  paste0('C:/Users/',userName,'/Desktop/pathToCSV/')
setwd(pathToFile)
buf <-
  read.csv(file = 'defaultPath.csv',
           header = F,
           skip = 0,
           stringsAsFactor = F,
           check.names = F,
           fileEncoding = 'utf-8',quote = "\"")
pathToFolder <- 'TSdata'
pathOutputTOcsv <-
  paste0("C:/Users/",userName,buf[2,1],'csv/csvData/',pathToFolder,'/')
setwd(pathOutputTOcsv)
objCSV <-
  grep('officedata_[0-9]+',dir(pathOutputTOcsv),ignore.case = T)
for(iii in seq(length(objCSV))){
  buf <- 
    read.csv(file = dir(pathOutputTOcsv)[objCSV[iii]],
             fileEncoding = 'UTF8',check.names = F,stringsAsFactors = F)
  if(iii==1){allOfficeData <- buf}else{allOfficeData <- rbind(allOfficeData,buf)}
}
```

```{r,warning=F,error=F,message=F,results='hold',echo=F}
allOfficeData$`エリア` <- NA 
objRaw <- grep('_sa',allOfficeData$xlsFile,ignore.case = T)
allOfficeData[objRaw,ncol(allOfficeData)] <- '札幌'
objRaw <- grep('_se',allOfficeData$xlsFile,ignore.case = T)
allOfficeData[objRaw,ncol(allOfficeData)] <- '仙台'
objRaw <- grep('_to',allOfficeData$xlsFile,ignore.case = T)
allOfficeData[objRaw,ncol(allOfficeData)] <- '東京'
objRaw <- grep('_yo',allOfficeData$xlsFile,ignore.case = T)
allOfficeData[objRaw,ncol(allOfficeData)] <- '横浜'
objRaw <- grep('_na',allOfficeData$xlsFile,ignore.case = T)
allOfficeData[objRaw,ncol(allOfficeData)] <- '名古屋'
objRaw <- grep('_os',allOfficeData$xlsFile,ignore.case = T)
allOfficeData[objRaw,ncol(allOfficeData)] <- '大阪'
objRaw <- grep('_fu',allOfficeData$xlsFile,ignore.case = T)
allOfficeData[objRaw,ncol(allOfficeData)] <- '福岡'
```

```{r,warning=F,error=F,message=F,results='hold',echo=F}
allOfficeData[,1] <- as.Date(allOfficeData[,1])
dateFormat <- 
  '%Y年%m月'
dataTitle <- 
  paste0('オフィス空室率(Source:三鬼商事株式会社):',format(max(allOfficeData[,1]),dateFormat)) 
dataSource <- '三鬼商事株式会社'
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- Source https://www.e-miki.com/market/office.html

***

```{r warning=F,error=F,message=F,echo=F,fig.height=4,results='asis'}
fun_plot <- function(iii = 1,objCol = 2){
  obj0 <- subset(allOfficeData,allOfficeData$`エリア`==area[iii])
  dist <- unique(obj0$`地区`)
  par(mar = c(4,5,4,1),font.main = 1,cex.main = 1.4,cex.axis = 1.2,cex.lab = 1.3,
      mfrow = c(ceiling(length(dist)/2),2))
  for(sss in seq(length(dist))){
    obj1 <- subset(obj0,obj0$`地区`==dist[sss])
    # 重複行削除処理
    dupRows <- duplicated(obj1[,-grep('xlsfile',colnames(obj1),ignore.case = T)])
    obj1 <- obj1[-which(dupRows),]
    obj1[,1] <- as.Date(obj1[,1])
    # 重複行削除処理
    plot(x = obj1[,1],y = obj1[,objCol],col = 'blue',
         main = paste0(paste0(area[iii],':',dist[sss]),
                       '\n',paste0(format(range(obj1[,1]),dateFormat),collapse = '~')),
         type = 'o',pch = 20,cex = 2.5,xaxt = 'n',xlab = '',ylab = colnames(obj1)[objCol],
         panel.first = grid(nx = NULL,ny = NULL,lty = 2,equilogs = T))
    lo <- loess(formula = obj1[,objCol] ~ as.numeric(obj1[,1]),degree = 2)
    lines(x = obj1[,1],y = predict(lo),col = 'red',lwd = 2,lty = 2)
    axis.Date(side = 1,at = obj1[,1],format = dateFormat,padj = 1,cex.axis = 1)
  }
}
area <- unique(allOfficeData$`エリア`)
objCol <- 8
```

#### 空室率時系列推移

```{r warning=F,error=F,message=F,echo=F,fig.height=12,results='asis'}
iii <- 1
cat('#### ',area[iii],'\n')
fun_plot(iii = iii,objCol = 8)
```

***

```{r warning=F,error=F,message=F,echo=F,fig.height=12,results='asis'}
iii <- 2
cat('#### ',area[iii],'\n')
fun_plot(iii = iii,objCol = 8)
```

***

```{r warning=F,error=F,message=F,echo=F,fig.height=12,results='asis'}
iii <- 3
cat('#### ',area[iii],'\n')
fun_plot(iii = iii,objCol = 8)
```

***

```{r warning=F,error=F,message=F,echo=F,fig.height=16,results='asis'}
iii <- 4
cat('#### ',area[iii],'\n')
fun_plot(iii = iii,objCol = 8)
```

***

```{r warning=F,error=F,message=F,echo=F,fig.height=12,results='asis'}
iii <- 5
cat('#### ',area[iii],'\n')
fun_plot(iii = iii,objCol = 8)
```

***

```{r warning=F,error=F,message=F,echo=F,fig.height=20,results='asis'}
iii <- 6
cat('#### ',area[iii],'\n')
fun_plot(iii = iii,objCol = 8)
```

***

```{r warning=F,error=F,message=F,echo=F,fig.height=16,results='asis'}
iii <- 7
cat('#### ',area[iii],'\n')
fun_plot(iii = iii,objCol = 8)
```

***

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fun_preparePlot()
pngFile <-
  paste0(htmlName, "1.png")
png(file = pngFile, width = 1000, height = 600)
##################
par(mar=c(4,5,5,1),family='Meiryo',font.main=1,cex.main=1.2,cex.lab=1.1)
obj0 <- 
  allOfficeData[grep('東京ビジネス地区|大阪ビジネス地区|福岡ビジネス地区',allOfficeData$`地区`),]
objCol <- 8
ylim <- 
  c(min(obj0[,objCol]),max(obj0[,objCol]))
dist <- 
  unique(obj0$`地区`)
lineColor <- c('blue','red','green')
iii <- 1
obj1 <- subset(obj0,obj0$`地区`==dist[iii])
plot(x = obj1[,1],y = obj1[,objCol],col = lineColor[iii],ylim = ylim,
     main = paste0(colnames(obj1)[objCol],'\n',
                   paste0(format(range(obj1[,1]),dateFormat),collapse = '~'),
                   '\nSource:',dataSource),
     type = 'o',pch = 20,cex = 2.5,xaxt = 'n',xlab = '',ylab = colnames(obj1)[objCol],
     panel.first = grid(nx = NULL,ny = NULL,lty = 2,equilogs = T))
iii <- 2
obj1 <- subset(obj0,obj0$`地区`==dist[iii])
lines(x = obj1[,1],y = obj1[,objCol],col = lineColor[iii],type = 'o',pch = 20,cex = 2.5)
iii <- 3
obj1 <- subset(obj0,obj0$`地区`==dist[iii])
lines(x = obj1[,1],y = obj1[,objCol],col = lineColor[iii],type = 'o',pch = 20,cex = 2.5)
axis.Date(side = 1,at = obj1[,1],format = dateFormat,padj = 1,cex.axis = 1)
graphics::legend(x = 'topright',col = lineColor,lty = 1,legend = dist,
                 cex = 1,bty = 'n',lwd = 2)
dev.off()
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
obj0 <- allOfficeData[max(allOfficeData[,1])==allOfficeData[,1],]
obj1 <- obj0[grep('ビジネス地区',obj0$`地区`),]
obj2 <- obj1[,c(17,7,8,9,10)]
fun_outputMD(tags = '三鬼商事,空室率',
             objDF = obj2,
             htmlName = htmlName,
             image1 = 1,image2 = 0,
             title = dataTitle,
             tableTitle = format(unique(obj1$Date),dateFormat),
             tableName = 'ビジネス地区空室率')
fun_updateURLcsv()
```

<script>MakeNegative()</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
