---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-IIMAGMVI.html')) })

title : 'Global Markets Volatility Index(Source:Institute for International Monetary Affairs)'
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 10
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 1000px;}</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 500)
```

```{r warning = F, error = F, message = F, echo = F}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r,warning=F,error=F,message=F,echo=F}
script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/importGMVI.r",
    ssl.verifypeer = FALSE
  )
eval(parse(text = script))
```

```{r,warning=F,error=F,message=F,results='hold',echo=F}
dataTitle <- 
  paste0('IIMA Global Market Volatility Index:',paste0(range(GMVI1[,1]),collapse = '~'))
dataSource <- 
  'Institute for International Monetary Affairs'
windowsFonts(Meiryo = windowsFont("Meiryo"))
options(scipen = 999)
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- Source http://www.iima.or.jp/index.html
- Source http://www.iima.or.jp/research/ppp/index.html

***

```{r,warning=F,error=F,message=F,results='hold',echo=F,fig.height=7}
library(lubridate)
obj <-
  subset(GMVI1,
         head(unique(year(GMVI1[,1])),1) < year(GMVI1[,1]) &
           year(GMVI1[,1]) < tail(unique(year(GMVI1[,1])),1))
yyyy <-
  unique(year(obj[,1]))
frequencyN <-
  median(sapply(yyyy,function(x)nrow(obj[year(obj[,1])==x,])))
tsData <-
  ts(obj[,2],frequency = frequencyN)
stlData <-
  stl(x = tsData, s.window = "per")
par(family = 'Meiryo')
plot(stlData,main = paste0(colnames(obj)[2],':',paste0(range(obj[,1]),collapse = '~')))
```

***

```{r,warning=F,error=F,message=F,results='hold',echo=F,fig.height=5}
specData <-
  spec.pgram(obj[,2],log="yes",plot = F)
par(family = 'Meiryo')
plot(specData,main =paste0(colnames(obj)[2],'\n',specData$method))
panel.first = grid(nx = NULL,
                   ny = NULL,
                   lty = 2,
                   equilogs = T)
```

***
<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
