---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');htmlName<-'CFTChistoricalData';rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-',htmlName,'.html')) })

title : "CFTC Historical Data:Futures Only Reports"
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 5
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<style>.main-container {max-width : 1000px;}</style>
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000)
```

```{r warning = F, error = F, message = F, echo = F}
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    RCurl::getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r warning=F, error=F, message=F, echo=F,results='hide'}
rFile <- c('importCFTChistoricalData.r')
for(iii in 1:length(rFile)){
  script <- 
    RCurl::getURL(
      paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/',rFile[iii]),
      ssl.verifypeer = F)
eval(parse(text = script))
}
cftc <- fun_CFTChistoricalData(objFirst = 4)
```

```{r,warning=F,error=F,message=F,results='hold',echo=F}
options(scipen = 999)
dateFormat <- '%Y-%m-%d'
dataTitle <- 
  paste0('CFTC Historical Data:Futures Only Reports:',tail(cftc[[1]],1)[1,1])
dataSource <- 'Commodity Futures Trading Commission'
windowsFonts(Meiryo=windowsFont("Meiryo"))
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- Source http://www.cftc.gov/index.htm

***

#### Latest Result

```{r,warning=F,error=F,message=F,results='asis',echo=F}
MarketName <- vector()
cnt <- 1
for(iii in seq(length(cftc))){
  if((as.Date(Sys.Date())-14)<=tail(cftc[[iii]],1)[1,1]){
    obj <- tail(cftc[[iii]],1)[,c(1,9,7,8,6)]
    cat(paste0('- ID:',iii,'. ',obj[,2],'\n'))
    fun_markdownTable(obj = obj[,-2])
    cat('\n<hr>\n')
    MarketName[cnt] <- obj[,2]
    cnt <- cnt + 1
  }
}
```

```{r warning=F, error=F, message=F, echo=F,results='asis'}
fun_plot <- function(obj0,objCol){
  lineColor <- c('blue','red')
  par(mfrow=c(1,2),oma=c(0,0,3,0),family='Meiryo',font.main=1,mar=c(4,3,3,2),cex.main=1.1)
  obj <- na.omit(obj0[,c(1,objCol)])
  ylim <- c(min(obj[,2:3]),max(obj[,2:3]))
  plot(x = obj[,1],y = obj[,2],type = 'o',pch = 20,cex=1.1,ylim = ylim,xaxt='n',
       xlab='',ylab = '',col=lineColor[1],panel.first = grid(nx = NULL,ny = NULL,lty = 2,equilogs = T))
  par(new=T)
  plot(x = obj[,1],y = obj[,3],type = 'o',pch = 20,cex=1.1,ylim = ylim,xaxt='n',
       xlab='',ylab = '',col=lineColor[2],panel.first = grid(nx = NULL,ny = NULL,lty = 2,equilogs = T),
       yaxt='n')
  graphics::legend(x = 'topleft',col = lineColor,lty = 1,legend = colnames(obj)[c(2,3)],
                   cex = 1.0,bty = 'n',lwd = 2)
  axis.Date(side = 1,at = obj[,1],format = dateFormat,padj = 1,cex.axis = 1.0)
  obj$Color <- ifelse(0<=obj[,4],'blue','red')
  plot(x = obj[,1],y = obj[,4],type = 'h',pch = 20,xaxt='n',xlab='',ylab = '',
       col=obj$Color,panel.first = grid(nx = NULL,ny = NULL,lty = 2,equilogs = T),main = colnames(obj)[4])
  axis.Date(side = 1,at = obj[,1],format = dateFormat,padj = 1,cex.axis = 1.0)
  mtext(text = paste0(unique(obj0$Name),'. Unit:',unique(obj0$Unit),
                      '\n',paste0(range(obj0$Date),collapse = ' ~ ')),side = 3,outer = T)
  cat('\n<hr>\n')
}
```

#### Time Series Chart

```{r warning=F, error=F, message=F, echo=F,results='asis'}
objData <-
  c('U.S. TREASURY BONDS',
    '10-YEAR U.S. TREASURY NOTES',
    'JAPANESE YEN',
    'U.S. DOLLAR INDEX',
    'VIX FUTURES',
    'SOUTH AFRICAN RAND',
    'DJIA Consolidated',
    'NIKKEI STOCK AVERAGE',
    'NIKKEI STOCK AVERAGE YEN DENOM')
for(iii in seq(length(cftc))){
  if((as.Date(Sys.Date())-14)<=tail(cftc[[iii]],1)[1,1]){
    obj0 <- cftc[[iii]]
    if(length(grep(paste0(objData,collapse = '|'),obj0$Name,ignore.case = T))!=0){
      if(length(grep('japanese yen',unique(obj0$Name),ignore.case = T))){JPY <- iii}
      cat(paste0('- ',unique(obj0$Name),'. Unit:',unique(obj0$Unit)))
      # Noncommercial
      objCol <- c(2,3,7)
      fun_plot(obj0 = obj0,objCol = objCol)
      # Commercial
      objCol <- c(4,5,8)
      fun_plot(obj0 = obj0,objCol = objCol)
    }
  }
}
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
obj <- na.omit(cftc[[JPY]])
colnames(obj) <- paste0(colnames(obj),':',unique(obj$Name))
obj <- obj[,c(1,7)]
fun_PlotStrawAnd4charts(obj = obj,varType = 2,
                        dateFormat = dateFormat,
                        tailN=c(10^10,5*12,5*6,5*3),
                        startYear = 2014)
dev.off();dev.off()
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
obj <- na.omit(cftc[[JPY]][,c(1,6,7,8,9)])
fun_outputMD(tags = 'CFTC,Futures',
             objDF = tail(obj[,c(1,3,4)],5),
             htmlName = htmlName,
             image1 = 1,image2 = 1,
             title = dataTitle,
             tableTitle = 'Latest 5days',
             tableName = paste0(unique(obj$Name),unique(obj$Unit)))
fun_updateURLcsv()
```

<script>MakeNegative()</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
