---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');htmlName<-'IMFPrimaryCommodityPrices';rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-',htmlName,'.html')) })

title : 'IMF Primary Commodity Prices'
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 4
    fig_width: 13
    keep_md: no
    md_extensions: -ascii_identifiers 
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 1300px;}</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000)
```

```{r warning = F, error = F, message = F, echo = F}
library(RCurl)
fileName <- 'functionList.csv'
functionList <-
  read.csv(
    file = paste0('https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/csv/',
                  fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    getURL(paste0("https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/", 
                  functionList[iii,1]),
           ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r,warning=F,error=F,message=F,echo=F}
# library(choroplethrAdmin1)
# library(DT)
# library(lubridate)
# library(googleVis)
# library(pipeR)
# library(RCurl)
# library(seasonal)
# library(dplyr)
# library(plotly)
script <-
  getURL(
    "https://raw.githubusercontent.com/am-consulting/Rscript/master/importIMFPrimaryCommodityPrices.r",
    ssl.verifypeer = FALSE
  )
eval(parse(text = script))
windowsFonts(Meiryo = windowsFont("Meiryo"))
options(scipen = 100)
dateFormat <- '%Y-%m'
```

```{r,warning=F,error=F,message=F,results='hold',echo=F}
fun_latestResult(obj = origData,dateFormat = dateFormat)
dataTitle <- paste0('IMF Primary Commodity Prices:',latestResult)
dataSource <- 'International Monetary Fund'
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- Source http://www.imf.org/external/np/res/commod/index.aspx

***
```{r,warning=F,error=F,message=F,echo=F} 
funPlotTimeSeries <- function() {
  plot(
    dataSet[, 1],
    dataSet[, 2],
    type = seriesType,
    col = dataSet$col,
    xlab = '' ,
    ylab = '' ,
    panel.first = grid(nx = NULL, ny = NULL, lty = 2, equilogs = T) ,
    xaxt = 'n',
    main = mainTitle,
    cex.axis = 1,
    cex.lab = 1,
    cex.main = 1,
    lwd = objlwd
  )
  lo <- loess(dataSet[, 2] ~ as.numeric(dataSet[, 1]), degree = 2)
  lines(dataSet[, 1] , predict(lo) , col = 'red', lwd = 2, lty = 2)
  axis.Date(side = 1, at = dataSet[, 1], format = dateFormat, padj = 1, cex.axis = 1.0)  
}
```

#### 直近月の前年同月比(%) / Year over Year of Latest Data

```{r,warning=F,error=F,message=F,echo=F,results='asis'} 
fun_dataTable(obj = fun_transposeDataFrame(obj = fun_makeDiffRatioTable(obj = origData,lag = 12),
                                               tailN = 1,
                                               dateFormat = dateFormat),
                  dateFormat =0,
                  needID = 1,
                  orderDirection = 'asc')
```

***

```{r,warning=F,error=F,message=F,echo=F,results='asis'} 
par(mar = c(3, 3, 3, 1),family = 'Meiryo',oma = c(0, 0, 0, 0),mfrow = c(1, 2),font.main = 1)
dateFormat <- '%Y-%m'
iii <- 2
for (iii in 2:ncol(origData)) {
  cat(paste0('<h5>',colnames(origData)[iii],'</h5>'))
  for (sss in 1:2) {
    dataSet0 <- na.omit(origData[, c(1, iii)])
    dataSet <- dataSet0
    seriesType <- 'l'
    objlwd <- 1
    if (sss == 2) {
      # 前月同月比
      dataSet <-
        data.frame(
          Date = tail(dataSet[, 1], nrow(dataSet) - 12),
          round(
            diff(
              as.matrix(dataSet[, -1]),
              lag = 12,
              differences = 1
            ) /
              as.matrix(head(dataSet[, -1], nrow(dataSet) - 12)) * 100,
            2
          ),
          check.names = F
        )
      seriesType <- 'h'
      objlwd <- 1
      dataSet$col <- ifelse(dataSet[, 2] < 0, 'red', 'blue')
      append <- '前年同月比(%)'
      colnames(dataSet)[2] <- paste0('YoY-',colnames(dataSet0)[2])
    } else{
      dataSet$col <- 'blue'
      append <- '原数値'
    }
    periodData <-
      format(c(head(dataSet[, 1], 1), tail(dataSet[, 1], 1)), dateFormat)
    mainTitle <- paste0(periodData[1], '~', periodData[2], '\n', append)
    funPlotTimeSeries()
  }
  mtext(text = '', outer = T, side = 3)
  cat('<hr>')
}
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
username <-
  Sys.info()['user']
pathToFile <-
  paste0('C:/Users/', username,'/Desktop/pathToCSV/')
setwd(pathToFile)
fileName <-
  'defaultPath.csv'
buf <-
  read.csv(file = fileName,
           header = F,
           skip = 0,
           stringsAsFactor = F,
           check.names = F,
           fileEncoding = 'utf-8',quote = "\"")
pathOutputTOcsv <-
  paste0("C:/Users/", username, buf[2,1],'charts/chartImages/')
setwd(pathOutputTOcsv)
getwd()
par(family = 'Meiryo')
pngFile <-
  paste0(htmlName, ".png")
png(file = pngFile, width = 1000, height = 600)
##################
obj <- origData[,c(1,2)]
fun_plot4charts(obj = obj,dateFormat = dateFormat,tailN = c(10^10,12*5,12*3,12*1))
dev.off()
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
obj <- na.omit(origData[,c(1,2)])
fun_outputMD(tags = 'IMF,Primary Commodity Prices',
             objDF = fun_summaryByName(obj = obj,dateFormat = dateFormat),
             htmlName = htmlName,
             image = 1,
             dataTitle = dataTitle,
             tableTitle = colnames(obj)[2])
```

<script>MakeNegative()</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
