---
knit: (function(inputFile, encoding) {username<-Sys.info()['user'];fileName<-'defaultPath.csv';pathToFile <-paste0('C:/Users/', username,'/Desktop/pathToCSV/');setwd(pathToFile);buf0<-read.csv(fileName,header = F,skip = 0,stringsAsFactor = F,check.names = F,fileEncoding = 'utf-8');timeStamp<-format(Sys.time(),'%Y%m%d%H%M%S');htmlName<-'WorldDevelopmentIndicators';rmarkdown::render(inputFile, encoding = encoding, output_file = paste0('C:/Users/',username,buf0[2,1],'charts/','am-consulting.co.jp-',htmlName,'.html')) })

title : 'World Development Indicators(Source:The World Bank Group)'
author: "アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    fig_height: 4
    fig_width: 10
    keep_md: no
    md_extensions: -ascii_identifiers
---
<link href="http://knowledgevault.saecanet.com/components/rmarkdown-html.css" rel="stylesheet">
<script src="http://knowledgevault.saecanet.com/components/JavascriptCode.js"></script>
<style>.main-container {max-width : 1000px;}</style>

- アセット･マネジメント･コンサルティング株式会社 http://am-consulting.co.jp
- SaECaNet http://saecanet.com/
- Olive http://olive.saecanet.com/
- twitter https://twitter.com/AMC2_Japan
- 本ページへのリンクを共有:<a href="https://twitter.com/share" class="twitter-share-button" data-via="AMC2_Japan" data-size="large">Tweet</a> <script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r set-options, echo=F, cache=F}
options(width = 1000)
```

```{r warning=F,error=F,message=F,echo=F}
fileName <- 
  'functionList.csv'
baseURL <- 
  'https://raw.githubusercontent.com/am-consulting/am-consulting.github.io/master/'
functionList <- 
  read.csv(
    file = paste0(baseURL,'csv/',fileName),
    header = F,
    as.is = T)
for(iii in 1:nrow(functionList)){
  script <- 
    RCurl::getURL(paste0(baseURL,functionList[iii,1]),ssl.verifypeer = F)
  eval(parse(text = script))
}
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
importData <- 
  c('importWorldDevelopmentIndicators.r')
for(fff in seq(length(importData))){
  script <-
    RCurl::getURL(paste0(baseURL,importData[fff]),ssl.verifypeer = F)
  eval(parse(text = script))
}
objDF <- WorldDevelopmentIndicators
```

```{r warning=F,error=F,message=F,results='hold',echo=F}
dateFormat <- '%Y'
dataTitle <- 
  paste0('World Development Indicators')
dataSource <- 
  'The World Bank Group'
windowsFonts(Meiryo = windowsFont("Meiryo"))
```

***

- `r paste0("タイトル : ", dataTitle)`
- `r paste0("データ出所 : ", dataSource)`
- Source http://databank.worldbank.org/data/home.aspx

***

```{r warning=F,error=F,message=F,results='asis',echo=F}
obj0 <- 
  objDF[!is.na(objDF[,ncol(objDF)]),]
seriesName <- 
  unique(obj0[,3])
countryCode <- 
  unique(obj0[,2])
objSeries <- 
  c(2,3,4)
iii <- 1
obj1 <- 
  obj0[obj0$`Series Name`==seriesName[objSeries[iii]],c(1,2,ncol(obj0))]
cat('#### ',seriesName[objSeries[iii]],'\n\n')
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fun_PlotStrawAnd4charts(obj = obj,dateFormat = dateFormat,tailN = c(10^10,250,125,25))
dev.off();dev.off()
```

```{r warning=F,error=F,message=F,echo=F,results='hide'}
fun_outputMD(tags = '',
             objDF = fun_transposeDataFrame(obj = obj),
             htmlName = htmlName,
             image1 = 1,image2 = 1,
             title = dataTitle,
             tableTitle = 'Latest 5 days',
             tableName = colnames(obj)[2])
fun_updateURLcsv()
```

***

<script>MakeNegative();</script>
<script>
  (function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
  (i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
  m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
  })(window,document,'script','https://www.google-analytics.com/analytics.js','ga');

  ga('create', 'UA-3077339-5', 'auto');
  ga('send', 'pageview');

</script>
